### 2025-02-28 code/Reddit_API.qmd
adding API code

---
title: "Assignment 2"
author: Group 2
date: "`r format(Sys.time(), '%d %B, %Y')`"
embed-resources: true
editor: visual
execute:
  warning: false
  message: false
  error: false
  tidy: true
format: pdf
theme: spacelab
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
# install.packages("devtools")
# devtools::install_github('ivan-rivera/RedditExtractor')
library(RedditExtractoR)
```

# Hitting the Reddit API

1.  Use the Reddit API to “listen” to and download a corpus of posts using the RedditExtractoR package in R

Define

```{r find_thread_url, message=FALSE, warning=FALSE}
# list of keywrods to try
topic_list <- c("DOGE", "Elon Musk", "Department of Government Efficiency", "wasteful spending", "government waste", "government fraud", "drain the swamp",  "reduction in force")

# query each keyword through the api
topic_urls <-  map_dfr(topic_list, function(x){
  find_thread_urls(keywords=x, period='day') 
})  |> tibble()

dim(topic_urls)

```

Clean the dataframe to prepare for descriptive analysis

-   Convert date str to date class

-   Filtering

    -   If text field is missing, it is a post with no text and only a picture. Remove it.

    -   Keep events after a set start date, presidential election

    -   remove posts that start with "https" as these are just links with no text.

```{r}
test <- topic_urls |> 
  # create date string to date object
  mutate(date_utc = ymd(date_utc),
         text = na_if(text, "") ) |> 
  # if text is NA, it's a picture or video, drop it 
  filter(!is.na(text),
         date_utc > "2024-11-05", ,
         !str_starts(text, "https")
         )
```

### Get threads from URLs

```{r get_thread_content}
topic_content = get_thread_content(topic_urls$url)

names(topic_content)

dim(topic_content$threads)
head(topic_content$threads)
```

The 'threads' data frame gives some more information on the posts: author, number of upvotes and downvotes, ratio of upvotes, number of awards received, golds, and cross-posts.

```{r}
dim(topic_content$comments)
head(topic_content$comments)
```

The 'comments' data frame gives comments on the main post. Many population Reddit posts contain many layers of comments. The RedditExtractoR does not give this information (although it is available on the Reddit API).

Lastly, we can search for subreddits based on a keyword using the 'find_subreddits' function.

```{r find_subreddits}
topic_subreddits = find_subreddits('reduction in force')
head(topic_subreddits)
dim(topic_subreddits)
```

#

### 2025-02-28 code/Reddit_API.qmd
adding API code

@@
 
+    -   DOGEcoin is a cryptocurrency, and we need to filter out any posts that are unrelated to our topic of interest.
+
 ```{r}
@@
          date_utc > "2024-11-05", ,
-         !str_starts(text, "https")
+         !str_starts(text, "https"),
+         !str_detect(text, "crypto|coin")
          )

### 2025-03-10 code/Reddit_API.qmd
adding data

--- 2025-02-28 code/Reddit_API.qmd
@@
 library(tidyverse)
+library(readxl)
+library(writexl)
 # install.packages("devtools")
@@
 
-Define
+-   For this work, we focus on the topic of **Department of Government Efficiency and the Federal Workforce** as of the new US administration in early January of this year.
+This topic can help examine DOGE's impact on government employees by exploring perceptions and approval of:
 
-```{r find_thread_url, message=FALSE, warning=FALSE}
+    -   The effects of remove work policies.
+
+    -   Changes in job security.
+
+    -   Impact on work culture
+
+    -   Employee reactions to efficiency measures.
+
+-   We expect that reddit will contain lively discussions surrounding this topic and offer us as researchers a vantage into the public's real time opinions and diverse perspective.
+Initially we examined how this topic is referred to on Reddit and finalized a list of keywords that will help us uncover aspects of this topic.
+However, during this stage we found that the cryptocurrency DOGEcoin, established in 2013, will also be captured using these kerterms and is unrelated with our topic.
+To minimize capturing threads on DOGEcoin, we will limit our search to this year only, as well as later in the process filter out specific keywordsthat are not related to our topic.
+Our final adjustment of this keywords list consisted of iterating over searches and broadening our keywords as needed to have a large corpus of posts.
+
+-   Additionally, we collectively went through several subreddit after the first scrap of these keywords to determine relevant subreddit channels to listen to.
+Our list attempts to compile subreddit channels that favor both sides of this topic.
+
+-   As we prepare our data on our topic we discover that some threads have no text but rather only a video, image, or weblink.
+We made the decision to exclude threads with no text as we will not be able to determine approval.
+Additionally, threads that only provide a weblink are excluded as well.
+
+    -   We build a list of keywords related to our topic.
+
+```{r}
 # list of keywrods to try
-topic_list <- c("DOGE", "Elon Musk", "Department of Government Efficiency", "wasteful spending", "government waste", "government fraud", "drain the swamp",  "reduction in force")
+topic_list <- c("DOGE", 
+                #"elon musk",
+                "Department of Government Efficiency", 
+                "wasteful spending",
+                "government waste", 
+                "government fraud", 
+                #"drain the swamp",  
+                "reduction in force", 
+                "rif",
+                "fork in the road"
+                )
 
-# query each keyword through the api
-topic_urls <-  map_dfr(topic_list, function(x){
-  find_thread_urls(keywords=x, period='day') 
-})  |> tibble()
+subreddit_list <- c("50501", "fednews", 
+                    "neoliberal", "FedEmployees", "WhatTrumpHasDone",
+                    "Whistleblowers", "economy",
+                    "PoliticalOpinions",
+                    "Trumpvirus", "Virginia", 
+                    "Libertarian", "AskTrumpSupporters",
+                    "AskPolitics", "AskConservitives",
+                    "govfire", "conservative", "VeteransAffairs",
+                    "economicCollapse",
+                    "feddiscussion",  
+                    "maryland"
+                    )
 
-dim(topic_urls)
+# Lets create a grid to loop through kewwords and subreddits
+
+search_grid <- expand_grid(topic_list, subreddit_list)
 
@@
 
-Clean the dataframe to prepare for descriptive analysis
+We begin by first reading in all posts from 1/1/2025 to
 
--   Convert date str to date class
+```{r find_thread_url, message=FALSE, warning=FALSE}
 
--   Filtering
+# query each keyword through the api
 
-    -   If text field is missing, it is a post with no text and only a picture. Remove it.
+#_________ Helpful functions _______________
 
-    -   Keep events after a set start date, presidential election
+hit_api_fun = function(topic_var, subreddit_var){
 
-    -   remove posts that start with "https" as these are just links with no text.
+  dat = find_thread_urls(keywords=topic_var, 
+                         period = "hour", 
+                         subreddit = subreddit_var) |> 
+    tibble() |> 
+    mutate(search_term = topic_var) |> 
+    drop_na()
+
+  if(nrow(dat) < 1){
+    cat(str_c("\n  . . . Skipping, search returned NA . . . \n",
+        Sys.time()))
+
+  } else{
+    cat(str_c("\n\n Reading in data file . . . 
+              writing new lines, saving to file . . . \n",
+              Sys.time()))
+
+    # read file, write new rows, save 
+    old_dat = readRDS("D:/repos/SURV622_Assignment/data/posts_data.RDS")
+    new_dat = old_dat |> add_row(dat |> tibble())
+    write_rds(new_dat, "D:/repos/SURV622_Assignment/data/posts_data.RDS")
+  }
+
+  # sleep 
+  Sys.sleep(26)
+
+}
+
+# ______________ Initiate Code Sequence
+
+# days to listen for
+num_days <- 5 * 24 # days * hours
+
+# repeat process for several days
+replicate(n=num_days,
+
+          walk(seq(1:nrow(search_grid)), function(x){
+            cat(str_c("\n Searching for \nkeyword = ", 
+                      search_grid[[x, 1]], " in subreddit = ", 
+                      search_grid[[x, 2]], "\n"))
+
+            posts = hit_api_fun(search_grid[[x, 1]],  search_grid[[x, 2]]) 
+            }) 
+)
+
+```
+
+Read in the full dataset to begin the cleaning process.
 
 ```{r}
-test <- topic_urls |> 
-  # create date string to date object
-  mutate(date_utc = ymd(date_utc),
-         text = na_if(text, "") ) |> 
-  # if text is NA, it's a picture or video, drop it 
-  filter(!is.na(text),
-         date_utc > "2024-11-05", ,
-         !str_starts(text, "https")
-         )
+reddit_unclean <- readRDS("D:/repos/SURV622_Assignment/data/posts_data.RDS")
+glimpse(reddit_unclean)
 ```
 
-### Get threads from URLs
+We will clean the data to remove posts that are only images, URLs, videos, contain irrelevant keywords such as "cryptocurrency" or "dodgecoin," and finally we remove posts that are brief.
 
-```{r get_thread_content}
-topic_content = get_thread_content(topic_urls$url)
+-   We listened for five days every hour, yet we needed to add additional posts as we did not have enough.
+Instead, we add posts starting from 2/24/25 when the project started.
+This way we have almost \~900 posts after cleaning the found data set.
 
-names(topic_content)
+```{r}
 
-dim(topic_content$threads)
-head(topic_content$threads)
+reddit_clean <- reddit_unclean |>
+  # set timeline threshold 
+  filter(date_utc > "2025-02-25") |> 
+  # function we created
+   tibble() |> 
+    # remove any duplicates
+  distinct() |> 
+   mutate(
+          # remove urls from text using rm_url function
+      text = qdapRegex::rm_url(text),
+      date_utc = ymd(date_utc) ) |> 
+   filter(# remove none related topic threads
+           !str_detect(text, "crypto|coin"))
+
+glimpse(reddit_clean)
 ```
 
-The 'threads' data frame gives some more information on the posts: author, number of upvotes and downvotes, ratio of upvotes, number of awards received, golds, and cross-posts.
+We now need to get the comments within each post. This will bring us back a list, and we will need to extract the post metadata and comments into separate data tables.
 
 ```{r}
-dim(topic_content$comments)
-head(topic_content$comments)
+# pass the urls collected from the post
+reddit_content <- map(reddit_clean$url, function(x){
+
+  thread = get_thread_content(x)
+
+  # let it sleep so it doesn't hit the max per hour
+  Sys.sleep(5)
+
+  return(thread)
+}) 
 ```
 
-The 'comments' data frame gives comments on the main post.
-Many population Reddit posts contain many layers of comments.
-The RedditExtractoR does not give this information (although it is available on the Reddit API).
+-   Separate post metadata and merge as new columns into the clean reddit data set we extracted from our initial data collection.
 
-Lastly, we can search for subreddits based on a keyword using the 'find_subreddits' function.
+```{r}
+# collect metadata
+reddit_metadata <- map_dfr(reddit_content, function(x){
 
-```{r find_subreddits}
-topic_subreddits = find_subreddits('reduction in force')
-head(topic_subreddits)
-dim(topic_subreddits)
+  dat = x$threads
+}) |> 
+  mutate(date = ymd(date)) |> 
+  rename(date_utc = date)
+
+# add new columns to our working data
+reddit_clean <- reddit_clean |> 
+  add_column(reddit_metadata |> 
+               select(score:cross_posts))
 ```
 
-#
+-   We can now create a dataframe of the comments from the list that we compiled above.
+
+```{r}
+reddit_comments <- map(reddit_content, function(x){
+
+  # pass the list element that houses comments
+  x$comments |> 
+    tibble() |> 
+    mutate_all(as.character)
+}
+) |> 
+  # ger rid of NULL, no comments
+  discard(is_null) |>
+  # put data in data frame structure
+  bind_rows() |> 
+  # remove duplicates
+  distinct() |> 
+  # retain variable types
+  mutate(
+    # remove URL links
+    comment = qdapRegex::rm_url(comment),
+    date = ymd(date), 
+    timestamp = as.double(timestamp),
+    # if no text in comment, code as NA
+    comment = na_if(comment, "")) |> 
+  rename(date_utc = date) |> 
+  filter(!is.na(comment),
+         # remove none related topic threads
+         !str_detect(comment, "crypto|coin"),#,
+         # drop text that are one or two words
+         str_count(comment, " ") >= 12
+  )
+
+```
+
+We want to do some additional cleaning to the posts dataset. Ideally, we want to remove empty or short text.
+
+```{r}
+reddit_clean <- reddit_clean |> 
+  mutate(text = na_if(text, "")) |> 
+   filter(!is.na(text),
+         # drop text that are one or two words
+         str_count(text, " ") >= 12
+  )
+
+```
+
+Finally, we check in two additional datasets into github, the posts, and the comments.
+
+```{r}
+# write posts data
+writexl::write_xlsx(reddit_clean, "D:/repos/SURV622_Assignment/data/posts_data_clean.xlsx")
+
+# write comments data
+writexl::write_xlsx(reddit_comments, "D:/repos/SURV622_Assignment/data/comments_data_clean.xlsx")
+
+```

### 2025-03-12 code/Reddit_API.qmd
added keyword search & subreddit columns to reddit_comments.xlsx
adding eda code

@@
 library(tidyverse)
-library(readxl)
 library(writexl)
@@
 
-    -   The effects of remove work policies.
+    -   The effects of remote work policies.
 
@@
 ```{r}
-reddit_unclean <- readRDS("D:/repos/SURV622_Assignment/data/posts_data.RDS")
+reddit_unclean <- readRDS("~/repos/SURV622_Assignment/data/posts_data.RDS")
 glimpse(reddit_unclean)
@@
 
+The comments are still missing subreddit and keyword search information. We will join this information from the reddit_clean data.
+
+```{r}
+reddit_comments <- reddit_comments |> 
+  left_join(
+    # select needed variables
+    reddit_clean |> 
+      select(url, subreddit, search_term),
+    relationship = "many-to-many"
+  )
+
+glimpse(reddit_comments)
+```
+
 We want to do some additional cleaning to the posts dataset. Ideally, we want to remove empty or short text.

### 2025-03-12 code/Reddit_eda.qmd
adding eda code

---
title: "Assignment 2"
author: Group 2
date: "`r format(Sys.time(), '%d %B, %Y')`"
embed-resources: true
editor: visual
execute:
  warning: false
  message: false
  error: false
  tidy: true
format: pdf
theme: spacelab
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(knitr)
library(fedmatch)
library(tidyverse)
library(readxl)
```

# We will explore the data we scraped to determine next steps for analysis.

1.  Read in data from github, and tidy it to continue processing.

```{r}
# posts data
reddit_posts <- read_xlsx(
  "~/repos/SURV622_Assignment/data/posts_data_clean.xlsx") |> 
  mutate(date_utc = ymd(date_utc)) |> 
  # remove variables not needed
  select(-timestamp)

# comments data
reddit_comment <- read_xlsx(
  "~/repos/SURV622_Assignment/data/comments_data_clean.xlsx") |> 
    mutate(date_utc = ymd(date_utc)) |> 
  # great unique post id
  arrange(date_utc) |> 
  group_by(url) |> 
  mutate(post_id = cur_group_id()) |> 
  ungroup() |> 
  # remove variables not needed
  select(-author, -timestamp, -comment_id)

# id url group IDs to the posts data
reddit_posts_2 <- reddit_posts |> 
  semi_join(reddit_comment |> select(url, post_id))

```

### The strings we will be processing sometimes have special characters, numbers, brackets. We need to clean these string for processing.

-   We can use the fedmatch::clean_strings() function to tidy up the text. The following is an example of what will be cleaned.

```{r}
# print example of posts
reddit_posts |> 
  slice(10:15) |> 
  select(text)

# clean posts
reddit_posts |> 
  slice(10:15) |> 
  mutate(text = clean_strings(text)) |> 
  select(text)

```

-   Clean posts and comment strings.

```{r}
reddit_posts <- reddit_posts |> 
  mutate(text = clean_strings(text))

reddit_comment <- reddit_comment |> 
  mutate(comment = clean_strings(comment))

reddit_posts_2 <- reddit_posts_2 |> 
  mutate(text=clean_strings(text))
```

\

### We can now begin to explore the data. First we explore the posts.

```{r, results = 'asis'}

  reddit_posts |>
  slice(364) |> 
  pull(text)

```

### 2025-03-13 code/Reddit_API.qmd
updated data

@@
 
-library(tidyverse)
 library(writexl)
+library(fedmatch)
 # install.packages("devtools")
@@
 library(RedditExtractoR)
+library(tidyverse)
+
 ```
@@
 reddit_unclean <- readRDS("~/repos/SURV622_Assignment/data/posts_data.RDS")
-glimpse(reddit_unclean)
+
 ```
@@
 This way we have almost \~900 posts after cleaning the found data set.
+-   Note.
+Some posts are related meaning that the more than one keyword may show up.
+Identify the duplicates, and just keep one.
+We don't really care for keyword search after this point, so we can drop it.
 
@@
 
-reddit_clean <- reddit_unclean |>
+reddit_post <- reddit_unclean |>
   # set timeline threshold 
-  filter(date_utc > "2025-02-25") |> 
+  filter(date_utc > "2025-03-01") |> 
   # function we created
    tibble() |> 
-    # remove any duplicates
-  distinct() |> 
    mutate(
@@
       text = qdapRegex::rm_url(text),
+      # clean text from unwanted character
+      text = clean_strings(text),
       date_utc = ymd(date_utc) ) |> 
    filter(# remove none related topic threads
-           !str_detect(text, "crypto|coin"))
+           !str_detect(text, "crypto|coin")) |> 
+  # drop duplicates
+  distinct_at(vars(-search_term, -comments))
 
-glimpse(reddit_clean)
+  # bring back search terms
+reddit_post <- reddit_post |> 
+  left_join(
+    reddit_unclean |> 
+      group_by(comments) |> 
+      filter(comments == max(comments)) |> 
+      group_by(url) |> 
+      mutate(id = row_number()) |> 
+      # keep first of x number of posts
+      filter(id==min(id)) |> 
+      select(url, search_term, comments)
+    )
+
 ```
@@
 # pass the urls collected from the post
-reddit_content <- map(reddit_clean$url, function(x){
+reddit_content <- map(seq_along(reddit_post$url), function(x){
 
-  thread = get_thread_content(x)
+  print(x)
+
+  thread = get_thread_content(reddit_post$url[x])
 
@@
 
--   Separate post metadata and merge as new columns into the clean reddit data set we extracted from our initial data collection.
+-   Separate post metadata and merge as new columns into the reddit posts data set we extracted from our initial data collection.
+-   We need a column that can join posts with comments. Currently, the URL column can do this but it is long. Let's assign a unique ID while enriching this dataset.
 
@@
 # add new columns to our working data
-reddit_clean <- reddit_clean |> 
+reddit_post <- reddit_post |> 
   add_column(reddit_metadata |> 
-               select(score:cross_posts))
+               select(score:cross_posts)) |> 
+  arrange(date_utc) |>
+  # assign IDs to posts
+  mutate(post_id = row_number())
 ```
@@
     comment = qdapRegex::rm_url(comment),
+    # clean comment strings
+    comment = clean_strings(comment),
     date = ymd(date), 
@@
     # select needed variables
-    reddit_clean |> 
-      select(url, subreddit, search_term),
-    relationship = "many-to-many"
+    reddit_post |> 
+      select(url, subreddit, search_term, post_id)
   )
@@
 glimpse(reddit_comments)
-```
-
-We want to do some additional cleaning to the posts dataset. Ideally, we want to remove empty or short text.
-
-```{r}
-reddit_clean <- reddit_clean |> 
-  mutate(text = na_if(text, "")) |> 
-   filter(!is.na(text),
-         # drop text that are one or two words
-         str_count(text, " ") >= 12
-  )
-
 ```
@@
 # write posts data
-writexl::write_xlsx(reddit_clean, "D:/repos/SURV622_Assignment/data/posts_data_clean.xlsx")
+writexl::write_xlsx(reddit_post, "~/repos/SURV622_Assignment/data/posts_data_clean.xlsx")
 
 # write comments data
-writexl::write_xlsx(reddit_comments, "D:/repos/SURV622_Assignment/data/comments_data_clean.xlsx")
+writexl::write_xlsx(reddit_comments, "~/repos/SURV622_Assignment/data/comments_data_clean.xlsx")
 

### 2025-03-13 code/Reddit_sentiment.qmd
adding sentiment analysis

---
title: "Assignment 2"
author: Group 2
date: "`r format(Sys.time(), '%d %B, %Y')`"
embed-resources: true
editor: visual
execute:
  warning: false
  message: false
  error: false
  tidy: true
format: pdf
theme: spacelab
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(writexl)
library(text)
library(readxl)
library(tidyverse)

```

We will explore sentiment analysis to give us an advantage in coding comments.

Read in data from github, and tidy it to continue processing.

```{r}

reddit_posts <- read_xlsx(
  "~/repos/repos/SURV622_Assignment/data/posts_data_clean.xlsx")

# comments data
reddit_comment <- read_xlsx(
  "~/repos/repos/SURV622_Assignment/data/comments_data_clean.xlsx")

```

We can use a model from huggingface to code each comment as positive, negative, or neutral.

We build a function that we will use to loop through comments and get scores.

```{r}
sentiment_score_fun <- function(comment_text){

  description = str_trunc(comment_text, 1600)

  # shorten descriptions to confirm to the model limitation

  # use huggingface model to detect emotional tone of summary
  mod = 
    textClassify(description,
                 model_info = "ProsusAI/finbert", 
                 return_all_scores = FALSE, 
                 return_incorrect_results = FALSE,
                 function_to_apply = "softmax",
                 tokenizer_parallelism = TRUE,
                 device = "gpu") |>   # change to "cpu" if a gpu is not configured
    pull(1)

  return(mod)

}
```

Loop the comments through our function.

```{r}
reddit_comment_new <- reddit_comment |> 
  mutate(label = ifelse(is.na(comment), NA, sentiment_score_fun(comment)))

```

```{r}
 reddit_comment_new |> count(label)
```

```{r}
 reddit_posts_new <- reddit_posts |> mutate(label = ifelse(is.na(text), NA, sentiment_score_fun(text)))
```

```{r}
 reddit_posts_new |> count(label)
```

```{r}
# write posts data
writexl::write_xlsx(reddit_posts_new, "~/repos/repos/SURV622_Assignment/data/posts_data_clean.xlsx")

# write comments data
writexl::write_xlsx(reddit_comment_new, "~/repos//repos/SURV622_Assignment/data/comments_data_clean.xlsx")

```

### 2025-03-13 code/Reddit_sentiment.qmd
adding data to hand code

@@
 reddit_posts <- read_xlsx(
-  "~/repos/repos/SURV622_Assignment/data/posts_data_clean.xlsx")
+  "~/repos/SURV622_Assignment/data/posts_data_clean.xlsx")
 
@@
 reddit_comment <- read_xlsx(
-  "~/repos/repos/SURV622_Assignment/data/comments_data_clean.xlsx")
+  "~/repos/SURV622_Assignment/data/comments_data_clean.xlsx")
 
@@
 ```{r}
- reddit_comment_new |> count(label)
-```
-
-```{r}
  reddit_posts_new <- reddit_posts |> mutate(label = ifelse(is.na(text), NA, sentiment_score_fun(text)))
@@
 
-```{r}
- reddit_posts_new |> count(label)
-```
+Add new column for hand coding (dis)approval
 
@@
 # write posts data
-writexl::write_xlsx(reddit_posts_new, "~/repos/repos/SURV622_Assignment/data/posts_data_clean.xlsx")
+write_xlsx(reddit_posts_new, "~/repos/SURV622_Assignment/data/posts_data_clean.xlsx")
 
 # write comments data
-writexl::write_xlsx(reddit_comment_new, "~/repos//repos/SURV622_Assignment/data/comments_data_clean.xlsx")
+write_xlsx(reddit_comment_new, "~/repos/SURV622_Assignment/data/comments_data_clean.xlsx")
 
 ```
+
+Separate out data for hand coding based on positive and negative scores for keyword searches rif, reduction in force, and fork in the road to concentrate comments on the topic of federal layoffs.
+Sample 400 comments without replacement from the negative and positive coded comments.
+
+```{r}
+sample_comments_dat <- reddit_comment |> 
+  filter(search_term %in% c("rif", "reduction in force", "fork in the road"),
+         label %in% c("positive", "negative")) |> 
+  #sample_n(size=400) |> 
+  mutate(outcome = NA)
+
+# group members
+group_members <-c("Kevin", 'Felix', "Aria", "Gloria")
+
+sample_comments_list <- infer::rep_slice_sample(sample_comments_dat, n=100, replace = FALSE, reps=4) |> 
+  group_by(replicate) |> 
+  group_split()
+
+walk(seq(1,4), function(x){
+
+  write_xlsx(# pass data from list
+    sample_comments_list[[x]] |> 
+      select(-replicate), 
+    # where to save, & how to name it
+    str_c(
+    "~/repos/SURV622_Assignment/data/comments_to_code/",
+    group_members[x], ".xlsx")
+  )
+})
+
+# write files to github by name
+
+```

### 2025-03-13 code/Reddit_eda.qmd
Added graphs to Reddit_eda.qmd

@@
 library(readxl)
+library(tidytext)
 ```
@@
 reddit_posts <- read_xlsx(
-  "~/repos/SURV622_Assignment/data/posts_data_clean.xlsx") |> 
+  # "~/repos/SURV622_Assignment/data/posts_data_clean.xlsx") |> path for Kevin
+  "~/Desktop/UMICH/SURV622_Assignment/data/posts_data_clean.xlsx") |> # path for Felix
   mutate(date_utc = ymd(date_utc)) |> 
@@
 reddit_comment <- read_xlsx(
-  "~/repos/SURV622_Assignment/data/comments_data_clean.xlsx") |> 
+  # "~/repos/SURV622_Assignment/data/comments_data_clean.xlsx") |> Kevin's path
+  "~/Desktop/UMICH/SURV622_Assignment/data/comments_data_clean.xlsx") |> # Felix's path
     mutate(date_utc = ymd(date_utc)) |> 
@@
 ```
+
+How many posts were collected in total and by day? How many posts after data cleaning? Is there a pattern with respect to the time of day or day of week when posts were created?
+```{r}
+# number of total posts
+totalposts <- reddit_posts %>%
+  summarize(
+    TotalPosts = n()
+  )
+knitr::kable(totalposts)
+
+# number of posts by day
+byday <- reddit_posts %>%
+  group_by(date_utc) %>%
+  summarize(
+    total = n()
+  )
+
+# plot
+ggplot(byday, aes(x = date_utc, y = total)) + 
+  geom_point(color = "blue", size = 3) +  # Larger points for visibility
+  geom_line(color = "steelblue", linewidth = 1) +  # Thicker line for clarity
+  labs(
+    title = "Total Number of Posts per Day",
+    x = "Day",
+    y = "Total Number of Posts"
+  ) +
+  theme_minimal()
+
+```
+
+Is there a relationship between events and frequency of tweets?
+
+The two peaks in our graph can potentially be attributed to these two major news stories on those days.
+On March 5, Elon talked about how he wishes to "save Western civilization from empathy".
+On March 6, President Trump was reported to further limit Elon Musk's authority amid backlash to DOGE cuts.
+These two events may have had a major impact in the number of Reddit posts related to DOGE and Elon.
+
+What are the words in the set of posts you have assembled that appear most frequently? 
+```{r}
+# tokenize words to count frequencies for reddit posts
+posts_word_counts <- reddit_posts |>
+  select(title, text) |>
+  pivot_longer(cols = c(title, text), values_drop_na = TRUE) |>
+  unnest_tokens(word, value) |>
+  count(word, sort = TRUE) |>
+  slice_max(n, n = 50)
+
+# plot
+ggplot(posts_word_counts, aes(x = reorder(word, n), y = n)) +
+  geom_col(fill = "steelblue") +
+  coord_flip() +
+  labs(title = "Top 50 Words in Reddit Posts (Including Stopwords)",
+       x = "Word",
+       y = "Count") +
+  theme_minimal()
+
+# tokenize words to count frequencies for reddit comments
+comments_word_counts <- reddit_comment |>
+  select(comment) |>
+  pivot_longer(cols = c(comment), values_drop_na = TRUE) |>
+  unnest_tokens(word, value) |>
+  count(word, sort = TRUE) |>
+  slice_max(n, n = 50)
+
+# plot
+ggplot(comments_word_counts, aes(x = reorder(word, n), y = n)) +
+  geom_col(fill = "lightgreen") +  # Removed extra parentheses
+  coord_flip() +
+  labs(title = "Top 50 Words in Reddit Comments (Including Stopwords)",
+       x = "Word",
+       y = "Count") +
+  theme_minimal()
+```
+
+The above graphs show the most frequent words in both reddit posts and their comments.
+Most of these are stopwords, therefore we will proceed to remove these to get a better idea of what people are really discussing.
+
+How does this change if you exclude “stop words” such as “a,” “an,” “the,” “is,” and others that are common in English sentences but are generally not informative?
+```{r}
+# tokenize words to count frequencies for reddit posts removing stop words
+posts_word_counts <- reddit_posts |>
+  select(title, text) |>
+  pivot_longer(cols = c(title, text), values_drop_na = TRUE) |>
+  unnest_tokens(word, value) |>
+  anti_join(stop_words, by = "word") |>
+  count(word, sort = TRUE) |>
+  slice_max(n, n = 50)
+
+# plot
+ggplot(posts_word_counts, aes(x = reorder(word, n), y = n)) +
+  geom_col(fill = "steelblue") +
+  coord_flip() +
+  labs(title = "Top 50 Words in Reddit Posts (Removing Stopwords)",
+       x = "Word",
+       y = "Count") +
+  theme_minimal()
+
+# tokenize words to count frequencies for Reddit comments, removing stop words
+comments_word_counts <- reddit_comment |>
+  select(comment) |>
+  pivot_longer(cols = c(comment), values_drop_na = TRUE) |>
+  unnest_tokens(word, value) |>
+  anti_join(stop_words, by = "word") |>
+  count(word, sort = TRUE) |>
+  slice_max(order_by = n, n = 50)
+
+# plot
+ggplot(comments_word_counts, aes(x = reorder(word, n), y = n)) +
+  geom_col(fill = "lightgreen") +  # Removed extra parentheses
+  coord_flip() +
+  labs(title = "Top 50 Words in Reddit Comments (Removing Stopwords)",
+       x = "Word",
+       y = "Count") +
+  theme_minimal()
+```
+
+The above graphs show the most frequent words used in both Reddit posts and their comment sections.
+We see that most of these are directly related to our topic, with mentions of the President, DOGE, the federal government and RIF.

### 2025-03-13 code/Reddit_eda.tex
Added graphs to Reddit_eda.qmd

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{241,243,245}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Assignment 2},
  pdfauthor={Group 2},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Assignment 2}
\author{Group 2}
\date{2025-03-13}

\begin{document}
\maketitle

\section{We will explore the data we scraped to determine next steps for
analysis.}\label{we-will-explore-the-data-we-scraped-to-determine-next-steps-for-analysis.}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Read in data from github, and tidy it to continue processing.
\end{enumerate}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# posts data}
\NormalTok{reddit\_posts }\OtherTok{\textless{}{-}} \FunctionTok{read\_xlsx}\NormalTok{(}
  \CommentTok{\# "\textasciitilde{}/repos/SURV622\_Assignment/data/posts\_data\_clean.xlsx") |\textgreater{} path for Kevin}
  \StringTok{"\textasciitilde{}/Desktop/UMICH/SURV622\_Assignment/data/posts\_data\_clean.xlsx"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} \CommentTok{\# path for Felix}
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{date\_utc =} \FunctionTok{ymd}\NormalTok{(date\_utc)) }\SpecialCharTok{|\textgreater{}} 
  \CommentTok{\# remove variables not needed}
  \FunctionTok{select}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{timestamp)}

\CommentTok{\# comments data}
\NormalTok{reddit\_comment }\OtherTok{\textless{}{-}} \FunctionTok{read\_xlsx}\NormalTok{(}
  \CommentTok{\# "\textasciitilde{}/repos/SURV622\_Assignment/data/comments\_data\_clean.xlsx") |\textgreater{} Kevin\textquotesingle{}s path}
  \StringTok{"\textasciitilde{}/Desktop/UMICH/SURV622\_Assignment/data/comments\_data\_clean.xlsx"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} \CommentTok{\# Felix\textquotesingle{}s path}
    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{date\_utc =} \FunctionTok{ymd}\NormalTok{(date\_utc)) }\SpecialCharTok{|\textgreater{}} 
  \CommentTok{\# great unique post id}
  \FunctionTok{arrange}\NormalTok{(date\_utc) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{group\_by}\NormalTok{(url) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{post\_id =} \FunctionTok{cur\_group\_id}\NormalTok{()) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{ungroup}\NormalTok{() }\SpecialCharTok{|\textgreater{}} 
  \CommentTok{\# remove variables not needed}
  \FunctionTok{select}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{author, }\SpecialCharTok{{-}}\NormalTok{timestamp, }\SpecialCharTok{{-}}\NormalTok{comment\_id) }

\CommentTok{\# id url group IDs to the posts data}
\NormalTok{reddit\_posts\_2 }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_posts }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{semi\_join}\NormalTok{(reddit\_comment }\SpecialCharTok{|\textgreater{}} \FunctionTok{select}\NormalTok{(url, post\_id)) }
\end{Highlighting}
\end{Shaded}

\subsubsection{The strings we will be processing sometimes have special
characters, numbers, brackets. We need to clean these string for
processing.}\label{the-strings-we-will-be-processing-sometimes-have-special-characters-numbers-brackets.-we-need-to-clean-these-string-for-processing.}

\begin{itemize}
\tightlist
\item
  We can use the fedmatch::clean\_strings() function to tidy up the
  text. The following is an example of what will be cleaned.
\end{itemize}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# print example of posts}
\NormalTok{reddit\_posts }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{slice}\NormalTok{(}\DecValTok{10}\SpecialCharTok{:}\DecValTok{15}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{select}\NormalTok{(text) }
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
# A tibble: 6 x 1
  text                                                                          
  <chr>                                                                         
1 <NA>                                                                          
2 <NA>                                                                          
3 <NA>                                                                          
4 <NA>                                                                          
5 <NA>                                                                          
6 commerce secretary howard lutnick said sunday that government spending could ~
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# clean posts}
\NormalTok{reddit\_posts }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{slice}\NormalTok{(}\DecValTok{10}\SpecialCharTok{:}\DecValTok{15}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{text =} \FunctionTok{clean\_strings}\NormalTok{(text)) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{select}\NormalTok{(text) }
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
# A tibble: 6 x 1
  text                                                                          
  <chr>                                                                         
1 <NA>                                                                          
2 <NA>                                                                          
3 <NA>                                                                          
4 <NA>                                                                          
5 <NA>                                                                          
6 commerce secretary howard lutnick said sunday that government spending could ~
\end{verbatim}

\begin{itemize}
\tightlist
\item
  Clean posts and comment strings.
\end{itemize}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{reddit\_posts }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_posts }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{text =} \FunctionTok{clean\_strings}\NormalTok{(text))}

\NormalTok{reddit\_comment }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_comment }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{comment =} \FunctionTok{clean\_strings}\NormalTok{(comment))}

\NormalTok{reddit\_posts\_2 }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_posts\_2 }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{text=}\FunctionTok{clean\_strings}\NormalTok{(text))}
\end{Highlighting}
\end{Shaded}

\hfill\break

\subsubsection{We can now begin to explore the data. First we explore
the
posts.}\label{we-can-now-begin-to-explore-the-data.-first-we-explore-the-posts.}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{  reddit\_posts }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{slice}\NormalTok{(}\DecValTok{364}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
  \FunctionTok{pull}\NormalTok{(text) }
\end{Highlighting}
\end{Shaded}

{[}1{]} ``hello all so i recently took the deferred resignation i was
working at the va and my job was not exempt i did not trust that my job
was safe even after coming off probation the day the fork in the road
came out i took the resignation and my last day was february 28 before i
started i was in the cwt program compensated work therapy i once again
have an opportunity to get back into the program i know we are allowed
to work while on the resignation but am i able to do the cwt because
both checks would be federal payments i don t want to lose out on the
resignation benefits just to make 12 hr but working does help me mental
health and give me a purpose any insight would be greatly appreciated''

How many posts were collected in total and by day? How many posts after
data cleaning? Is there a pattern with respect to the time of day or day
of week when posts were created?

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# number of total posts}
\NormalTok{totalposts }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_posts }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{summarize}\NormalTok{(}
    \AttributeTok{TotalPosts =} \FunctionTok{n}\NormalTok{()}
\NormalTok{  )}
\NormalTok{knitr}\SpecialCharTok{::}\FunctionTok{kable}\NormalTok{(totalposts)}
\end{Highlighting}
\end{Shaded}

\begin{longtable}[]{@{}r@{}}
\toprule\noalign{}
TotalPosts \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
557 \\
\end{longtable}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# number of posts by day}
\NormalTok{byday }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_posts }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{group\_by}\NormalTok{(date\_utc) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{summarize}\NormalTok{(}
    \AttributeTok{total =} \FunctionTok{n}\NormalTok{()}
\NormalTok{  )}

\CommentTok{\# plot}
\FunctionTok{ggplot}\NormalTok{(byday, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ date\_utc, }\AttributeTok{y =}\NormalTok{ total)) }\SpecialCharTok{+} 
  \FunctionTok{geom\_point}\NormalTok{(}\AttributeTok{color =} \StringTok{"blue"}\NormalTok{, }\AttributeTok{size =} \DecValTok{3}\NormalTok{) }\SpecialCharTok{+}  \CommentTok{\# Larger points for visibility}
  \FunctionTok{geom\_line}\NormalTok{(}\AttributeTok{color =} \StringTok{"steelblue"}\NormalTok{, }\AttributeTok{linewidth =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{+}  \CommentTok{\# Thicker line for clarity}
  \FunctionTok{labs}\NormalTok{(}
    \AttributeTok{title =} \StringTok{"Total Number of Posts per Day"}\NormalTok{,}
    \AttributeTok{x =} \StringTok{"Day"}\NormalTok{,}
    \AttributeTok{y =} \StringTok{"Total Number of Posts"}
\NormalTok{  ) }\SpecialCharTok{+}
  \FunctionTok{theme\_minimal}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\includegraphics{Reddit_eda_files/figure-pdf/unnamed-chunk-5-1.pdf}

Is there a relationship between events and frequency of tweets?

The two peaks in our graph can potentially be attributed to these two
major news stories on those days. On March 5, Elon talked about how he
wishes to ``save Western civilization from empathy''. On March 6,
President Trump was reported to further limit Elon Musk's authority amid
backlash to DOGE cuts. These two events may have had a major impact in
the number of Reddit posts related to DOGE and Elon.

What are the words in the set of posts you have assembled that appear
most frequently?

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# tokenize words to count frequencies for reddit posts}
\NormalTok{posts\_word\_counts }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_posts }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{select}\NormalTok{(title, text) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{pivot\_longer}\NormalTok{(}\AttributeTok{cols =} \FunctionTok{c}\NormalTok{(title, text), }\AttributeTok{values\_drop\_na =} \ConstantTok{TRUE}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{unnest\_tokens}\NormalTok{(word, value) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{count}\NormalTok{(word, }\AttributeTok{sort =} \ConstantTok{TRUE}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{slice\_max}\NormalTok{(n, }\AttributeTok{n =} \DecValTok{50}\NormalTok{)}

\CommentTok{\# plot}
\FunctionTok{ggplot}\NormalTok{(posts\_word\_counts, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =} \FunctionTok{reorder}\NormalTok{(word, n), }\AttributeTok{y =}\NormalTok{ n)) }\SpecialCharTok{+}
  \FunctionTok{geom\_col}\NormalTok{(}\AttributeTok{fill =} \StringTok{"steelblue"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{coord\_flip}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Top 50 Words in Reddit Posts (Including Stopwords)"}\NormalTok{,}
       \AttributeTok{x =} \StringTok{"Word"}\NormalTok{,}
       \AttributeTok{y =} \StringTok{"Count"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{theme\_minimal}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\includegraphics{Reddit_eda_files/figure-pdf/unnamed-chunk-6-1.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# tokenize words to count frequencies for reddit comments}
\NormalTok{comments\_word\_counts }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_comment }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{select}\NormalTok{(comment) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{pivot\_longer}\NormalTok{(}\AttributeTok{cols =} \FunctionTok{c}\NormalTok{(comment), }\AttributeTok{values\_drop\_na =} \ConstantTok{TRUE}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{unnest\_tokens}\NormalTok{(word, value) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{count}\NormalTok{(word, }\AttributeTok{sort =} \ConstantTok{TRUE}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{slice\_max}\NormalTok{(n, }\AttributeTok{n =} \DecValTok{50}\NormalTok{)}

\CommentTok{\# plot}
\FunctionTok{ggplot}\NormalTok{(comments\_word\_counts, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =} \FunctionTok{reorder}\NormalTok{(word, n), }\AttributeTok{y =}\NormalTok{ n)) }\SpecialCharTok{+}
  \FunctionTok{geom\_col}\NormalTok{(}\AttributeTok{fill =} \StringTok{"lightgreen"}\NormalTok{) }\SpecialCharTok{+}  \CommentTok{\# Removed extra parentheses}
  \FunctionTok{coord\_flip}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Top 50 Words in Reddit Comments (Including Stopwords)"}\NormalTok{,}
       \AttributeTok{x =} \StringTok{"Word"}\NormalTok{,}
       \AttributeTok{y =} \StringTok{"Count"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{theme\_minimal}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\includegraphics{Reddit_eda_files/figure-pdf/unnamed-chunk-6-2.pdf}

The above graphs show the most frequent words in both reddit posts and
their comments. Most of these are stopwords, therefore we will proceed
to remove these to get a better idea of what people are really
discussing.

How does this change if you exclude ``stop words'' such as ``a,''
``an,'' ``the,'' ``is,'' and others that are common in English sentences
but are generally not informative?

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# tokenize words to count frequencies for reddit posts removing stop words}
\NormalTok{posts\_word\_counts }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_posts }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{select}\NormalTok{(title, text) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{pivot\_longer}\NormalTok{(}\AttributeTok{cols =} \FunctionTok{c}\NormalTok{(title, text), }\AttributeTok{values\_drop\_na =} \ConstantTok{TRUE}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{unnest\_tokens}\NormalTok{(word, value) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{anti\_join}\NormalTok{(stop\_words, }\AttributeTok{by =} \StringTok{"word"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{count}\NormalTok{(word, }\AttributeTok{sort =} \ConstantTok{TRUE}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{slice\_max}\NormalTok{(n, }\AttributeTok{n =} \DecValTok{50}\NormalTok{)}

\CommentTok{\# plot}
\FunctionTok{ggplot}\NormalTok{(posts\_word\_counts, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =} \FunctionTok{reorder}\NormalTok{(word, n), }\AttributeTok{y =}\NormalTok{ n)) }\SpecialCharTok{+}
  \FunctionTok{geom\_col}\NormalTok{(}\AttributeTok{fill =} \StringTok{"steelblue"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{coord\_flip}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Top 50 Words in Reddit Posts (Removing Stopwords)"}\NormalTok{,}
       \AttributeTok{x =} \StringTok{"Word"}\NormalTok{,}
       \AttributeTok{y =} \StringTok{"Count"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{theme\_minimal}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\includegraphics{Reddit_eda_files/figure-pdf/unnamed-chunk-7-1.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# tokenize words to count frequencies for Reddit comments, removing stop words}
\NormalTok{comments\_word\_counts }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_comment }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{select}\NormalTok{(comment) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{pivot\_longer}\NormalTok{(}\AttributeTok{cols =} \FunctionTok{c}\NormalTok{(comment), }\AttributeTok{values\_drop\_na =} \ConstantTok{TRUE}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{unnest\_tokens}\NormalTok{(word, value) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{anti\_join}\NormalTok{(stop\_words, }\AttributeTok{by =} \StringTok{"word"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{count}\NormalTok{(word, }\AttributeTok{sort =} \ConstantTok{TRUE}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
  \FunctionTok{slice\_max}\NormalTok{(}\AttributeTok{order\_by =}\NormalTok{ n, }\AttributeTok{n =} \DecValTok{50}\NormalTok{)}

\CommentTok{\# plot}
\FunctionTok{ggplot}\NormalTok{(comments\_word\_counts, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =} \FunctionTok{reorder}\NormalTok{(word, n), }\AttributeTok{y =}\NormalTok{ n)) }\SpecialCharTok{+}
  \FunctionTok{geom\_col}\NormalTok{(}\AttributeTok{fill =} \StringTok{"lightgreen"}\NormalTok{) }\SpecialCharTok{+}  \CommentTok{\# Removed extra parentheses}
  \FunctionTok{coord\_flip}\NormalTok{() }\SpecialCharTok{+}
  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Top 50 Words in Reddit Comments (Removing Stopwords)"}\NormalTok{,}
       \AttributeTok{x =} \StringTok{"Word"}\NormalTok{,}
       \AttributeTok{y =} \StringTok{"Count"}\NormalTok{) }\SpecialCharTok{+}
  \FunctionTok{theme\_minimal}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

\includegraphics{Reddit_eda_files/figure-pdf/unnamed-chunk-7-2.pdf}

The above graphs show the most frequent words used in both Reddit posts
and their comment sections. We see that most of these are directly
related to our topic, with mentions of the President, the federal
government, DOGE and RIF.

\end{document}

### 2025-03-14 code/Reddit_eda.qmd
Added interpretations to analysis graphs

@@
   # remove variables not needed
-  select(-timestamp)
+  # select(-timestamp)
+  mutate(
+    # Convert timestamp to POSIXct format
+    timestamp = as.POSIXct(timestamp, origin = "1970-01-01", tz = "UTC"),
+
+    # Extract time of day (you can adjust the format as needed)
+    time_of_day = format(timestamp, "%H:%M:%S")
+  )
 
@@
   # remove variables not needed
-  select(-author, -timestamp, -comment_id)
+  mutate(
+    # Convert timestamp to POSIXct format
+    timestamp = as.POSIXct(timestamp, origin = "1970-01-01", tz = "UTC"),
+
+    # Extract time of day (you can adjust the format as needed)
+    time_of_day = format(timestamp, "%H:%M:%S")
+  ) |>
+  select(-author, -comment_id)
 
@@
 
-How many posts were collected in total and by day? How many posts after data cleaning? Is there a pattern with respect to the time of day or day of week when posts were created?
+## How many posts were collected in total and by day?
+How many posts after data cleaning?
+Is there a pattern with respect to the time of day or day of week when posts were created?
+Is there a relationship between events and frequency of tweets?
 ```{r}
@@
 # number of posts by day
-byday <- reddit_posts %>%
+byday_posts <- reddit_posts %>%
   group_by(date_utc) %>%
@@
 # plot
-ggplot(byday, aes(x = date_utc, y = total)) + 
-  geom_point(color = "blue", size = 3) +  # Larger points for visibility
-  geom_line(color = "steelblue", linewidth = 1) +  # Thicker line for clarity
+ggplot(byday_posts, aes(x = date_utc, y = total)) + 
+  geom_point(color = "blue", size = 3) +  
+  geom_line(color = "steelblue", linewidth = 1) +  
   labs(
@@
 
+# number of total comments
+totalcomments <- reddit_comment %>%
+  summarize(
+    TotalComments = n()
+  )
+knitr::kable(totalcomments)
+
+# number of comments by day
+byday_comments <- reddit_comment %>%
+  group_by(date_utc) %>%
+  summarize(
+    total = n()
+  )
+
+# plot
+ggplot(byday_comments, aes(x = date_utc, y = total)) + 
+  geom_point(color = "green", size = 3) +  
+  geom_line(color = "lightgreen", linewidth = 1) +
+  labs(
+    title = "Total Number of Posts per Day",
+    x = "Day",
+    y = "Total Number of Posts"
+  ) +
+  theme_minimal()
 ```
 
-Is there a relationship between events and frequency of tweets?
+There appears to be a noticeable peak in activity during the middle of the week.
+However, we don't have enough data to conclusively say it's due to the day of the week itself.
+It's more likely that these spikes are linked to specific events that occurred on those days, which sparked conversations.
 
-The two peaks in our graph can potentially be attributed to these two major news stories on those days.
-On March 5, Elon talked about how he wishes to "save Western civilization from empathy".
-On March 6, President Trump was reported to further limit Elon Musk's authority amid backlash to DOGE cuts.
-These two events may have had a major impact in the number of Reddit posts related to DOGE and Elon.
+The two peaks in our graph could be attributed to two major news stories.
+On March 5, Elon Musk made a statement about wanting to "save Western civilization from empathy," and on March 6, there were reports that President Trump was limiting Musk's authority due to backlash over cuts to DOGE.
+These events likely had a significant impact on the volume of Reddit posts related to Elon Musk and DOGE, driving the observed spikes in activity.
 
-What are the words in the set of posts you have assembled that appear most frequently? 
+```{r}
+# Number of posts by time of day (hour)
+byhour_posts <- reddit_posts %>%
+  mutate(hour_of_day = hour(timestamp)) %>%
+  group_by(hour_of_day) %>%
+  summarize(total = n())
+
+# Plot number of posts by hour of day
+ggplot(byhour_posts, aes(x = hour_of_day, y = total)) + 
+  # geom_bar(stat = "identity", fill = "steelblue") + 
+  geom_point(color = "blue", size = 3) +  
+  geom_line(color = "steelblue", linewidth = 1) +
+  labs(
+    title = "Total Number of Posts by Hour of Day (24-hour clock)",
+    x = "Hour of Day",
+    y = "Total Number of Posts"
+  ) +
+  theme_minimal()
+
+# Number of comments by time of day (hour)
+byhour_comments <- reddit_comment %>%
+  mutate(hour_of_day = hour(timestamp)) %>%
+  group_by(hour_of_day) %>%
+  summarize(total = n())
+
+# Plot number of posts by hour of day
+ggplot(byhour_comments, aes(x = hour_of_day, y = total)) + 
+  # geom_bar(stat = "identity", fill = "lightgreen") + 
+  geom_point(color = "green", size = 3) +  
+  geom_line(color = "lightgreen", linewidth = 1) +
+  labs(
+    title = "Total Number of Comments by Hour of Day (24-hour clock)",
+    x = "Hour of Day",
+    y = "Total Number of Posts"
+  ) +
+  theme_minimal()
+```
+
+Most posts occur during the early morning, noon, and afternoon hours.
+The highest peak is around lunchtime, likely due to people posting during their lunch break.
+There is also significant activity in the afternoon, evening, and early morning.
+This could be because people have more free time or stay up late, allowing them to take the time to write posts, which require more effort than quick interactions.
+The fewest posts are seen in the morning, which makes sense as people are typically getting ready for work, commuting, or sleeping in.
+
+The trend for comments mirrors that of posts.
+This makes sense because people are likely using Reddit at similar times for both posting and commenting.
+However, the volume of comments is much higher than the number of posts, as each post receives many comments from different users.
+
+## What are the words in the set of posts you have assembled that appear most frequently? 
 ```{r}
@@
 
-The above graphs show the most frequent words in both reddit posts and their comments.
-Most of these are stopwords, therefore we will proceed to remove these to get a better idea of what people are really discussing.
+The graphs above show the most frequent words in both Reddit posts and their comments.
+However, many of these words are stopwords, which don't provide much insight into the actual content of the discussions.
+To get a better understanding of what people are really talking about, we will remove these stopwords in the next step.
 
-How does this change if you exclude “stop words” such as “a,” “an,” “the,” “is,” and others that are common in English sentences but are generally not informative?
+## How does this change if you exclude “stop words” such as “a,” “an,” “the,” “is,” and others that are common in English sentences but are generally not informative?
 ```{r}
@@
 
-The above graphs show the most frequent words used in both Reddit posts and their comment sections.
-We see that most of these are directly related to our topic, with mentions of the President, DOGE, the federal government and RIF.
+The graphs above show the most frequent words used in both Reddit posts and their comment sections.
+We can see that many of these words are directly related to our topic, with frequent mentions of the President, DOGE, the federal government, and RIF.

### 2025-03-14 code/Reddit_eda.tex
Added interpretations to analysis graphs

@@
   \CommentTok{\# remove variables not needed}
-  \FunctionTok{select}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{timestamp)}
+  \CommentTok{\# select({-}timestamp)}
+  \FunctionTok{mutate}\NormalTok{(}
+    \CommentTok{\# Convert timestamp to POSIXct format}
+    \AttributeTok{timestamp =} \FunctionTok{as.POSIXct}\NormalTok{(timestamp, }\AttributeTok{origin =} \StringTok{"1970{-}01{-}01"}\NormalTok{, }\AttributeTok{tz =} \StringTok{"UTC"}\NormalTok{),}
+
+    \CommentTok{\# Extract time of day (you can adjust the format as needed)}
+    \AttributeTok{time\_of\_day =} \FunctionTok{format}\NormalTok{(timestamp, }\StringTok{"\%H:\%M:\%S"}\NormalTok{)}
+\NormalTok{  )}
 
@@
   \CommentTok{\# remove variables not needed}
-  \FunctionTok{select}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{author, }\SpecialCharTok{{-}}\NormalTok{timestamp, }\SpecialCharTok{{-}}\NormalTok{comment\_id) }
+  \FunctionTok{mutate}\NormalTok{(}
+    \CommentTok{\# Convert timestamp to POSIXct format}
+    \AttributeTok{timestamp =} \FunctionTok{as.POSIXct}\NormalTok{(timestamp, }\AttributeTok{origin =} \StringTok{"1970{-}01{-}01"}\NormalTok{, }\AttributeTok{tz =} \StringTok{"UTC"}\NormalTok{),}
+
+    \CommentTok{\# Extract time of day (you can adjust the format as needed)}
+    \AttributeTok{time\_of\_day =} \FunctionTok{format}\NormalTok{(timestamp, }\StringTok{"\%H:\%M:\%S"}\NormalTok{)}
+\NormalTok{  ) }\SpecialCharTok{|\textgreater{}}
+  \FunctionTok{select}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{author, }\SpecialCharTok{{-}}\NormalTok{comment\_id) }
 
@@
 
-How many posts were collected in total and by day? How many posts after
-data cleaning? Is there a pattern with respect to the time of day or day
-of week when posts were created?
+\subsection{How many posts were collected in total and by day? How many
+posts after data cleaning? Is there a pattern with respect to the time
+of day or day of week when posts were created? Is there a relationship
+between events and frequency of
+tweets?}\label{how-many-posts-were-collected-in-total-and-by-day-how-many-posts-after-data-cleaning-is-there-a-pattern-with-respect-to-the-time-of-day-or-day-of-week-when-posts-were-created-is-there-a-relationship-between-events-and-frequency-of-tweets}
 
@@
 \CommentTok{\# number of posts by day}
-\NormalTok{byday }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_posts }\SpecialCharTok{\%\textgreater{}\%}
+\NormalTok{byday\_posts }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_posts }\SpecialCharTok{\%\textgreater{}\%}
   \FunctionTok{group\_by}\NormalTok{(date\_utc) }\SpecialCharTok{\%\textgreater{}\%}
@@
 \CommentTok{\# plot}
-\FunctionTok{ggplot}\NormalTok{(byday, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ date\_utc, }\AttributeTok{y =}\NormalTok{ total)) }\SpecialCharTok{+} 
-  \FunctionTok{geom\_point}\NormalTok{(}\AttributeTok{color =} \StringTok{"blue"}\NormalTok{, }\AttributeTok{size =} \DecValTok{3}\NormalTok{) }\SpecialCharTok{+}  \CommentTok{\# Larger points for visibility}
-  \FunctionTok{geom\_line}\NormalTok{(}\AttributeTok{color =} \StringTok{"steelblue"}\NormalTok{, }\AttributeTok{linewidth =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{+}  \CommentTok{\# Thicker line for clarity}
+\FunctionTok{ggplot}\NormalTok{(byday\_posts, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ date\_utc, }\AttributeTok{y =}\NormalTok{ total)) }\SpecialCharTok{+} 
+  \FunctionTok{geom\_point}\NormalTok{(}\AttributeTok{color =} \StringTok{"blue"}\NormalTok{, }\AttributeTok{size =} \DecValTok{3}\NormalTok{) }\SpecialCharTok{+}  
+  \FunctionTok{geom\_line}\NormalTok{(}\AttributeTok{color =} \StringTok{"steelblue"}\NormalTok{, }\AttributeTok{linewidth =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{+}  
   \FunctionTok{labs}\NormalTok{(}
@@
 
-Is there a relationship between events and frequency of tweets?
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# number of total comments}
+\NormalTok{totalcomments }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_comment }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{summarize}\NormalTok{(}
+    \AttributeTok{TotalPosts =} \FunctionTok{n}\NormalTok{()}
+\NormalTok{  )}
+\NormalTok{knitr}\SpecialCharTok{::}\FunctionTok{kable}\NormalTok{(totalcomments)}
+\end{Highlighting}
+\end{Shaded}
 
-The two peaks in our graph can potentially be attributed to these two
-major news stories on those days. On March 5, Elon talked about how he
-wishes to ``save Western civilization from empathy''. On March 6,
-President Trump was reported to further limit Elon Musk's authority amid
-backlash to DOGE cuts. These two events may have had a major impact in
-the number of Reddit posts related to DOGE and Elon.
+\begin{longtable}[]{@{}r@{}}
+\toprule\noalign{}
+TotalPosts \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+12492 \\
+\end{longtable}
 
-What are the words in the set of posts you have assembled that appear
-most frequently?
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# number of comments by day}
+\NormalTok{byday\_comments }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_comment }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{group\_by}\NormalTok{(date\_utc) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{summarize}\NormalTok{(}
+    \AttributeTok{total =} \FunctionTok{n}\NormalTok{()}
+\NormalTok{  )}
+
+\CommentTok{\# plot}
+\FunctionTok{ggplot}\NormalTok{(byday\_comments, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ date\_utc, }\AttributeTok{y =}\NormalTok{ total)) }\SpecialCharTok{+} 
+  \FunctionTok{geom\_point}\NormalTok{(}\AttributeTok{color =} \StringTok{"green"}\NormalTok{, }\AttributeTok{size =} \DecValTok{3}\NormalTok{) }\SpecialCharTok{+}  
+  \FunctionTok{geom\_line}\NormalTok{(}\AttributeTok{color =} \StringTok{"lightgreen"}\NormalTok{, }\AttributeTok{linewidth =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}
+    \AttributeTok{title =} \StringTok{"Total Number of Posts per Day"}\NormalTok{,}
+    \AttributeTok{x =} \StringTok{"Day"}\NormalTok{,}
+    \AttributeTok{y =} \StringTok{"Total Number of Posts"}
+\NormalTok{  ) }\SpecialCharTok{+}
+  \FunctionTok{theme\_minimal}\NormalTok{()}
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics{Reddit_eda_files/figure-pdf/unnamed-chunk-5-2.pdf}
+
+There appears to be a noticeable peak in activity during the middle of
+the week. However, we don't have enough data to conclusively say it's
+due to the day of the week itself. It's more likely that these spikes
+are linked to specific events that occurred on those days, which sparked
+conversations.
+
+The two peaks in our graph could be attributed to two major news
+stories. On March 5, Elon Musk made a statement about wanting to ``save
+Western civilization from empathy,'' and on March 6, there were reports
+that President Trump was limiting Musk's authority due to backlash over
+cuts to DOGE. These events likely had a significant impact on the volume
+of Reddit posts related to Elon Musk and DOGE, driving the observed
+spikes in activity.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# Number of posts by time of day (hour)}
+\NormalTok{byhour\_posts }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_posts }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{hour\_of\_day =} \FunctionTok{hour}\NormalTok{(timestamp)) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{group\_by}\NormalTok{(hour\_of\_day) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{summarize}\NormalTok{(}\AttributeTok{total =} \FunctionTok{n}\NormalTok{())}
+
+\CommentTok{\# Plot number of posts by hour of day}
+\FunctionTok{ggplot}\NormalTok{(byhour\_posts, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ hour\_of\_day, }\AttributeTok{y =}\NormalTok{ total)) }\SpecialCharTok{+} 
+  \CommentTok{\# geom\_bar(stat = "identity", fill = "steelblue") + }
+  \FunctionTok{geom\_point}\NormalTok{(}\AttributeTok{color =} \StringTok{"blue"}\NormalTok{, }\AttributeTok{size =} \DecValTok{3}\NormalTok{) }\SpecialCharTok{+}  
+  \FunctionTok{geom\_line}\NormalTok{(}\AttributeTok{color =} \StringTok{"steelblue"}\NormalTok{, }\AttributeTok{linewidth =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}
+    \AttributeTok{title =} \StringTok{"Total Number of Posts by Hour of Day (24{-}hour clock)"}\NormalTok{,}
+    \AttributeTok{x =} \StringTok{"Hour of Day"}\NormalTok{,}
+    \AttributeTok{y =} \StringTok{"Total Number of Posts"}
+\NormalTok{  ) }\SpecialCharTok{+}
+  \FunctionTok{theme\_minimal}\NormalTok{()}
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics{Reddit_eda_files/figure-pdf/unnamed-chunk-6-1.pdf}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# Number of comments by time of day (hour)}
+\NormalTok{byhour\_comments }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_comment }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{hour\_of\_day =} \FunctionTok{hour}\NormalTok{(timestamp)) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{group\_by}\NormalTok{(hour\_of\_day) }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{summarize}\NormalTok{(}\AttributeTok{total =} \FunctionTok{n}\NormalTok{())}
+
+\CommentTok{\# Plot number of posts by hour of day}
+\FunctionTok{ggplot}\NormalTok{(byhour\_comments, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ hour\_of\_day, }\AttributeTok{y =}\NormalTok{ total)) }\SpecialCharTok{+} 
+  \CommentTok{\# geom\_bar(stat = "identity", fill = "lightgreen") + }
+  \FunctionTok{geom\_point}\NormalTok{(}\AttributeTok{color =} \StringTok{"green"}\NormalTok{, }\AttributeTok{size =} \DecValTok{3}\NormalTok{) }\SpecialCharTok{+}  
+  \FunctionTok{geom\_line}\NormalTok{(}\AttributeTok{color =} \StringTok{"lightgreen"}\NormalTok{, }\AttributeTok{linewidth =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{+}
+  \FunctionTok{labs}\NormalTok{(}
+    \AttributeTok{title =} \StringTok{"Total Number of Comments by Hour of Day (24{-}hour clock)"}\NormalTok{,}
+    \AttributeTok{x =} \StringTok{"Hour of Day"}\NormalTok{,}
+    \AttributeTok{y =} \StringTok{"Total Number of Posts"}
+\NormalTok{  ) }\SpecialCharTok{+}
+  \FunctionTok{theme\_minimal}\NormalTok{()}
+\end{Highlighting}
+\end{Shaded}
+
+\includegraphics{Reddit_eda_files/figure-pdf/unnamed-chunk-6-2.pdf}
+
+Most posts occur during the early morning, noon, and afternoon hours.
+The highest peak is around lunchtime, likely due to people posting
+during their lunch break. There is also significant activity in the
+afternoon, evening, and early morning. This could be because people have
+more free time or stay up late, allowing them to take the time to write
+posts, which require more effort than quick interactions. The fewest
+posts are seen in the morning, which makes sense as people are typically
+getting ready for work, commuting, or sleeping in.
+
+The trend for comments mirrors that of posts. This makes sense because
+people are likely using Reddit at similar times for both posting and
+commenting. However, the volume of comments is much higher than the
+number of posts, as each post receives many comments from different
+users.
+
+\subsection{What are the words in the set of posts you have assembled
+that appear most
+frequently?}\label{what-are-the-words-in-the-set-of-posts-you-have-assembled-that-appear-most-frequently}
 
@@
 
-\includegraphics{Reddit_eda_files/figure-pdf/unnamed-chunk-6-1.pdf}
+\includegraphics{Reddit_eda_files/figure-pdf/unnamed-chunk-7-1.pdf}
 
@@
 
-\includegraphics{Reddit_eda_files/figure-pdf/unnamed-chunk-6-2.pdf}
+\includegraphics{Reddit_eda_files/figure-pdf/unnamed-chunk-7-2.pdf}
 
-The above graphs show the most frequent words in both reddit posts and
-their comments. Most of these are stopwords, therefore we will proceed
-to remove these to get a better idea of what people are really
-discussing.
+The graphs above show the most frequent words in both Reddit posts and
+their comments. However, many of these words are stopwords, which don't
+provide much insight into the actual content of the discussions. To get
+a better understanding of what people are really talking about, we will
+remove these stopwords in the next step.
 
-How does this change if you exclude ``stop words'' such as ``a,''
-``an,'' ``the,'' ``is,'' and others that are common in English sentences
-but are generally not informative?
+\subsection{How does this change if you exclude ``stop words'' such as
+``a,'' ``an,'' ``the,'' ``is,'' and others that are common in English
+sentences but are generally not
+informative?}\label{how-does-this-change-if-you-exclude-stop-words-such-as-a-an-the-is-and-others-that-are-common-in-english-sentences-but-are-generally-not-informative}
 
@@
 
-\includegraphics{Reddit_eda_files/figure-pdf/unnamed-chunk-7-1.pdf}
+\includegraphics{Reddit_eda_files/figure-pdf/unnamed-chunk-8-1.pdf}
 
@@
 
-\includegraphics{Reddit_eda_files/figure-pdf/unnamed-chunk-7-2.pdf}
+\includegraphics{Reddit_eda_files/figure-pdf/unnamed-chunk-8-2.pdf}
 
-The above graphs show the most frequent words used in both Reddit posts
-and their comment sections. We see that most of these are directly
-related to our topic, with mentions of the President, the federal
-government, DOGE and RIF.
+The graphs above show the most frequent words used in both Reddit posts
+and their comment sections. We can see that many of these words are
+directly related to our topic, with frequent mentions of the President,
+DOGE, the federal government, and RIF.
 

### 2025-03-14 code/Reddit_eda.qmd
cleaned eda file

--- 2025-03-12 code/Reddit_eda.qmd
@@
 
+library(readxl)
+library(viridis)
+library(ggthemes)
+library(tidytext)
 library(knitr)
-library(fedmatch)
 library(tidyverse)
-library(readxl)
+
 ```
 
-# We will explore the data we scraped to determine next steps for analysis.
+# We will explore the data we scraped to determine next steps for analysis examining both posts and comments related to these posts.
 
@@
 
-```{r}
-# posts data
-reddit_posts <- read_xlsx(
-  "~/repos/SURV622_Assignment/data/posts_data_clean.xlsx") |> 
-  mutate(date_utc = ymd(date_utc)) |> 
-  # remove variables not needed
-  select(-timestamp)
+```{r, message=FALSE}
 
-# comments data
-reddit_comment <- read_xlsx(
-  "~/repos/SURV622_Assignment/data/comments_data_clean.xlsx") |> 
-    mutate(date_utc = ymd(date_utc)) |> 
-  # great unique post id
-  arrange(date_utc) |> 
-  group_by(url) |> 
-  mutate(post_id = cur_group_id()) |> 
-  ungroup() |> 
-  # remove variables not needed
-  select(-author, -timestamp, -comment_id)
+# path to repo
+#repo_path <- str_c(~/Desktop/UMICH/SURV622_Assignment/data/") # felix
+repo_path <- str_c("~/repos/SURV622_Assignment/data/") # kevin
 
-# id url group IDs to the posts data
-reddit_posts_2 <- reddit_posts |> 
-  semi_join(reddit_comment |> select(url, post_id))
+data_files <- list.files(repo_path) |> 
+  tibble() |> 
+  rename(data_file_names = 1) |> 
+  filter(str_detect(data_file_names, ".xlsx|.RDS")) |> 
+  mutate(data_names = str_remove_all(data_file_names, "\\..*"))
+
+list2env(
+  map(data_files$data_file_names, function(x){
+
+  # read data file
+  if(str_detect(x, ".xlsx")) {
+    dat = read_xlsx(str_c(repo_path, x))
+  } else(
+    dat = readRDS(str_c(repo_path, x)) 
+  )
+
+  # manipualte variables
+  dat = dat |> 
+     mutate(date_utc = ymd(date_utc),
+    hour_posted = hour(as_datetime(timestamp)),
+  )
+
+}) |> 
+  # name the files
+    set_names(data_files$data_names),
+
+# save data to the global environment
+globalenv()
+)
 
@@
 
-### The strings we will be processing sometimes have special characters, numbers, brackets. We need to clean these string for processing.
+###
 
--   We can use the fedmatch::clean_strings() function to tidy up the text. The following is an example of what will be cleaned.
+## How many posts were collected in total and by day before and after processing/cleaning?
+
+-   There appears to be a noticeable peak in activity during the middle of the week.
+However, we don't have enough data to conclusively say it's due to the day of the week itself.
+It's more likely that these spikes are linked to specific events that occurred on those days, which sparked conversations.
+-   The two peaks in our graph could be attributed to two major news stories.
+On March 5, Elon Musk made a statement about wanting to "save Western civilization from empathy," and on March 6, there were reports that President Trump was limiting Musk's authority due to backlash over cuts to DOGE.
+These events likely had a significant impact on the volume of Reddit posts related to Elon Musk and DOGE, driving the observed spikes in activity.
+-   On May third, news outlets started reporting that DOGE was claiming \$105 billion dollars in savings from cutting "wasteful" spending by layoffs and cutting foreign aid.
+This amount is controversial since since the receipts shown on their site only amount to less than \$9.6 billion [https://abcnews.go.com/US/doge-website-now-saved-105-billion-backtracked-earlier/story?id=119408347](#0).
+This could have prompted reddit users to take to subreddits and provide their opinion or thoughts on this matter.
 
 ```{r}
-# print example of posts
-reddit_posts |> 
-  slice(10:15) |> 
-  select(text)
+# number of total posts
+total_posts <- posts_data |> 
+  filter(date_utc > "2025-03-01") |> 
+  group_by(date_utc) |> 
+  reframe(total = n()) |> 
+  mutate(Posts = "pre processing") |> 
+  add_row(
+    posts_data_clean |> 
+  group_by(date_utc) |> 
+  reframe(total = n()) |> 
+  mutate(Posts = "post processing")
+  )
 
-# clean posts
-reddit_posts |> 
-  slice(10:15) |> 
-  mutate(text = clean_strings(text)) |> 
-  select(text)
+total_posts |> 
+  group_by(Posts) |> 
+  reframe(Total = sum(total)) |> 
+  kable()
 
-```
+total_posts |> 
+  ggplot( aes(x = date_utc, y = total, color= Posts)) + 
+  geom_point(size = 3) +  
+  geom_line(linewidth = 1) +  
+  labs(
+    title = "Total Number of Posts per Day Pre and Post Processing",
+    x = "Day",
+    y = "Total Number of Posts") +
+  scale_color_viridis_d(option="C", end=.8) + 
+  theme_hc()
 
--   Clean posts and comment strings.
-
-```{r}
-reddit_posts <- reddit_posts |> 
-  mutate(text = clean_strings(text))
-
-reddit_comment <- reddit_comment |> 
-  mutate(comment = clean_strings(comment))
-
-reddit_posts_2 <- reddit_posts_2 |> 
-  mutate(text=clean_strings(text))
 ```
@@
 
-### We can now begin to explore the data. First we explore the posts.
+## How many comments and by day?
 
-```{r, results = 'asis'}
+-   We see a peak in the comments during March 6th, which was a Thursday, and perhaps in anticipation of DOGE policies that often are released on Friday morning and have come to be known as "Musk-acre Friday" (<https://smotus.substack.com/p/friday-night-musk-acre>).
 
-  reddit_posts |>
-  slice(364) |> 
-  pull(text)
+```{r}
+
+# number of comments
+comments_data_clean |> nrow() |> kable(col.names = "Total Comments")
+
+comments_data_clean |> 
+  group_by(date_utc) |> 
+  reframe(total = n()) |> 
+  ggplot( aes(x = date_utc, y = total)) + 
+  geom_point(size = 3) +  
+  geom_line(linewidth = 1) +  
+  labs(
+    title = "Total Number of comments per Day during collection",
+    x = "Day",
+    y = "Total Number of Posts") +
+  scale_color_viridis_d(option="A") +
+  theme_hc()
 
 ```
+
+##
+
+## Is there a pattern with respect to the time of day or day of week when posts were created?
+
+## Is there a relationship between events and frequency of reddit posts?
+
+-   Most posts occur during the early morning, noon, and afternoon hours.
+The highest peak is around lunchtime, likely due to people posting during their lunch break.
+There is also significant activity in the afternoon, evening, and early morning.
+This could be because people have more free time or stay up late, allowing them to take the time to write posts, which require more effort than quick interactions.
+The fewest posts are seen in the morning, which makes sense as people are typically getting ready for work, commuting, or sleeping in.
+
+-   The trend for comments mirrors that of posts.
+This makes sense because people are likely using Reddit at similar times for both posting and commenting.
+However, the volume of comments is much higher than the number of posts, as each post receives many comments from different users.
+
+```{r}
+
+posts_data_clean |> 
+  group_by(hour_posted ) |> 
+  reframe(Total = n()) |> 
+  ggplot(aes(x=hour_posted, y=Total)) + 
+  # geom_bar(stat = "identity", fill = "steelblue") + 
+  geom_point(color = "blue", size = 3) +  
+  geom_line(color = "steelblue", linewidth = 1) +
+  labs(
+    title = "Total Number of Posts by Hour of Day (24-hour clock)",
+    x = "Hour of Day",
+    y = "Total Number of Posts"
+  ) +
+  theme_minimal() +
+  theme_hc()
+
+comments_data_clean |> 
+  group_by(hour_posted ) |> 
+  reframe(Total = n()) |> 
+  ggplot(aes(x=hour_posted, y=Total)) + 
+  # geom_bar(stat = "identity", fill = "steelblue") + 
+  geom_point(color = "green", size = 3) +  
+  geom_line(color = "lightgreen", linewidth = 1) +
+  labs(
+    title = "Total Number of Comments by Hour of Day (24-hour clock)",
+    x = "Hour of Day",
+    y = "Total Number of Posts"
+  ) +
+  theme_hc()
+```
+
+## What are the words in the set of posts you have assembled that appear most frequently?
+
+```{r}
+#| fig-width: 6
+#| fig-height: 7
+#| 
+# tokenize words to count frequencies for reddit posts
+posts_word_counts <- posts_data_clean |>
+  select(title, text) |>
+  pivot_longer(cols = c(title, text), values_drop_na = TRUE) |>
+  unnest_tokens(word, value) |>
+  count(word, sort = TRUE) |>
+  slice_max(n, n = 50)
+
+# plot
+ggplot(posts_word_counts, aes(x = reorder(word, n), y = n)) +
+  geom_col(fill = "steelblue") +
+  coord_flip() +
+  labs(title = "Top 50 Words in Reddit Posts (Including Stopwords)",
+       x = "Word",
+       y = "Count") +
+  theme_minimal()
+
+# tokenize words to count frequencies for reddit comments
+comments_word_counts <- comments_data_clean |>
+  select(comment) |>
+  pivot_longer(cols = c(comment), values_drop_na = TRUE) |>
+  unnest_tokens(word, value) |>
+  count(word, sort = TRUE) |>
+  slice_max(n, n = 50)
+
+# plot
+ggplot(comments_word_counts, aes(x = reorder(word, n), y = n)) +
+  geom_col(fill = "lightgreen") +  # Removed extra parentheses
+  coord_flip() +
+  labs(title = "Top 50 Words in Reddit Comments (Including Stopwords)",
+       x = "Word",
+       y = "Count") +
+  theme_minimal()
+```
+
+The graphs above show the most frequent words in both Reddit posts and their comments.
+However, many of these words are stopwords, which don't provide much insight into the actual content of the discussions.
+To get a better understanding of what people are really talking about, we will remove these stopwords in the next step.
+
+## How does this change if you exclude “stop words” such as “a,” “an,” “the,” “is,” and others that are common in English sentences but are generally not informative?
+
+```{r}
+#| fig-width: 6
+#| fig-height: 7
+#| #| 
+# tokenize words to count frequencies for reddit posts removing stop words
+posts_word_counts <- posts_data_clean |>
+  select(title, text) |>
+  pivot_longer(cols = c(title, text), values_drop_na = TRUE) |>
+  unnest_tokens(word, value) |>
+  anti_join(stop_words, by = "word") |>
+  count(word, sort = TRUE) |>
+  slice_max(n, n = 50)
+
+# plot
+ggplot(posts_word_counts, aes(x = reorder(word, n), y = n)) +
+  geom_col(fill = "steelblue") +
+  coord_flip() +
+  labs(title = "Top 50 Words in Reddit Posts (Removing Stopwords)",
+       x = "Word",
+       y = "Count") +
+  theme_minimal()
+
+# tokenize words to count frequencies for Reddit comments, removing stop words
+comments_word_counts <- comments_data_clean |>
+  select(comment) |>
+  pivot_longer(cols = c(comment), values_drop_na = TRUE) |>
+  unnest_tokens(word, value) |>
+  anti_join(stop_words, by = "word") |>
+  count(word, sort = TRUE) |>
+  slice_max(order_by = n, n = 50)
+
+# plot
+ggplot(comments_word_counts, aes(x = reorder(word, n), y = n)) +
+  geom_col(fill = "lightgreen") +  # Removed extra parentheses
+  coord_flip() +
+  labs(title = "Top 50 Words in Reddit Comments (Removing Stopwords)",
+       x = "Word",
+       y = "Count") +
+  theme_minimal()
+```
+
+The graphs above show the most frequent words used in both Reddit posts and their comment sections.
+We can see that many of these words are directly related to our topic, with frequent mentions of the President, DOGE, the federal government, and RIF.

### 2025-03-20 code/paper.qmd
adding report

---
title: "DOGE Days on Reddit: Decoding Public Sentiment in a Federal Shakeup"
format:
  jasa-pdf:
    keep-tex: true  
    journal:
      blinded: false
  jasa-html: default
date: last-modified
author:
  - name: Kevin Linares
    affiliations:
      - name: University of Maryland
  - name: Felix Baez-Santiago
  - name: Aria Lu
  - name: Gloria Zhou
    affiliations:
      - name: University of Michigan
abstract: |
  This study explores the impact of the Department of Government Efficiency (DOGE)'s federal workforce reductions on public sentiment, utilizing Reddit as a data source. By scraping and analyzing posts and comments related to DOGE, we examined public reactions, including fear, anxiety, and support, during a period of significant governmental change. The analysis reveals how specific news events influenced online discourse and highlights the utility of social media for understanding public perception of policy impacts.
keywords:
  - Reddit
  - Federal Government
  - DOGE
editor: 
  markdown: 
    wrap: sentence
---

```{r include=FALSE}

knitr::opts_chunk$set(echo = FALSE)

library(readxl)
library(viridis)
library(ggthemes)
library(tidytext)
library(knitr)
library(tidyverse)

# path to repo
#repo_path <- str_c(~/Desktop/UMICH/SURV622_Assignment/data/") # felix
repo_path <- str_c("~/repos/SURV622_Assignment/data/") # kevin

data_files <- list.files(repo_path) |> 
  tibble() |> 
  rename(data_file_names = 1) |> 
  filter(str_detect(data_file_names, ".xlsx|.RDS")) |> 
  mutate(data_names = str_remove_all(data_file_names, "\\..*"))

list2env(
  map(data_files$data_file_names, function(x){

  # read data file
  if(str_detect(x, "posts_data_clean")) {
    dat = read_xlsx(str_c(repo_path, x))
  } 
    else if(str_detect(x, "comments_data_clean")){

    dat =  read_excel(str_c(repo_path, x),
                      col_types = c("text", "text", "date", "guess", "numeric",
                                    "numeric", "numeric", "numeric", "text",
                                     "guess", "text", "text", "guess", "text",
                                     "text"))

    }

    else(
    dat = readRDS(str_c(repo_path, x)) 
  )

  # manipualte variables
  dat = dat |> 
     mutate(date_utc = ymd(date_utc),
    hour_posted = hour(as_datetime(timestamp)),
  )

}) |> 
  # name the files
    set_names(data_files$data_names),

# save data to the global environment
globalenv()
)
```

## Introduction {#sec-intro}

Since it's inception in January of 2025, the Department of Government Efficiency (DOGE) has fired over 200,000 federal workers in an effort by the new administration to keep a campaign promise in reducing federal government.
However, DOGE's overreaching approach and often illegal tactics has resulted sparked fear and anxiety among the federal workforce, thus taking a toll on their mental health.
Many are uncertain about their career faith as it is in the hands of outsiders that disregard internal policies with no remorse.
The current topic on how DOGE is impacting federal worker's perceptions of job security is likely to continue and worsen over the next few months, given DOGE's nontransparent and unconventional methods without accountability.
We propose that Reddit as a platform offers researchers a vantage look into lively discussions, timely reactions, and grievances from federal workers on this topic.
Furthermore, we also expect to capture positive reactions to DOGE's approach in reducing the federal workforce.

## Methods {#sec-meth}

*Search Terms*.
Our preliminary Reddit API scrape allowed us to decide on a set of keyword searches related to this topic of research.
This was an iterative process that resulted in the use of 8 keywords we used to search for posts related to the topic of interest (see Table 1).
We excluded keywords that were either vague or broad such as "Elon Musk" or "drain the swamp." Additionally, we examined subreddit posts and found a plethora of unrelated posts using our keyword search list.
For instance, searching for "Fork in the Road" brought back several subreddits on motorcycles and mountain biking.
Additionally, searching for "DOGE" also brought back posts on DOGEcoin which is unrelated to our topic.
Therefore, we meticoulsly combed through a list of subreddits we acquired from our initial scrape and selected those that contaiend relevant posts.
To compensate for balance on this topic, we included conservative subreddits such as "neoliberal", "AskConservitives" as well as we avoided specific agency subreddits, for instance "NIH" or "CDC" as to not overwhelm one particular view point.
Overall we ended with 19 subreddits (see appendix) and 8 keywords resulting in 152 unique combinations to scrape.

```{r}
posts_data |> distinct(search_term) |> 
  kable(caption = "List of keywords related to topic")

```

*Analytic Plan*.
We listened to the Reddit API from March 2 through the 10th on every top of the hour by scraping each combination of our seven keywords and 20 subreddits resulting in 152 API hits per hour.
Reddit API scraping limits were managed by setting a sleep timer in between API hits.
As new Reddit posts were scraped they were entered into a data table without preprocessing.
After the listening period, the accumulated number of unprocessed posts was 643.
Every row in our data table equated to one post, and we had 8 columns to include the date and time of the post, title and text of post, subreddit where the post derived from, number of comments associated with it, url, and we recorded the search term that was used to collect the post.
We processed the posts to exclude duplicates, and in some instance two different keywords resulted in scraping the same posts so we kept we dropped one of them.
Post text were cleaned in terms of removing weblinks and when possible translating special character such as the at sign to the word "at." The date column was converted to a date class variable and we extracted the day of the week and time of day from it to use in analysis.
Cleaning our scraped posts resulted in 557 posts.

A glance at the posts revealed that many of them are factual statements, questions, or re-postings of news articles and videos.
Therefore, these texts do not lend themselves to be coded for favorability, and we decided to also scrape the comments associated with each post.
This resulted in 12,553 comments, post processing, containing information about the score, up/down votes, and date/time posted.
We removed comments that had only a weblink, video, or image as these cannot be coded.
A look into some of these comments revealed more opinionated statements and reactions which we than randomly (without replacement) selected 400 comments assigned to four graduate students to code for whether the comment favored DOGE's approach to the reduction in the federal force, opposed, or was neutral.

## Results

We show the number of posts pre/post processing by day in Figure 1 during the timeframe that we collected these data..
There appears to be a noticeable peak in activity during the middle of the week.
However, we don't have enough data across weeks to conclusively say it's due to the day of the week itself.
It's more likely that these spikes are linked to specific events that occurred on those days, which sparked conversations.
The two peaks in our graph could be attributed to two major news stories.
On March 5, Elon Musk made a statement about wanting to "save Western civilization from empathy," and on March 6, there were reports that President Trump was limiting Musk's authority due to backlash over cuts to DOGE.
These events likely had a significant impact on the volume of Reddit posts related to Elon Musk and DOGE, driving the observed spikes in activity.

On May third, news outlets started reporting that DOGE was claiming \$105 billion dollars in savings from cutting "wasteful" spending by layoffs and cutting foreign aid.
This amount is controversial since since the receipts shown on their site only amount to less than [\$9.6 billion](https://abcnews.go.com/US/doge-website-now-saved-105-billion-backtracked-earlier/story?id=119408347).
This could have prompted Reddit users to take to subreddits and provide their opinion or thoughts on this matter.

```{r}
#| fig-width: 6
#| fig-height: 3
#| 
# number of total posts
total_posts <- posts_data |> 
  filter(date_utc > "2025-03-01") |> 
  group_by(date_utc) |> 
  reframe(total = n()) |> 
  mutate(Posts = "pre processing") |> 
  add_row(
    posts_data_clean |> 
  group_by(date_utc) |> 
  reframe(total = n()) |> 
  mutate(Posts = "post processing")
  )

total_posts |> 
  ggplot( aes(x = date_utc, y = total, color= Posts)) + 
  geom_point(size = 3) +  
  geom_line(linewidth = 1) +  
  labs(
    title = "Figure 1. Total Number of Daily Posts Pre/Post Processing",
    x = "Day",
    y = "Total Number of Posts") +
  scale_color_viridis_d(option="C", end=.8) + 
  theme_hc()

```

We see a peak in the comments in Figure 2 during March 6th, which was a Thursday, and perhaps in anticipation of DOGE policies that often are released on Friday morning and have come to be known as "[Musk-acre Friday](https://smotus.substack.com/p/friday-night-musk-acre)."

```{r}

comments_data_clean |> 
  group_by(date_utc) |> 
  reframe(total = n()) |> 
  ggplot( aes(x = date_utc, y = total)) + 
  geom_point(size = 3) +  
  geom_line(linewidth = 1) +  
  labs(
    title = "Figure 2. Total Number of daily comments",
    x = "Day",
    y = "Total Number of Posts") +
  scale_color_viridis_d(option="A") +
  theme_hc()
```

Most posts occur during the early morning, noon, and afternoon hours (see Figure 3).
The highest peak is around lunchtime, likely due to people posting during their lunch break.
There is also significant activity in the afternoon, evening, and early morning.
This could be because people have more free time or stay up late, allowing them to take the time to write posts, which require more effort than quick interactions.
The fewest posts are seen in the morning, which makes sense as people are typically getting ready for work, commuting, or sleeping in.
The trend for comments (see Figure 4) mirrors that of posts.
This makes sense because people are likely using Reddit at similar times for both posting and commenting.
However, the volume of comments is much higher than the number of posts, as each post receives many comments from different users.

```{r}
posts_data_clean |> 
  group_by(hour_posted ) |> 
  reframe(Total = n()) |> 
  ggplot(aes(x=hour_posted, y=Total)) + 
  # geom_bar(stat = "identity", fill = "steelblue") + 
  geom_point(color = "blue", size = 3) +  
  geom_line(color = "steelblue", linewidth = 1) +
  labs(
    title = "Figure 3. Total Number of Posts by Hour of Day",
    subtitle = "(24-hour clock)",
    x = "Hour of Day",
    y = "Total Number of Posts"
  ) +
  theme_minimal() +
  theme_hc()

comments_data_clean |> 
  group_by(hour_posted ) |> 
  reframe(Total = n()) |> 
  ggplot(aes(x=hour_posted, y=Total)) + 
  # geom_bar(stat = "identity", fill = "steelblue") + 
  geom_point(color = "green", size = 3) +  
  geom_line(color = "lightgreen", linewidth = 1) +
  labs(
    title = "Figure 4. Total Number of Comments by Hour of Day",
    subtitle = "(24-hour clock)",
    x = "Hour of Day",
    y = "Total Number of Posts"
  ) +
  theme_hc()
```

### What are the words in the set of posts you have assembled that appear most frequently?

```{r}
#| fig-width: 6
#| fig-height: 7
#| 
# tokenize words to count frequencies for reddit posts
posts_word_counts <- posts_data_clean |>
  select(title, text) |>
  pivot_longer(cols = c(title, text), values_drop_na = TRUE) |>
  unnest_tokens(word, value) |>
  count(word, sort = TRUE) |>
  slice_max(n, n = 50)

# plot
ggplot(posts_word_counts, aes(x = reorder(word, n), y = n)) +
  geom_col(fill = "steelblue") +
  coord_flip() +
  labs(title = "Top 50 Words in Reddit Posts (Including Stopwords)",
       x = "Word",
       y = "Count") +
  theme_minimal()

# tokenize words to count frequencies for reddit comments
comments_word_counts <- comments_data_clean |>
  select(comment) |>
  pivot_longer(cols = c(comment), values_drop_na = TRUE) |>
  unnest_tokens(word, value) |>
  count(word, sort = TRUE) |>
  slice_max(n, n = 50)

# plot
ggplot(comments_word_counts, aes(x = reorder(word, n), y = n)) +
  geom_col(fill = "lightgreen") +  # Removed extra parentheses
  coord_flip() +
  labs(title = "Top 50 Words in Reddit Comments (Including Stopwords)",
       x = "Word",
       y = "Count") +
  theme_minimal()
```

The graphs above show the most frequent words in both Reddit posts and their comments.
However, many of these words are stopwords, which don't provide much insight into the actual content of the discussions.
To get a better understanding of what people are really talking about, we will remove these stopwords in the next step.

### How does this change if you exclude “stop words” such as “a,” “an,” “the,” “is,” and others that are common in English sentences but are generally not informative?

```{r}
#| fig-width: 6
#| fig-height: 7
#| #| 
# tokenize words to count frequencies for reddit posts removing stop words
posts_word_counts <- posts_data_clean |>
  select(title, text) |>
  pivot_longer(cols = c(title, text), values_drop_na = TRUE) |>
  unnest_tokens(word, value) |>
  anti_join(stop_words, by = "word") |>
  count(word, sort = TRUE) |>
  slice_max(n, n = 50)

# plot
ggplot(posts_word_counts, aes(x = reorder(word, n), y = n)) +
  geom_col(fill = "steelblue") +
  coord_flip() +
  labs(title = "Top 50 Words in Reddit Posts (Removing Stopwords)",
       x = "Word",
       y = "Count") +
  theme_minimal()

# tokenize words to count frequencies for Reddit comments, removing stop words
comments_word_counts <- comments_data_clean |>
  select(comment) |>
  pivot_longer(cols = c(comment), values_drop_na = TRUE) |>
  unnest_tokens(word, value) |>
  anti_join(stop_words, by = "word") |>
  count(word, sort = TRUE) |>
  slice_max(order_by = n, n = 50)

# plot
ggplot(comments_word_counts, aes(x = reorder(word, n), y = n)) +
  geom_col(fill = "lightgreen") +  # Removed extra parentheses
  coord_flip() +
  labs(title = "Top 50 Words in Reddit Comments (Removing Stopwords)",
       x = "Word",
       y = "Count") +
  theme_minimal()
```

The graphs above show the most frequent words used in both Reddit posts and their comment sections.
We can see that many of these words are directly related to our topic, with frequent mentions of the President, DOGE, the federal government, and RIF.

*Coding Comments*.
We coded 400 comments chosen at random

```{r}
comments_data_clean |> 
  mutate(outcome = replace_na(outcome, "Not Coded")) |> 
  count(outcome, name = 'Total') |>

  kable(caption = "Distribution of favorability coding for 400 comments")
```

\newpage

## Appendix

```{r}
posts_data |> distinct(subreddit) |> 
  kable(caption = "List of subreddits relevant to the topic of DOGE")
```

### 2025-03-20 code/paper.tex
adding report

--- 2025-03-14 code/Reddit_eda.tex
@@
 \documentclass[
-  letterpaper,
-  DIV=11,
-  numbers=noendperiod]{scrartcl}
+  12pt]{article}
 
@@
 \setlength{\emergencystretch}{3em} % prevent overfull lines
-\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+\setcounter{secnumdepth}{5}
 % Make \paragraph and \subparagraph free-standing
@@
 \makeatother
-
-\usepackage{color}
-\usepackage{fancyvrb}
-\newcommand{\VerbBar}{|}
-\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
-\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
-% Add ',fontsize=\small' for more characters per line
-\usepackage{framed}
-\definecolor{shadecolor}{RGB}{241,243,245}
-\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
-\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
-\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
-\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
-\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
-\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
-\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{\textbf{#1}}}
-\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
-\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
-\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
-\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
-\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
-\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{\textbf{#1}}}
-\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
-\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
-\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
-\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
-\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
-\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
-\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
-\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
-\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
-\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
-\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
 
@@
 
-\KOMAoption{captions}{tableheading}
+\addtolength{\oddsidemargin}{-.5in}%
+\addtolength{\evensidemargin}{-1in}%
+\addtolength{\textwidth}{1in}%
+\addtolength{\textheight}{1.7in}%
+\addtolength{\topmargin}{-1in}%
 \makeatletter
@@
 \fi
+\usepackage[]{natbib}
+\bibliographystyle{agsm}
 \usepackage{bookmark}
@@
 \hypersetup{
-  pdftitle={Assignment 2},
-  pdfauthor={Group 2},
+  pdftitle={DOGE Days on Reddit: Decoding Public Sentiment in a Federal Shakeup},
+  pdfauthor={Kevin Linares; Felix Baez-Santiago; Aria Lu; Gloria Zhou},
+  pdfkeywords={Reddit, Federal Government, DOGE},
   colorlinks=true,
@@
 
-\title{Assignment 2}
-\author{Group 2}
-\date{2025-03-13}
+\begin{document}
 
-\begin{document}
+\def\spacingset#1{\renewcommand{\baselinestretch}%
+{#1}\small\normalsize} \spacingset{1}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\date{March 20, 2025}
+\title{\bf DOGE Days on Reddit: Decoding Public Sentiment in a Federal
+Shakeup}
+\author{
+Kevin Linares\\
+University of Maryland\\
+and\\Felix Baez-Santiago\\
+and\\Aria Lu\\
+and\\Gloria Zhou\\
+University of Michigan\\
+}
 \maketitle
 
-\section{We will explore the data we scraped to determine next steps for
-analysis.}\label{we-will-explore-the-data-we-scraped-to-determine-next-steps-for-analysis.}
+\bigskip
+\bigskip
+\begin{abstract}
+This study explores the impact of the Department of Government
+Efficiency (DOGE)'s federal workforce reductions on public sentiment,
+utilizing Reddit as a data source. By scraping and analyzing posts and
+comments related to DOGE, we examined public reactions, including fear,
+anxiety, and support, during a period of significant governmental
+change. The analysis reveals how specific news events influenced online
+discourse and highlights the utility of social media for understanding
+public perception of policy impacts.
+\end{abstract}
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  Read in data from github, and tidy it to continue processing.
-\end{enumerate}
+\noindent%
+{\it Keywords:} Reddit, Federal Government, DOGE
+\vfill
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# posts data}
-\NormalTok{reddit\_posts }\OtherTok{\textless{}{-}} \FunctionTok{read\_xlsx}\NormalTok{(}
-  \CommentTok{\# "\textasciitilde{}/repos/SURV622\_Assignment/data/posts\_data\_clean.xlsx") |\textgreater{} path for Kevin}
-  \StringTok{"\textasciitilde{}/Desktop/UMICH/SURV622\_Assignment/data/posts\_data\_clean.xlsx"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} \CommentTok{\# path for Felix}
-  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{date\_utc =} \FunctionTok{ymd}\NormalTok{(date\_utc)) }\SpecialCharTok{|\textgreater{}} 
-  \CommentTok{\# remove variables not needed}
-  \CommentTok{\# select({-}timestamp)}
-  \FunctionTok{mutate}\NormalTok{(}
-    \CommentTok{\# Convert timestamp to POSIXct format}
-    \AttributeTok{timestamp =} \FunctionTok{as.POSIXct}\NormalTok{(timestamp, }\AttributeTok{origin =} \StringTok{"1970{-}01{-}01"}\NormalTok{, }\AttributeTok{tz =} \StringTok{"UTC"}\NormalTok{),}
+\newpage
+\spacingset{1.9} % DON'T change the spacing!
 
-    \CommentTok{\# Extract time of day (you can adjust the format as needed)}
-    \AttributeTok{time\_of\_day =} \FunctionTok{format}\NormalTok{(timestamp, }\StringTok{"\%H:\%M:\%S"}\NormalTok{)}
-\NormalTok{  )}
+\section{Introduction}\label{sec-intro}
 
-\CommentTok{\# comments data}
-\NormalTok{reddit\_comment }\OtherTok{\textless{}{-}} \FunctionTok{read\_xlsx}\NormalTok{(}
-  \CommentTok{\# "\textasciitilde{}/repos/SURV622\_Assignment/data/comments\_data\_clean.xlsx") |\textgreater{} Kevin\textquotesingle{}s path}
-  \StringTok{"\textasciitilde{}/Desktop/UMICH/SURV622\_Assignment/data/comments\_data\_clean.xlsx"}\NormalTok{) }\SpecialCharTok{|\textgreater{}} \CommentTok{\# Felix\textquotesingle{}s path}
-    \FunctionTok{mutate}\NormalTok{(}\AttributeTok{date\_utc =} \FunctionTok{ymd}\NormalTok{(date\_utc)) }\SpecialCharTok{|\textgreater{}} 
-  \CommentTok{\# great unique post id}
-  \FunctionTok{arrange}\NormalTok{(date\_utc) }\SpecialCharTok{|\textgreater{}} 
-  \FunctionTok{group\_by}\NormalTok{(url) }\SpecialCharTok{|\textgreater{}} 
-  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{post\_id =} \FunctionTok{cur\_group\_id}\NormalTok{()) }\SpecialCharTok{|\textgreater{}} 
-  \FunctionTok{ungroup}\NormalTok{() }\SpecialCharTok{|\textgreater{}} 
-  \CommentTok{\# remove variables not needed}
-  \FunctionTok{mutate}\NormalTok{(}
-    \CommentTok{\# Convert timestamp to POSIXct format}
-    \AttributeTok{timestamp =} \FunctionTok{as.POSIXct}\NormalTok{(timestamp, }\AttributeTok{origin =} \StringTok{"1970{-}01{-}01"}\NormalTok{, }\AttributeTok{tz =} \StringTok{"UTC"}\NormalTok{),}
+Since it's inception in January of 2025, the Department of Government
+Efficiency (DOGE) has fired over 200,000 federal workers in an effort by
+the new administration to keep a campaign promise in reducing federal
+government. However, DOGE's overreaching approach and often illegal
+tactics has resulted sparked fear and anxiety among the federal
+workforce, thus taking a toll on their mental health. Many are uncertain
+about their career faith as it is in the hands of outsiders that
+disregard internal policies with no remorse. The current topic on how
+DOGE is impacting federal worker's perceptions of job security is likely
+to continue and worsen over the next few months, given DOGE's
+nontransparent and unconventional methods without accountability. We
+propose that Reddit as a platform offers researchers a vantage look into
+lively discussions, timely reactions, and grievances from federal
+workers on this topic. Furthermore, we also expect to capture positive
+reactions to DOGE's approach in reducing the federal workforce.
 
-    \CommentTok{\# Extract time of day (you can adjust the format as needed)}
-    \AttributeTok{time\_of\_day =} \FunctionTok{format}\NormalTok{(timestamp, }\StringTok{"\%H:\%M:\%S"}\NormalTok{)}
-\NormalTok{  ) }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{select}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{author, }\SpecialCharTok{{-}}\NormalTok{comment\_id) }
+\section{Methods}\label{sec-meth}
 
-\CommentTok{\# id url group IDs to the posts data}
-\NormalTok{reddit\_posts\_2 }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_posts }\SpecialCharTok{|\textgreater{}} 
-  \FunctionTok{semi\_join}\NormalTok{(reddit\_comment }\SpecialCharTok{|\textgreater{}} \FunctionTok{select}\NormalTok{(url, post\_id)) }
-\end{Highlighting}
-\end{Shaded}
+\emph{Search Terms}. Our preliminary Reddit API scrape allowed us to
+decide on a set of keyword searches related to this topic of research.
+This was an iterative process that resulted in the use of 8 keywords we
+used to search for posts related to the topic of interest (see Table 1).
+We excluded keywords that were either vague or broad such as ``Elon
+Musk'' or ``drain the swamp.'' Additionally, we examined subreddit posts
+and found a plethora of unrelated posts using our keyword search list.
+For instance, searching for ``Fork in the Road'' brought back several
+subreddits on motorcycles and mountain biking. Additionally, searching
+for ``DOGE'' also brought back posts on DOGEcoin which is unrelated to
+our topic. Therefore, we meticoulsly combed through a list of subreddits
+we acquired from our initial scrape and selected those that contaiend
+relevant posts. To compensate for balance on this topic, we included
+conservative subreddits such as ``neoliberal'', ``AskConservitives'' as
+well as we avoided specific agency subreddits, for instance ``NIH'' or
+``CDC'' as to not overwhelm one particular view point. Overall we ended
+with 19 subreddits (see appendix) and 8 keywords resulting in 152 unique
+combinations to scrape.
 
-\subsubsection{The strings we will be processing sometimes have special
-characters, numbers, brackets. We need to clean these string for
-processing.}\label{the-strings-we-will-be-processing-sometimes-have-special-characters-numbers-brackets.-we-need-to-clean-these-string-for-processing.}
-
-\begin{itemize}
-\tightlist
-\item
-  We can use the fedmatch::clean\_strings() function to tidy up the
-  text. The following is an example of what will be cleaned.
-\end{itemize}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# print example of posts}
-\NormalTok{reddit\_posts }\SpecialCharTok{|\textgreater{}} 
-  \FunctionTok{slice}\NormalTok{(}\DecValTok{10}\SpecialCharTok{:}\DecValTok{15}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
-  \FunctionTok{select}\NormalTok{(text) }
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-# A tibble: 6 x 1
-  text                                                                          
-  <chr>                                                                         
-1 <NA>                                                                          
-2 <NA>                                                                          
-3 <NA>                                                                          
-4 <NA>                                                                          
-5 <NA>                                                                          
-6 commerce secretary howard lutnick said sunday that government spending could ~
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# clean posts}
-\NormalTok{reddit\_posts }\SpecialCharTok{|\textgreater{}} 
-  \FunctionTok{slice}\NormalTok{(}\DecValTok{10}\SpecialCharTok{:}\DecValTok{15}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
-  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{text =} \FunctionTok{clean\_strings}\NormalTok{(text)) }\SpecialCharTok{|\textgreater{}} 
-  \FunctionTok{select}\NormalTok{(text) }
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-# A tibble: 6 x 1
-  text                                                                          
-  <chr>                                                                         
-1 <NA>                                                                          
-2 <NA>                                                                          
-3 <NA>                                                                          
-4 <NA>                                                                          
-5 <NA>                                                                          
-6 commerce secretary howard lutnick said sunday that government spending could ~
-\end{verbatim}
-
-\begin{itemize}
-\tightlist
-\item
-  Clean posts and comment strings.
-\end{itemize}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{reddit\_posts }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_posts }\SpecialCharTok{|\textgreater{}} 
-  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{text =} \FunctionTok{clean\_strings}\NormalTok{(text))}
-
-\NormalTok{reddit\_comment }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_comment }\SpecialCharTok{|\textgreater{}} 
-  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{comment =} \FunctionTok{clean\_strings}\NormalTok{(comment))}
-
-\NormalTok{reddit\_posts\_2 }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_posts\_2 }\SpecialCharTok{|\textgreater{}} 
-  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{text=}\FunctionTok{clean\_strings}\NormalTok{(text))}
-\end{Highlighting}
-\end{Shaded}
-
-\hfill\break
-
-\subsubsection{We can now begin to explore the data. First we explore
-the
-posts.}\label{we-can-now-begin-to-explore-the-data.-first-we-explore-the-posts.}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{  reddit\_posts }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{slice}\NormalTok{(}\DecValTok{364}\NormalTok{) }\SpecialCharTok{|\textgreater{}} 
-  \FunctionTok{pull}\NormalTok{(text) }
-\end{Highlighting}
-\end{Shaded}
-
-{[}1{]} ``hello all so i recently took the deferred resignation i was
-working at the va and my job was not exempt i did not trust that my job
-was safe even after coming off probation the day the fork in the road
-came out i took the resignation and my last day was february 28 before i
-started i was in the cwt program compensated work therapy i once again
-have an opportunity to get back into the program i know we are allowed
-to work while on the resignation but am i able to do the cwt because
-both checks would be federal payments i don t want to lose out on the
-resignation benefits just to make 12 hr but working does help me mental
-health and give me a purpose any insight would be greatly appreciated''
-
-\subsection{How many posts were collected in total and by day? How many
-posts after data cleaning? Is there a pattern with respect to the time
-of day or day of week when posts were created? Is there a relationship
-between events and frequency of
-tweets?}\label{how-many-posts-were-collected-in-total-and-by-day-how-many-posts-after-data-cleaning-is-there-a-pattern-with-respect-to-the-time-of-day-or-day-of-week-when-posts-were-created-is-there-a-relationship-between-events-and-frequency-of-tweets}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# number of total posts}
-\NormalTok{totalposts }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_posts }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{summarize}\NormalTok{(}
-    \AttributeTok{TotalPosts =} \FunctionTok{n}\NormalTok{()}
-\NormalTok{  )}
-\NormalTok{knitr}\SpecialCharTok{::}\FunctionTok{kable}\NormalTok{(totalposts)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{longtable}[]{@{}r@{}}
+\begin{longtable}[]{@{}l@{}}
+\caption{List of keywords related to topic}\tabularnewline
 \toprule\noalign{}
-TotalPosts \\
+search\_term \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+search\_term \\
 \midrule\noalign{}
@@
 \endlastfoot
-557 \\
+DOGE \\
+Department of Government Efficiency \\
+wasteful spending \\
+government waste \\
+government fraud \\
+reduction in force \\
+rif \\
+fork in the road \\
 \end{longtable}
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# number of posts by day}
-\NormalTok{byday\_posts }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_posts }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{group\_by}\NormalTok{(date\_utc) }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{summarize}\NormalTok{(}
-    \AttributeTok{total =} \FunctionTok{n}\NormalTok{()}
-\NormalTok{  )}
+\emph{Analytic Plan}. We listened to the Reddit API from March 2 through
+the 10th on every top of the hour by scraping each combination of our
+seven keywords and 20 subreddits resulting in 152 API hits per hour.
+Reddit API scraping limits were managed by setting a sleep timer in
+between API hits. As new Reddit posts were scraped they were entered
+into a data table without preprocessing. After the listening period, the
+accumulated number of unprocessed posts was 643. Every row in our data
+table equated to one post, and we had 8 columns to include the date and
+time of the post, title and text of post, subreddit where the post
+derived from, number of comments associated with it, url, and we
+recorded the search term that was used to collect the post. We processed
+the posts to exclude duplicates, and in some instance two different
+keywords resulted in scraping the same posts so we kept we dropped one
+of them. Post text were cleaned in terms of removing weblinks and when
+possible translating special character such as the at sign to the word
+``at.'' The date column was converted to a date class variable and we
+extracted the day of the week and time of day from it to use in
+analysis. Cleaning our scraped posts resulted in 557 posts.
 
-\CommentTok{\# plot}
-\FunctionTok{ggplot}\NormalTok{(byday\_posts, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ date\_utc, }\AttributeTok{y =}\NormalTok{ total)) }\SpecialCharTok{+} 
-  \FunctionTok{geom\_point}\NormalTok{(}\AttributeTok{color =} \StringTok{"blue"}\NormalTok{, }\AttributeTok{size =} \DecValTok{3}\NormalTok{) }\SpecialCharTok{+}  
-  \FunctionTok{geom\_line}\NormalTok{(}\AttributeTok{color =} \StringTok{"steelblue"}\NormalTok{, }\AttributeTok{linewidth =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{+}  
-  \FunctionTok{labs}\NormalTok{(}
-    \AttributeTok{title =} \StringTok{"Total Number of Posts per Day"}\NormalTok{,}
-    \AttributeTok{x =} \StringTok{"Day"}\NormalTok{,}
-    \AttributeTok{y =} \StringTok{"Total Number of Posts"}
-\NormalTok{  ) }\SpecialCharTok{+}
-  \FunctionTok{theme\_minimal}\NormalTok{()}
-\end{Highlighting}
-\end{Shaded}
+A glance at the posts revealed that many of them are factual statements,
+questions, or re-postings of news articles and videos. Therefore, these
+texts do not lend themselves to be coded for favorability, and we
+decided to also scrape the comments associated with each post. This
+resulted in 12,553 comments, post processing, containing information
+about the score, up/down votes, and date/time posted. We removed
+comments that had only a weblink, video, or image as these cannot be
+coded. A look into some of these comments revealed more opinionated
+statements and reactions which we than randomly (without replacement)
+selected 400 comments assigned to four graduate students to code for
+whether the comment favored DOGE's approach to the reduction in the
+federal force, opposed, or was neutral.
 
-\includegraphics{Reddit_eda_files/figure-pdf/unnamed-chunk-5-1.pdf}
+\section{Results}\label{results}
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# number of total comments}
-\NormalTok{totalcomments }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_comment }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{summarize}\NormalTok{(}
-    \AttributeTok{TotalPosts =} \FunctionTok{n}\NormalTok{()}
-\NormalTok{  )}
-\NormalTok{knitr}\SpecialCharTok{::}\FunctionTok{kable}\NormalTok{(totalcomments)}
-\end{Highlighting}
-\end{Shaded}
+We show the number of posts pre/post processing by day in Figure 1
+during the timeframe that we collected these data.. There appears to be
+a noticeable peak in activity during the middle of the week. However, we
+don't have enough data across weeks to conclusively say it's due to the
+day of the week itself. It's more likely that these spikes are linked to
+specific events that occurred on those days, which sparked
+conversations. The two peaks in our graph could be attributed to two
+major news stories. On March 5, Elon Musk made a statement about wanting
+to ``save Western civilization from empathy,'' and on March 6, there
+were reports that President Trump was limiting Musk's authority due to
+backlash over cuts to DOGE. These events likely had a significant impact
+on the volume of Reddit posts related to Elon Musk and DOGE, driving the
+observed spikes in activity.
 
-\begin{longtable}[]{@{}r@{}}
-\toprule\noalign{}
-TotalPosts \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-12492 \\
-\end{longtable}
+On May third, news outlets started reporting that DOGE was claiming
+\$105 billion dollars in savings from cutting ``wasteful'' spending by
+layoffs and cutting foreign aid. This amount is controversial since
+since the receipts shown on their site only amount to less than
+\href{https://abcnews.go.com/US/doge-website-now-saved-105-billion-backtracked-earlier/story?id=119408347}{\$9.6
+billion}. This could have prompted Reddit users to take to subreddits
+and provide their opinion or thoughts on this matter.
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# number of comments by day}
-\NormalTok{byday\_comments }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_comment }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{group\_by}\NormalTok{(date\_utc) }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{summarize}\NormalTok{(}
-    \AttributeTok{total =} \FunctionTok{n}\NormalTok{()}
-\NormalTok{  )}
+\includegraphics{paper_files/figure-pdf/unnamed-chunk-3-1.pdf}
 
-\CommentTok{\# plot}
-\FunctionTok{ggplot}\NormalTok{(byday\_comments, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ date\_utc, }\AttributeTok{y =}\NormalTok{ total)) }\SpecialCharTok{+} 
-  \FunctionTok{geom\_point}\NormalTok{(}\AttributeTok{color =} \StringTok{"green"}\NormalTok{, }\AttributeTok{size =} \DecValTok{3}\NormalTok{) }\SpecialCharTok{+}  
-  \FunctionTok{geom\_line}\NormalTok{(}\AttributeTok{color =} \StringTok{"lightgreen"}\NormalTok{, }\AttributeTok{linewidth =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{+}
-  \FunctionTok{labs}\NormalTok{(}
-    \AttributeTok{title =} \StringTok{"Total Number of Posts per Day"}\NormalTok{,}
-    \AttributeTok{x =} \StringTok{"Day"}\NormalTok{,}
-    \AttributeTok{y =} \StringTok{"Total Number of Posts"}
-\NormalTok{  ) }\SpecialCharTok{+}
-  \FunctionTok{theme\_minimal}\NormalTok{()}
-\end{Highlighting}
-\end{Shaded}
+We see a peak in the comments in Figure 2 during March 6th, which was a
+Thursday, and perhaps in anticipation of DOGE policies that often are
+released on Friday morning and have come to be known as
+``\href{https://smotus.substack.com/p/friday-night-musk-acre}{Musk-acre
+Friday}.''
 
-\includegraphics{Reddit_eda_files/figure-pdf/unnamed-chunk-5-2.pdf}
+\includegraphics{paper_files/figure-pdf/unnamed-chunk-4-1.pdf}
 
-There appears to be a noticeable peak in activity during the middle of
-the week. However, we don't have enough data to conclusively say it's
-due to the day of the week itself. It's more likely that these spikes
-are linked to specific events that occurred on those days, which sparked
-conversations.
+Most posts occur during the early morning, noon, and afternoon hours
+(see Figure 3). The highest peak is around lunchtime, likely due to
+people posting during their lunch break. There is also significant
+activity in the afternoon, evening, and early morning. This could be
+because people have more free time or stay up late, allowing them to
+take the time to write posts, which require more effort than quick
+interactions. The fewest posts are seen in the morning, which makes
+sense as people are typically getting ready for work, commuting, or
+sleeping in. The trend for comments (see Figure 4) mirrors that of
+posts. This makes sense because people are likely using Reddit at
+similar times for both posting and commenting. However, the volume of
+comments is much higher than the number of posts, as each post receives
+many comments from different users.
 
-The two peaks in our graph could be attributed to two major news
-stories. On March 5, Elon Musk made a statement about wanting to ``save
-Western civilization from empathy,'' and on March 6, there were reports
-that President Trump was limiting Musk's authority due to backlash over
-cuts to DOGE. These events likely had a significant impact on the volume
-of Reddit posts related to Elon Musk and DOGE, driving the observed
-spikes in activity.
+\includegraphics{paper_files/figure-pdf/unnamed-chunk-5-1.pdf}
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# Number of posts by time of day (hour)}
-\NormalTok{byhour\_posts }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_posts }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{hour\_of\_day =} \FunctionTok{hour}\NormalTok{(timestamp)) }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{group\_by}\NormalTok{(hour\_of\_day) }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{summarize}\NormalTok{(}\AttributeTok{total =} \FunctionTok{n}\NormalTok{())}
-
-\CommentTok{\# Plot number of posts by hour of day}
-\FunctionTok{ggplot}\NormalTok{(byhour\_posts, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ hour\_of\_day, }\AttributeTok{y =}\NormalTok{ total)) }\SpecialCharTok{+} 
-  \CommentTok{\# geom\_bar(stat = "identity", fill = "steelblue") + }
-  \FunctionTok{geom\_point}\NormalTok{(}\AttributeTok{color =} \StringTok{"blue"}\NormalTok{, }\AttributeTok{size =} \DecValTok{3}\NormalTok{) }\SpecialCharTok{+}  
-  \FunctionTok{geom\_line}\NormalTok{(}\AttributeTok{color =} \StringTok{"steelblue"}\NormalTok{, }\AttributeTok{linewidth =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{+}
-  \FunctionTok{labs}\NormalTok{(}
-    \AttributeTok{title =} \StringTok{"Total Number of Posts by Hour of Day (24{-}hour clock)"}\NormalTok{,}
-    \AttributeTok{x =} \StringTok{"Hour of Day"}\NormalTok{,}
-    \AttributeTok{y =} \StringTok{"Total Number of Posts"}
-\NormalTok{  ) }\SpecialCharTok{+}
-  \FunctionTok{theme\_minimal}\NormalTok{()}
-\end{Highlighting}
-\end{Shaded}
-
-\includegraphics{Reddit_eda_files/figure-pdf/unnamed-chunk-6-1.pdf}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# Number of comments by time of day (hour)}
-\NormalTok{byhour\_comments }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_comment }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{mutate}\NormalTok{(}\AttributeTok{hour\_of\_day =} \FunctionTok{hour}\NormalTok{(timestamp)) }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{group\_by}\NormalTok{(hour\_of\_day) }\SpecialCharTok{\%\textgreater{}\%}
-  \FunctionTok{summarize}\NormalTok{(}\AttributeTok{total =} \FunctionTok{n}\NormalTok{())}
-
-\CommentTok{\# Plot number of posts by hour of day}
-\FunctionTok{ggplot}\NormalTok{(byhour\_comments, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =}\NormalTok{ hour\_of\_day, }\AttributeTok{y =}\NormalTok{ total)) }\SpecialCharTok{+} 
-  \CommentTok{\# geom\_bar(stat = "identity", fill = "lightgreen") + }
-  \FunctionTok{geom\_point}\NormalTok{(}\AttributeTok{color =} \StringTok{"green"}\NormalTok{, }\AttributeTok{size =} \DecValTok{3}\NormalTok{) }\SpecialCharTok{+}  
-  \FunctionTok{geom\_line}\NormalTok{(}\AttributeTok{color =} \StringTok{"lightgreen"}\NormalTok{, }\AttributeTok{linewidth =} \DecValTok{1}\NormalTok{) }\SpecialCharTok{+}
-  \FunctionTok{labs}\NormalTok{(}
-    \AttributeTok{title =} \StringTok{"Total Number of Comments by Hour of Day (24{-}hour clock)"}\NormalTok{,}
-    \AttributeTok{x =} \StringTok{"Hour of Day"}\NormalTok{,}
-    \AttributeTok{y =} \StringTok{"Total Number of Posts"}
-\NormalTok{  ) }\SpecialCharTok{+}
-  \FunctionTok{theme\_minimal}\NormalTok{()}
-\end{Highlighting}
-\end{Shaded}
-
-\includegraphics{Reddit_eda_files/figure-pdf/unnamed-chunk-6-2.pdf}
-
-Most posts occur during the early morning, noon, and afternoon hours.
-The highest peak is around lunchtime, likely due to people posting
-during their lunch break. There is also significant activity in the
-afternoon, evening, and early morning. This could be because people have
-more free time or stay up late, allowing them to take the time to write
-posts, which require more effort than quick interactions. The fewest
-posts are seen in the morning, which makes sense as people are typically
-getting ready for work, commuting, or sleeping in.
-
-The trend for comments mirrors that of posts. This makes sense because
-people are likely using Reddit at similar times for both posting and
-commenting. However, the volume of comments is much higher than the
-number of posts, as each post receives many comments from different
-users.
+\includegraphics{paper_files/figure-pdf/unnamed-chunk-5-2.pdf}
 
@@
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# tokenize words to count frequencies for reddit posts}
-\NormalTok{posts\_word\_counts }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_posts }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{select}\NormalTok{(title, text) }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{pivot\_longer}\NormalTok{(}\AttributeTok{cols =} \FunctionTok{c}\NormalTok{(title, text), }\AttributeTok{values\_drop\_na =} \ConstantTok{TRUE}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{unnest\_tokens}\NormalTok{(word, value) }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{count}\NormalTok{(word, }\AttributeTok{sort =} \ConstantTok{TRUE}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{slice\_max}\NormalTok{(n, }\AttributeTok{n =} \DecValTok{50}\NormalTok{)}
+\includegraphics{paper_files/figure-pdf/unnamed-chunk-6-1.pdf}
 
-\CommentTok{\# plot}
-\FunctionTok{ggplot}\NormalTok{(posts\_word\_counts, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =} \FunctionTok{reorder}\NormalTok{(word, n), }\AttributeTok{y =}\NormalTok{ n)) }\SpecialCharTok{+}
-  \FunctionTok{geom\_col}\NormalTok{(}\AttributeTok{fill =} \StringTok{"steelblue"}\NormalTok{) }\SpecialCharTok{+}
-  \FunctionTok{coord\_flip}\NormalTok{() }\SpecialCharTok{+}
-  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Top 50 Words in Reddit Posts (Including Stopwords)"}\NormalTok{,}
-       \AttributeTok{x =} \StringTok{"Word"}\NormalTok{,}
-       \AttributeTok{y =} \StringTok{"Count"}\NormalTok{) }\SpecialCharTok{+}
-  \FunctionTok{theme\_minimal}\NormalTok{()}
-\end{Highlighting}
-\end{Shaded}
-
-\includegraphics{Reddit_eda_files/figure-pdf/unnamed-chunk-7-1.pdf}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# tokenize words to count frequencies for reddit comments}
-\NormalTok{comments\_word\_counts }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_comment }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{select}\NormalTok{(comment) }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{pivot\_longer}\NormalTok{(}\AttributeTok{cols =} \FunctionTok{c}\NormalTok{(comment), }\AttributeTok{values\_drop\_na =} \ConstantTok{TRUE}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{unnest\_tokens}\NormalTok{(word, value) }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{count}\NormalTok{(word, }\AttributeTok{sort =} \ConstantTok{TRUE}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{slice\_max}\NormalTok{(n, }\AttributeTok{n =} \DecValTok{50}\NormalTok{)}
-
-\CommentTok{\# plot}
-\FunctionTok{ggplot}\NormalTok{(comments\_word\_counts, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =} \FunctionTok{reorder}\NormalTok{(word, n), }\AttributeTok{y =}\NormalTok{ n)) }\SpecialCharTok{+}
-  \FunctionTok{geom\_col}\NormalTok{(}\AttributeTok{fill =} \StringTok{"lightgreen"}\NormalTok{) }\SpecialCharTok{+}  \CommentTok{\# Removed extra parentheses}
-  \FunctionTok{coord\_flip}\NormalTok{() }\SpecialCharTok{+}
-  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Top 50 Words in Reddit Comments (Including Stopwords)"}\NormalTok{,}
-       \AttributeTok{x =} \StringTok{"Word"}\NormalTok{,}
-       \AttributeTok{y =} \StringTok{"Count"}\NormalTok{) }\SpecialCharTok{+}
-  \FunctionTok{theme\_minimal}\NormalTok{()}
-\end{Highlighting}
-\end{Shaded}
-
-\includegraphics{Reddit_eda_files/figure-pdf/unnamed-chunk-7-2.pdf}
+\includegraphics{paper_files/figure-pdf/unnamed-chunk-6-2.pdf}
 
@@
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# tokenize words to count frequencies for reddit posts removing stop words}
-\NormalTok{posts\_word\_counts }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_posts }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{select}\NormalTok{(title, text) }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{pivot\_longer}\NormalTok{(}\AttributeTok{cols =} \FunctionTok{c}\NormalTok{(title, text), }\AttributeTok{values\_drop\_na =} \ConstantTok{TRUE}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{unnest\_tokens}\NormalTok{(word, value) }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{anti\_join}\NormalTok{(stop\_words, }\AttributeTok{by =} \StringTok{"word"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{count}\NormalTok{(word, }\AttributeTok{sort =} \ConstantTok{TRUE}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{slice\_max}\NormalTok{(n, }\AttributeTok{n =} \DecValTok{50}\NormalTok{)}
+\includegraphics{paper_files/figure-pdf/unnamed-chunk-7-1.pdf}
 
-\CommentTok{\# plot}
-\FunctionTok{ggplot}\NormalTok{(posts\_word\_counts, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =} \FunctionTok{reorder}\NormalTok{(word, n), }\AttributeTok{y =}\NormalTok{ n)) }\SpecialCharTok{+}
-  \FunctionTok{geom\_col}\NormalTok{(}\AttributeTok{fill =} \StringTok{"steelblue"}\NormalTok{) }\SpecialCharTok{+}
-  \FunctionTok{coord\_flip}\NormalTok{() }\SpecialCharTok{+}
-  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Top 50 Words in Reddit Posts (Removing Stopwords)"}\NormalTok{,}
-       \AttributeTok{x =} \StringTok{"Word"}\NormalTok{,}
-       \AttributeTok{y =} \StringTok{"Count"}\NormalTok{) }\SpecialCharTok{+}
-  \FunctionTok{theme\_minimal}\NormalTok{()}
-\end{Highlighting}
-\end{Shaded}
-
-\includegraphics{Reddit_eda_files/figure-pdf/unnamed-chunk-8-1.pdf}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# tokenize words to count frequencies for Reddit comments, removing stop words}
-\NormalTok{comments\_word\_counts }\OtherTok{\textless{}{-}}\NormalTok{ reddit\_comment }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{select}\NormalTok{(comment) }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{pivot\_longer}\NormalTok{(}\AttributeTok{cols =} \FunctionTok{c}\NormalTok{(comment), }\AttributeTok{values\_drop\_na =} \ConstantTok{TRUE}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{unnest\_tokens}\NormalTok{(word, value) }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{anti\_join}\NormalTok{(stop\_words, }\AttributeTok{by =} \StringTok{"word"}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{count}\NormalTok{(word, }\AttributeTok{sort =} \ConstantTok{TRUE}\NormalTok{) }\SpecialCharTok{|\textgreater{}}
-  \FunctionTok{slice\_max}\NormalTok{(}\AttributeTok{order\_by =}\NormalTok{ n, }\AttributeTok{n =} \DecValTok{50}\NormalTok{)}
-
-\CommentTok{\# plot}
-\FunctionTok{ggplot}\NormalTok{(comments\_word\_counts, }\FunctionTok{aes}\NormalTok{(}\AttributeTok{x =} \FunctionTok{reorder}\NormalTok{(word, n), }\AttributeTok{y =}\NormalTok{ n)) }\SpecialCharTok{+}
-  \FunctionTok{geom\_col}\NormalTok{(}\AttributeTok{fill =} \StringTok{"lightgreen"}\NormalTok{) }\SpecialCharTok{+}  \CommentTok{\# Removed extra parentheses}
-  \FunctionTok{coord\_flip}\NormalTok{() }\SpecialCharTok{+}
-  \FunctionTok{labs}\NormalTok{(}\AttributeTok{title =} \StringTok{"Top 50 Words in Reddit Comments (Removing Stopwords)"}\NormalTok{,}
-       \AttributeTok{x =} \StringTok{"Word"}\NormalTok{,}
-       \AttributeTok{y =} \StringTok{"Count"}\NormalTok{) }\SpecialCharTok{+}
-  \FunctionTok{theme\_minimal}\NormalTok{()}
-\end{Highlighting}
-\end{Shaded}
-
-\includegraphics{Reddit_eda_files/figure-pdf/unnamed-chunk-8-2.pdf}
+\includegraphics{paper_files/figure-pdf/unnamed-chunk-7-2.pdf}
 
@@
 
+\emph{Coding Comments}. We coded 400 comments chosen at random
+
+\begin{longtable}[]{@{}lr@{}}
+\caption{Distribution of favorability coding for 400
+comments}\tabularnewline
+\toprule\noalign{}
+outcome & Total \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+outcome & Total \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+Not Coded & 12153 \\
+favor & 110 \\
+neutral & 73 \\
+oppose & 217 \\
+\end{longtable}
+
+\newpage
+
+\section{Appendix}\label{appendix}
+
+\begin{longtable}[]{@{}l@{}}
+\caption{List of subreddits relevant to the topic of
+DOGE}\tabularnewline
+\toprule\noalign{}
+subreddit \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+subreddit \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+50501 \\
+fednews \\
+neoliberal \\
+FedEmployees \\
+WhatTrumpHasDone \\
+Whistleblowers \\
+economy \\
+PoliticalOpinions \\
+Trumpvirus \\
+Virginia \\
+Libertarian \\
+AskTrumpSupporters \\
+Askpolitics \\
+Conservative \\
+VeteransAffairs \\
+economicCollapse \\
+feddiscussion \\
+maryland \\
+govfire \\
+\end{longtable}
+
 \end{document}

### 2025-03-21 code/paper.qmd
reduced visuals, expanded and edited interpretations, wrote conclusion

@@
 library(tidyverse)
+library(patchwork)
 
 # path to repo
-#repo_path <- str_c(~/Desktop/UMICH/SURV622_Assignment/data/") # felix
-repo_path <- str_c("~/repos/SURV622_Assignment/data/") # kevin
+repo_path <- str_c("~/Desktop/UMICH/SURV622_Assignment/data/") # felix
+# repo_path <- str_c("~/repos/SURV622_Assignment/data/") # kevin
 
@@
 
+*Post and Comment Trends*
+
 We show the number of posts pre/post processing by day in Figure 1 during the timeframe that we collected these data..
@@
 
+*Word Frequency*
+
 Most posts occur during the early morning, noon, and afternoon hours (see Figure 3).
@@
 The fewest posts are seen in the morning, which makes sense as people are typically getting ready for work, commuting, or sleeping in.
-The trend for comments (see Figure 4) mirrors that of posts.
+The trend for comments (see Figure 3) mirrors that of posts.
 This makes sense because people are likely using Reddit at similar times for both posting and commenting.
@@
 ```{r}
-posts_data_clean |> 
-  group_by(hour_posted ) |> 
+# Aggregate posts data
+posts_by_hour <- posts_data_clean |> 
+  group_by(hour_posted) |> 
   reframe(Total = n()) |> 
-  ggplot(aes(x=hour_posted, y=Total)) + 
-  # geom_bar(stat = "identity", fill = "steelblue") + 
-  geom_point(color = "blue", size = 3) +  
-  geom_line(color = "steelblue", linewidth = 1) +
+  mutate(type = "Posts")
+
+# Aggregate comments data
+comments_by_hour <- comments_data_clean |> 
+  group_by(hour_posted) |> 
+  reframe(Total = n()) |> 
+  mutate(type = "Comments")
+
+# Combine both datasets
+combined_data <- bind_rows(comments_by_hour, posts_by_hour)
+
+# Plot with facet_wrap to display them side by side
+ggplot(combined_data, aes(x = hour_posted, y = Total)) + 
+  geom_point(aes(color = type), size = 3) +  
+  geom_line(aes(color = type), linewidth = 1) +
+  scale_color_manual(values = c("Posts" = "steelblue", "Comments" = "lightgreen")) +  # Color distinction
+  facet_wrap(~type, scales = "free_y") +  # Display side by side
   labs(
-    title = "Figure 3. Total Number of Posts by Hour of Day",
+    title = "Figure 3. Total Number of Posts and Comments by Hour",
     subtitle = "(24-hour clock)",
     x = "Hour of Day",
-    y = "Total Number of Posts"
+    y = "Total Count"
   ) +
   theme_minimal() +
-  theme_hc()
-
-comments_data_clean |> 
-  group_by(hour_posted ) |> 
-  reframe(Total = n()) |> 
-  ggplot(aes(x=hour_posted, y=Total)) + 
-  # geom_bar(stat = "identity", fill = "steelblue") + 
-  geom_point(color = "green", size = 3) +  
-  geom_line(color = "lightgreen", linewidth = 1) +
-  labs(
-    title = "Figure 4. Total Number of Comments by Hour of Day",
-    subtitle = "(24-hour clock)",
-    x = "Hour of Day",
-    y = "Total Number of Posts"
-  ) +
-  theme_hc()
+  theme_hc() +
+  theme(legend.position = "none") 
 ```
 
-### What are the words in the set of posts you have assembled that appear most frequently?
+The graphs below (Figure 4) show the most frequent words used in both Reddit posts and their comment sections.
+These words were identified by tokenizing the text and removing stop words, then counting the occurrences of the most common terms.
+From the visualizations, we can see that many of these words are directly related to our topic of discussion.
+Specifically, there are frequent mentions of 'President,' 'DOGE,' 'federal government,' and 'RIF,' which suggest that discussions surrounding political events, cryptocurrency (like Dogecoin), and government-related issues are significant in the posts and comments.
+This highlights the focus of the community on these key themes, reflecting the ongoing conversations and interests of Reddit users within this context.
 
 ```{r}
-#| fig-width: 6
-#| fig-height: 7
-#| 
-# tokenize words to count frequencies for reddit posts
-posts_word_counts <- posts_data_clean |>
-  select(title, text) |>
-  pivot_longer(cols = c(title, text), values_drop_na = TRUE) |>
-  unnest_tokens(word, value) |>
-  count(word, sort = TRUE) |>
-  slice_max(n, n = 50)
-
-# plot
-ggplot(posts_word_counts, aes(x = reorder(word, n), y = n)) +
-  geom_col(fill = "steelblue") +
-  coord_flip() +
-  labs(title = "Top 50 Words in Reddit Posts (Including Stopwords)",
-       x = "Word",
-       y = "Count") +
-  theme_minimal()
-
-# tokenize words to count frequencies for reddit comments
-comments_word_counts <- comments_data_clean |>
-  select(comment) |>
-  pivot_longer(cols = c(comment), values_drop_na = TRUE) |>
-  unnest_tokens(word, value) |>
-  count(word, sort = TRUE) |>
-  slice_max(n, n = 50)
-
-# plot
-ggplot(comments_word_counts, aes(x = reorder(word, n), y = n)) +
-  geom_col(fill = "lightgreen") +  # Removed extra parentheses
-  coord_flip() +
-  labs(title = "Top 50 Words in Reddit Comments (Including Stopwords)",
-       x = "Word",
-       y = "Count") +
-  theme_minimal()
-```
-
-The graphs above show the most frequent words in both Reddit posts and their comments.
-However, many of these words are stopwords, which don't provide much insight into the actual content of the discussions.
-To get a better understanding of what people are really talking about, we will remove these stopwords in the next step.
-
-### How does this change if you exclude “stop words” such as “a,” “an,” “the,” “is,” and others that are common in English sentences but are generally not informative?
-
-```{r}
-#| fig-width: 6
-#| fig-height: 7
-#| #| 
-# tokenize words to count frequencies for reddit posts removing stop words
+# Tokenize words and count frequencies for Reddit posts
 posts_word_counts <- posts_data_clean |>
@@
   count(word, sort = TRUE) |>
-  slice_max(n, n = 50)
+  slice_max(n, n = 25)
 
-# plot
-ggplot(posts_word_counts, aes(x = reorder(word, n), y = n)) +
-  geom_col(fill = "steelblue") +
-  coord_flip() +
-  labs(title = "Top 50 Words in Reddit Posts (Removing Stopwords)",
-       x = "Word",
-       y = "Count") +
-  theme_minimal()
-
-# tokenize words to count frequencies for Reddit comments, removing stop words
+# Tokenize words and count frequencies for Reddit comments
 comments_word_counts <- comments_data_clean |>
@@
   count(word, sort = TRUE) |>
-  slice_max(order_by = n, n = 50)
+  slice_max(order_by = n, n = 25)
 
-# plot
-ggplot(comments_word_counts, aes(x = reorder(word, n), y = n)) +
-  geom_col(fill = "lightgreen") +  # Removed extra parentheses
+# Plot for posts
+plot_posts <- ggplot(posts_word_counts, aes(x = reorder(word, n), y = n)) +
+  geom_col(fill = "steelblue") +
   coord_flip() +
-  labs(title = "Top 50 Words in Reddit Comments (Removing Stopwords)",
-       x = "Word",
+  labs(x = "Word",
        y = "Count") +
   theme_minimal()
+
+# Plot for comments
+plot_comments <- ggplot(comments_word_counts, aes(x = reorder(word, n), y = n)) +
+  geom_col(fill = "lightgreen") +
+  coord_flip() +
+  labs(x = "Word",
+       y = "Count") +
+  theme_minimal()
+
+# Combine them side by side using patchwork
+combined_plot <- plot_posts + plot_comments + plot_layout(ncol = 2) + plot_annotation(title = "Figure 4. Top 25 Words in Reddit Posts and Comments")
+
+# Display the combined plot
+combined_plot
+
 ```
 
-The graphs above show the most frequent words used in both Reddit posts and their comment sections.
-We can see that many of these words are directly related to our topic, with frequent mentions of the President, DOGE, the federal government, and RIF.
+*Coding Comments*
 
-*Coding Comments*.
-We coded 400 comments chosen at random
+We randomly selected and coded 400 comments from the Reddit posts.
+The table below shows the distribution of favorability coding for these comments.
+Among the 400 comments, the majority (217) expressed opposition to DOGE's approach to reducing the federal workforce, while 110 were supportive, and 73 remained neutral.
+A large number of comments (12,153) were not coded, as their content was not relevant for favorability assessment.
 
@@
 
+## Conclusion
+
+In this study, we explored the impact of the Department of Government Efficiency’s (DOGE) actions on federal workers’ perceptions of job security, using Reddit as a platform to analyze public discourse.
+By examining Reddit posts and comments related to DOGE’s workforce reduction policies, we gained valuable insights into the sentiments of both federal workers and the broader public.
+Our findings indicate that these discussions are heavily influenced by political events and high-profile figures, such as President Trump and Elon Musk, with particular attention given to DOGE’s controversial cost-cutting measures.
+Through the analysis of both posts and comments, we captured a wide range of reactions, with the majority being strongly opposed to DOGE’s approach.
+The frequent mention of terms like ‘President,’ ‘DOGE,’ ‘federal government,’ and ‘RIF’ underscores the community’s focus on government policies and the emotional responses these issues generate.
+
+In terms of favorability, the distribution of comments revealed that 217 out of 400 were opposed to DOGE’s approach, 110 were supportive, and 73 were neutral.
+Additionally, patterns in post volume, especially peaks during significant news events, highlight the dynamic nature of these discussions, providing insights into the timing and public reactions to key policy decisions.
+While our study provides a snapshot of Reddit discussions during a specific period, the findings demonstrate the value of social media platforms like Reddit in capturing public sentiment on contemporary political and policy issues.
+However, it’s important to note that Reddit may not fully represent the broader population’s views, as the platform tends to skew younger and more politically engaged, potentially limiting the generalizability of these findings.
+
+Furthermore, the use of sentiment analysis on social media presents challenges, as it can be influenced by sarcasm, humor, or polarized language, which might affect the accuracy of sentiment classification.
+The specific subreddits analyzed, while designed to capture diverse perspectives, may still over-represent certain political or ideological viewpoints.
+Additionally, the relatively short timeframe of this analysis—spanning only March 2-10, 2025—means that we may not have captured long-term trends or shifts in sentiment as the DOGE policies unfold.
+Future research could address these limitations by expanding the data collection to other platforms or a longer timeframe and by incorporating demographic data to better understand the views of different Reddit user groups.
+
 \newpage

### 2025-03-21 code/paper.tex
reduced visuals, expanded and edited interpretations, wrote conclusion

@@
 
+\emph{Post and Comment Trends}
+
 We show the number of posts pre/post processing by day in Figure 1
@@
 
+\emph{Word Frequency}
+
 Most posts occur during the early morning, noon, and afternoon hours
@@
 sense as people are typically getting ready for work, commuting, or
-sleeping in. The trend for comments (see Figure 4) mirrors that of
+sleeping in. The trend for comments (see Figure 3) mirrors that of
 posts. This makes sense because people are likely using Reddit at
@@
 
-\includegraphics{paper_files/figure-pdf/unnamed-chunk-5-2.pdf}
-
-\subsection{What are the words in the set of posts you have assembled
-that appear most
-frequently?}\label{what-are-the-words-in-the-set-of-posts-you-have-assembled-that-appear-most-frequently}
+The graphs below (Figure 4) show the most frequent words used in both
+Reddit posts and their comment sections. These words were identified by
+tokenizing the text and removing stop words, then counting the
+occurrences of the most common terms. From the visualizations, we can
+see that many of these words are directly related to our topic of
+discussion. Specifically, there are frequent mentions of `President,'
+`DOGE,' `federal government,' and `RIF,' which suggest that discussions
+surrounding political events, cryptocurrency (like Dogecoin), and
+government-related issues are significant in the posts and comments.
+This highlights the focus of the community on these key themes,
+reflecting the ongoing conversations and interests of Reddit users
+within this context.
 
@@
 
-\includegraphics{paper_files/figure-pdf/unnamed-chunk-6-2.pdf}
+\emph{Coding Comments}
 
-The graphs above show the most frequent words in both Reddit posts and
-their comments. However, many of these words are stopwords, which don't
-provide much insight into the actual content of the discussions. To get
-a better understanding of what people are really talking about, we will
-remove these stopwords in the next step.
-
-\subsection{How does this change if you exclude ``stop words'' such as
-``a,'' ``an,'' ``the,'' ``is,'' and others that are common in English
-sentences but are generally not
-informative?}\label{how-does-this-change-if-you-exclude-stop-words-such-as-a-an-the-is-and-others-that-are-common-in-english-sentences-but-are-generally-not-informative}
-
-\includegraphics{paper_files/figure-pdf/unnamed-chunk-7-1.pdf}
-
-\includegraphics{paper_files/figure-pdf/unnamed-chunk-7-2.pdf}
-
-The graphs above show the most frequent words used in both Reddit posts
-and their comment sections. We can see that many of these words are
-directly related to our topic, with frequent mentions of the President,
-DOGE, the federal government, and RIF.
-
-\emph{Coding Comments}. We coded 400 comments chosen at random
+We randomly selected and coded 400 comments from the Reddit posts. The
+table below shows the distribution of favorability coding for these
+comments. Among the 400 comments, the majority (217) expressed
+opposition to DOGE's approach to reducing the federal workforce, while
+110 were supportive, and 73 remained neutral. A large number of comments
+(12,153) were not coded, as their content was not relevant for
+favorability assessment.
 
@@
 \end{longtable}
+
+\section{Conclusion}\label{conclusion}
+
+In this study, we explored the impact of the Department of Government
+Efficiency's (DOGE) actions on federal workers' perceptions of job
+security, using Reddit as a platform to analyze public discourse. By
+examining Reddit posts and comments related to DOGE's workforce
+reduction policies, we gained valuable insights into the sentiments of
+both federal workers and the broader public. Our findings indicate that
+these discussions are heavily influenced by political events and
+high-profile figures, such as President Trump and Elon Musk, with
+particular attention given to DOGE's controversial cost-cutting
+measures. Through the analysis of both posts and comments, we captured a
+wide range of reactions, with the majority being strongly opposed to
+DOGE's approach. The frequent mention of terms like `President,' `DOGE,'
+`federal government,' and `RIF' underscores the community's focus on
+government policies and the emotional responses these issues generate.
+
+In terms of favorability, the distribution of comments revealed that 217
+out of 400 were opposed to DOGE's approach, 110 were supportive, and 73
+were neutral. Additionally, patterns in post volume, especially peaks
+during significant news events, highlight the dynamic nature of these
+discussions, providing insights into the timing and public reactions to
+key policy decisions. While our study provides a snapshot of Reddit
+discussions during a specific period, the findings demonstrate the value
+of social media platforms like Reddit in capturing public sentiment on
+contemporary political and policy issues. However, it's important to
+note that Reddit may not fully represent the broader population's views,
+as the platform tends to skew younger and more politically engaged,
+potentially limiting the generalizability of these findings.
+
+Furthermore, the use of sentiment analysis on social media presents
+challenges, as it can be influenced by sarcasm, humor, or polarized
+language, which might affect the accuracy of sentiment classification.
+The specific subreddits analyzed, while designed to capture diverse
+perspectives, may still over-represent certain political or ideological
+viewpoints. Additionally, the relatively short timeframe of this
+analysis---spanning only March 2-10, 2025---means that we may not have
+captured long-term trends or shifts in sentiment as the DOGE policies
+unfold. Future research could address these limitations by expanding the
+data collection to other platforms or a longer timeframe and by
+incorporating demographic data to better understand the views of
+different Reddit user groups.
 

### 2025-03-21 code/paper.qmd
final paper draft

@@
 abstract: |
-  This study explores the impact of the Department of Government Efficiency (DOGE)'s federal workforce reductions on public sentiment, utilizing Reddit as a data source.
-By scraping and analyzing posts and comments related to DOGE, we examined public reactions, including fear, anxiety, and support, during a period of significant governmental change.
-The analysis reveals how specific news events influenced online discourse and highlights the utility of social media for understanding public perception of policy impacts.
+  This study explores the impact of the Department of Government Efficiency (DOGE)'s federal workforce reductions, known as reduction in force (RIF), on public sentiment, utilizing Reddit as a data source.
+We scraped the Reddit API from March 2nd to March 10th resulting in 557 unique posts with 12,553 comments from subreddits related to DOGE's approach to the RIF.
+Our exploratory analysis captures peaks in the number of posts/comments following major news event coverage related to the RIF, highlighting the utility of social media for understanding public perception of policy impacts.
+Our text analysis reveals a saliency on community with words such as people, employees, service, public, workers, and care being top words in both posts and comments.
+Moreover, a team of researchers coded a random subset of comments for public sentiment and found that only a quarter approved of DOGE's actions towards the RIF.
+
 keywords:
@@
 # path to repo
-repo_path <- str_c("~/Desktop/UMICH/SURV622_Assignment/data/") # felix
-# repo_path <- str_c("~/repos/SURV622_Assignment/data/") # kevin
+#repo_path <- str_c("~/Desktop/UMICH/SURV622_Assignment/data/") # felix
+repo_path <- str_c("~/repos/SURV622_Assignment/data/") # kevin
 
@@
 
-Since it's inception in January of 2025, the Department of Government Efficiency (DOGE) has fired over 200,000 federal workers in an effort by the new administration to keep a campaign promise in reducing federal government.
-However, DOGE's overreaching approach and often illegal tactics has resulted sparked fear and anxiety among the federal workforce, thus taking a toll on their mental health.
-Many are uncertain about their career faith as it is in the hands of outsiders that disregard internal policies with no remorse.
-The current topic on how DOGE is impacting federal worker's perceptions of job security is likely to continue and worsen over the next few months, given DOGE's nontransparent and unconventional methods without accountability.
-We propose that Reddit as a platform offers researchers a vantage look into lively discussions, timely reactions, and grievances from federal workers on this topic.
-Furthermore, we also expect to capture positive reactions to DOGE's approach in reducing the federal workforce.
+Since its inception in January 2025, the Department of Government Efficiency (DOGE) has implemented significant reductions in the federal workforce, resulting in the separation of over 200,000 employees, in alignment with the new administration's campaign promises.
+These reductions have generated widespread concern and anxiety among federal workers regarding their job security and mental well-being.
+Reports indicate that DOGE's methods have raised questions about adherence to established internal policies.
+The ongoing debate surrounding DOGE's impact on federal worker perceptions of job security necessitates a thorough examination.
+This study proposes that Reddit, as a platform for public discourse, provides researchers with valuable insights into real-time reactions and discussions among federal workers on this topic.
+Furthermore, this research aims to capture a range of public sentiments, including both critical and supportive perspectives, regarding DOGE's workforce reduction efforts.
 
@@
 *Search Terms*.
-Our preliminary Reddit API scrape allowed us to decide on a set of keyword searches related to this topic of research.
-This was an iterative process that resulted in the use of 8 keywords we used to search for posts related to the topic of interest (see Table 1).
-We excluded keywords that were either vague or broad such as "Elon Musk" or "drain the swamp." Additionally, we examined subreddit posts and found a plethora of unrelated posts using our keyword search list.
-For instance, searching for "Fork in the Road" brought back several subreddits on motorcycles and mountain biking.
-Additionally, searching for "DOGE" also brought back posts on DOGEcoin which is unrelated to our topic.
-Therefore, we meticoulsly combed through a list of subreddits we acquired from our initial scrape and selected those that contaiend relevant posts.
-To compensate for balance on this topic, we included conservative subreddits such as "neoliberal", "AskConservitives" as well as we avoided specific agency subreddits, for instance "NIH" or "CDC" as to not overwhelm one particular view point.
-Overall we ended with 19 subreddits (see appendix) and 8 keywords resulting in 152 unique combinations to scrape.
+Our initial Reddit API scrape facilitated the development of a targeted keyword search strategy for this research.
+This iterative process resulted in the selection of eight keywords (see Table 1).
+We excluded keywords deemed vague or overly broad, such as 'Elon Musk' or 'drain the swamp.' Additionally, we observed that certain keywords yielded a high volume of irrelevant posts.
+For example, 'policy changes' returned numerous discussions unrelated to government workforce reductions.
+Similarly, 'DOGE' produced results related to DOGEcoin, which is outside the scope of this study.
+Therefore, we meticulously examined the subreddits identified in our initial scrape and selected those containing relevant discussions.
+To ensure a balanced representation of viewpoints, we included subreddits with conservative perspectives, such as 'neoliberal' and 'AskConservatives,' while avoiding subreddits focused on specific agencies like 'NIH' or 'CDC,' which could skew the data.
+In total, we selected 19 subreddits (see Appendix A) and utilized eight keywords, resulting in 152 unique keyword and subreddit combinations for our data collection.
 
@@
 *Analytic Plan*.
-We listened to the Reddit API from March 2 through the 10th on every top of the hour by scraping each combination of our seven keywords and 20 subreddits resulting in 152 API hits per hour.
-Reddit API scraping limits were managed by setting a sleep timer in between API hits.
-As new Reddit posts were scraped they were entered into a data table without preprocessing.
-After the listening period, the accumulated number of unprocessed posts was 643.
-Every row in our data table equated to one post, and we had 8 columns to include the date and time of the post, title and text of post, subreddit where the post derived from, number of comments associated with it, url, and we recorded the search term that was used to collect the post.
-We processed the posts to exclude duplicates, and in some instance two different keywords resulted in scraping the same posts so we kept we dropped one of them.
-Post text were cleaned in terms of removing weblinks and when possible translating special character such as the at sign to the word "at." The date column was converted to a date class variable and we extracted the day of the week and time of day from it to use in analysis.
-Cleaning our scraped posts resulted in 557 posts.
+We collected data from the Reddit API hourly, from March 2nd through the 10th, by scraping each combination of our eight keywords and 19 subreddits, resulting in 152 API requests per hour.
+Reddit API rate limits were managed by implementing a sleep timer between requests.
+Raw data from new Reddit posts were entered into a data table without initial processing.
+Following the data collection period, the raw dataset contained 643 posts.
+Each row in the data table represented a single post, and the columns included the post's date and time, title, text, subreddit, comment count, URL, and the search term used for collection.
+Duplicate posts, which occurred when multiple keywords matched the same post, were removed.
+Post text was cleaned by removing weblinks and converting special characters, such as the at sign, to the word 'at.' The date column was converted to a date class variable, and the day of the week and time of day were extracted for analysis.
+After cleaning, the dataset consisted of 557 posts.
 
-A glance at the posts revealed that many of them are factual statements, questions, or re-postings of news articles and videos.
-Therefore, these texts do not lend themselves to be coded for favorability, and we decided to also scrape the comments associated with each post.
-This resulted in 12,553 comments, post processing, containing information about the score, up/down votes, and date/time posted.
-We removed comments that had only a weblink, video, or image as these cannot be coded.
-A look into some of these comments revealed more opinionated statements and reactions which we than randomly (without replacement) selected 400 comments assigned to four graduate students to code for whether the comment favored DOGE's approach to the reduction in the federal force, opposed, or was neutral.
+A preliminary review of the posts revealed that many were factual statements, questions, or reposted news articles and videos, which were not suitable for sentiment coding.
+Therefore, we also scraped the comments associated with each post.
+This resulted in 12,553 comments after processing, including information on score, up/down votes, and date/time.
+Comments containing only weblinks, videos, or images were removed.
+A review of the comments revealed more opinionated statements and reactions.
+We then randomly selected 400 comments (without replacement) and assigned them to four graduate students for coding, categorizing each comment as favoring, opposing, or neutral towards DOGE's approach to federal workforce reductions.
 
@@
 
-We show the number of posts pre/post processing by day in Figure 1 during the timeframe that we collected these data..
+We show the number of posts pre/post processing by day in Figure 1 during the timeframe that we collected these data.
 There appears to be a noticeable peak in activity during the middle of the week.
-However, we don't have enough data across weeks to conclusively say it's due to the day of the week itself.
-It's more likely that these spikes are linked to specific events that occurred on those days, which sparked conversations.
+However, we don't have enough data across weeks to conclusively say it is due to the day of the week itself.
+It is more likely that these spikes are linked to specific events that occurred on those days, which sparked conversations.
 The two peaks in our graph could be attributed to two major news stories.
-On March 5, Elon Musk made a statement about wanting to "save Western civilization from empathy," and on March 6, there were reports that President Trump was limiting Musk's authority due to backlash over cuts to DOGE.
+On March 5th, Elon Musk made a statement about wanting to "save Western civilization from empathy," and on March 6th, there were reports that President Trump was limiting Musk's authority due to backlash over cuts to DOGE.
 These events likely had a significant impact on the volume of Reddit posts related to Elon Musk and DOGE, driving the observed spikes in activity.
 
-On May third, news outlets started reporting that DOGE was claiming \$105 billion dollars in savings from cutting "wasteful" spending by layoffs and cutting foreign aid.
+On March 3rd, news outlets started reporting that DOGE was claiming \$105 billion dollars in savings from cutting "wasteful" spending by layoffs and cutting foreign aid.
 This amount is controversial since since the receipts shown on their site only amount to less than [\$9.6 billion](https://abcnews.go.com/US/doge-website-now-saved-105-billion-backtracked-earlier/story?id=119408347).
@@
 
-We see a peak in the comments in Figure 2 during March 6th, which was a Thursday, and perhaps in anticipation of DOGE policies that often are released on Friday morning and have come to be known as "[Musk-acre Friday](https://smotus.substack.com/p/friday-night-musk-acre)."
+We see a peak in the comments in Figure 2 on March 6th, which was a Thursday, and perhaps in anticipation of DOGE policies that often are released on Friday morning and have come to be known as "[Musk-acre Friday](https://smotus.substack.com/p/friday-night-musk-acre)."
 
@@
 There is also significant activity in the afternoon, evening, and early morning.
-This could be because people have more free time or stay up late, allowing them to take the time to write posts, which require more effort than quick interactions.
+It is possible that people have more time in the evenings allowing them to be more likely to post on Reddit.
 The fewest posts are seen in the morning, which makes sense as people are typically getting ready for work, commuting, or sleeping in.
@@
 
-The graphs below (Figure 4) show the most frequent words used in both Reddit posts and their comment sections.
+The graphs below (Figure 4) show the most frequent words used in both Reddit posts and their comment sections while excluding our keyword search terms.
 These words were identified by tokenizing the text and removing stop words, then counting the occurrences of the most common terms.
-From the visualizations, we can see that many of these words are directly related to our topic of discussion.
-Specifically, there are frequent mentions of 'President,' 'DOGE,' 'federal government,' and 'RIF,' which suggest that discussions surrounding political events, cryptocurrency (like Dogecoin), and government-related issues are significant in the posts and comments.
+Examining this visual reveals that in posts the current president's name is the top word.
+However, in both posts and comments, there appears to be an emerging theme of community as words like people, employees, service, care, jobs, and public are also top words.
 This highlights the focus of the community on these key themes, reflecting the ongoing conversations and interests of Reddit users within this context.
@@
 ```{r}
+#| fig-width: 6
+#| fig-height: 6
+#| 
+keywords <- posts_data_clean |>
+    select( search_term) |>
+    pivot_longer(cols = search_term, values_drop_na = TRUE) |>
+    unnest_tokens(word, value) |> 
+  distinct(word) |> 
+  pull()
+
 # Tokenize words and count frequencies for Reddit posts
 posts_word_counts <- posts_data_clean |>
-  select(title, text) |>
-  pivot_longer(cols = c(title, text), values_drop_na = TRUE) |>
+  select( text) |>
+  pivot_longer(cols = text, values_drop_na = TRUE) |>
   unnest_tokens(word, value) |>
@@
   count(word, sort = TRUE) |>
-  slice_max(n, n = 25)
+  # remove keywords
+  filter(!(word %in% keywords),
+         # filter out numbers
+         !str_detect(word, "[:digit:]") ) |> 
+  slice_max(n, n = 30)
 
@@
   select(comment) |>
-  pivot_longer(cols = c(comment), values_drop_na = TRUE) |>
+  pivot_longer(cols = comment, values_drop_na = TRUE) |>
   unnest_tokens(word, value) |>
@@
   count(word, sort = TRUE) |>
-  slice_max(order_by = n, n = 25)
+  # remove keywords
+  filter(!(word %in% keywords),
+         # filter out numbers
+         !str_detect(word, "[:digit:]") ) |> 
+  slice_max(order_by = n, n = 30)
 
@@
 We randomly selected and coded 400 comments from the Reddit posts.
-The table below shows the distribution of favorability coding for these comments.
+Table 2 shows the distribution of favorability coding for these comments.
 Among the 400 comments, the majority (217) expressed opposition to DOGE's approach to reducing the federal workforce, while 110 were supportive, and 73 remained neutral.
@@
 
-In this study, we explored the impact of the Department of Government Efficiency’s (DOGE) actions on federal workers’ perceptions of job security, using Reddit as a platform to analyze public discourse.
-By examining Reddit posts and comments related to DOGE’s workforce reduction policies, we gained valuable insights into the sentiments of both federal workers and the broader public.
+In this study, we explored the impact of the DOGE's actions towards the reduction in force impacting federal workers’ perceptions of job security, using Reddit as a platform to analyze public discourse.
+In examining Reddit posts and comments related to DOGE’s workforce reduction policies, we gained valuable insights into the sentiments of both federal workers and the broader public.
 Our findings indicate that these discussions are heavily influenced by political events and high-profile figures, such as President Trump and Elon Musk, with particular attention given to DOGE’s controversial cost-cutting measures.
 Through the analysis of both posts and comments, we captured a wide range of reactions, with the majority being strongly opposed to DOGE’s approach.
-The frequent mention of terms like ‘President,’ ‘DOGE,’ ‘federal government,’ and ‘RIF’ underscores the community’s focus on government policies and the emotional responses these issues generate.
+The frequent mention of terms related to the administration underscores the community’s focus on government policies and the emotional responses these issues generate.
 
@@
 While our study provides a snapshot of Reddit discussions during a specific period, the findings demonstrate the value of social media platforms like Reddit in capturing public sentiment on contemporary political and policy issues.
-However, it’s important to note that Reddit may not fully represent the broader population’s views, as the platform tends to skew younger and more politically engaged, potentially limiting the generalizability of these findings.
+However, it is important to note that Reddit may not fully represent the broader population’s views, as the platform tends to skew younger and more politically engaged, potentially limiting the generalizability of these findings.
 
-Furthermore, the use of sentiment analysis on social media presents challenges, as it can be influenced by sarcasm, humor, or polarized language, which might affect the accuracy of sentiment classification.
+The use of sentiment analysis on social media presents challenges, as it can be influenced by sarcasm, humor, or polarized language, which might affect the accuracy of sentiment classification.
+Therefore, our research team hand coded a subset of comments, yet inter-rater reliability was not estimated.
 The specific subreddits analyzed, while designed to capture diverse perspectives, may still over-represent certain political or ideological viewpoints.
-Additionally, the relatively short timeframe of this analysis—spanning only March 2-10, 2025—means that we may not have captured long-term trends or shifts in sentiment as the DOGE policies unfold.
+Moreover, the relatively short timeframe of this analysis—spanning only March 2nd to March 10th—means that we may not have captured long-term trends or shifts in sentiment as the DOGE policies unfold.
 Future research could address these limitations by expanding the data collection to other platforms or a longer timeframe and by incorporating demographic data to better understand the views of different Reddit user groups.
@@
 
+We examined almost 100 subreddit posts while paying attention to the post topics and determined which ones were related to our topic.
+We also included right leaning subreddits to attempt to capture a balanced public sentiment on the topic.
+The following is our final list of subreddits that we scraped from.
+
 ```{r}

### 2025-03-21 code/paper.tex
final paper draft

@@
 
-\date{March 20, 2025}
+\date{March 21, 2025}
 \title{\bf DOGE Days on Reddit: Decoding Public Sentiment in a Federal
@@
 This study explores the impact of the Department of Government
-Efficiency (DOGE)'s federal workforce reductions on public sentiment,
-utilizing Reddit as a data source. By scraping and analyzing posts and
-comments related to DOGE, we examined public reactions, including fear,
-anxiety, and support, during a period of significant governmental
-change. The analysis reveals how specific news events influenced online
-discourse and highlights the utility of social media for understanding
-public perception of policy impacts.
+Efficiency (DOGE)'s federal workforce reductions, known as reduction in
+force (RIF), on public sentiment, utilizing Reddit as a data source. We
+scraped the Reddit API from March 2nd to March 10th resulting in 557
+unique posts with 12,553 comments from subreddits related to DOGE's
+approach to the RIF. Our exploratory analysis captures peaks in the
+number of posts/comments following major news event coverage related to
+the RIF, highlighting the utility of social media for understanding
+public perception of policy impacts. Our text analysis reveals a
+saliency on community with words such as people, employees, service,
+public, workers, and care being top words in both posts and comments.
+Moreover, a team of researchers coded a random subset of comments for
+public sentiment and found that only a quarter approved of DOGE's
+actions towards the RIF.
 \end{abstract}
@@
 
-Since it's inception in January of 2025, the Department of Government
-Efficiency (DOGE) has fired over 200,000 federal workers in an effort by
-the new administration to keep a campaign promise in reducing federal
-government. However, DOGE's overreaching approach and often illegal
-tactics has resulted sparked fear and anxiety among the federal
-workforce, thus taking a toll on their mental health. Many are uncertain
-about their career faith as it is in the hands of outsiders that
-disregard internal policies with no remorse. The current topic on how
-DOGE is impacting federal worker's perceptions of job security is likely
-to continue and worsen over the next few months, given DOGE's
-nontransparent and unconventional methods without accountability. We
-propose that Reddit as a platform offers researchers a vantage look into
-lively discussions, timely reactions, and grievances from federal
-workers on this topic. Furthermore, we also expect to capture positive
-reactions to DOGE's approach in reducing the federal workforce.
+Since its inception in January 2025, the Department of Government
+Efficiency (DOGE) has implemented significant reductions in the federal
+workforce, resulting in the separation of over 200,000 employees, in
+alignment with the new administration's campaign promises. These
+reductions have generated widespread concern and anxiety among federal
+workers regarding their job security and mental well-being. Reports
+indicate that DOGE's methods have raised questions about adherence to
+established internal policies. The ongoing debate surrounding DOGE's
+impact on federal worker perceptions of job security necessitates a
+thorough examination. This study proposes that Reddit, as a platform for
+public discourse, provides researchers with valuable insights into
+real-time reactions and discussions among federal workers on this topic.
+Furthermore, this research aims to capture a range of public sentiments,
+including both critical and supportive perspectives, regarding DOGE's
+workforce reduction efforts.
 
@@
 
-\emph{Search Terms}. Our preliminary Reddit API scrape allowed us to
-decide on a set of keyword searches related to this topic of research.
-This was an iterative process that resulted in the use of 8 keywords we
-used to search for posts related to the topic of interest (see Table 1).
-We excluded keywords that were either vague or broad such as ``Elon
-Musk'' or ``drain the swamp.'' Additionally, we examined subreddit posts
-and found a plethora of unrelated posts using our keyword search list.
-For instance, searching for ``Fork in the Road'' brought back several
-subreddits on motorcycles and mountain biking. Additionally, searching
-for ``DOGE'' also brought back posts on DOGEcoin which is unrelated to
-our topic. Therefore, we meticoulsly combed through a list of subreddits
-we acquired from our initial scrape and selected those that contaiend
-relevant posts. To compensate for balance on this topic, we included
-conservative subreddits such as ``neoliberal'', ``AskConservitives'' as
-well as we avoided specific agency subreddits, for instance ``NIH'' or
-``CDC'' as to not overwhelm one particular view point. Overall we ended
-with 19 subreddits (see appendix) and 8 keywords resulting in 152 unique
-combinations to scrape.
+\emph{Search Terms}. Our initial Reddit API scrape facilitated the
+development of a targeted keyword search strategy for this research.
+This iterative process resulted in the selection of eight keywords (see
+Table 1). We excluded keywords deemed vague or overly broad, such as
+`Elon Musk' or `drain the swamp.' Additionally, we observed that certain
+keywords yielded a high volume of irrelevant posts. For example, `policy
+changes' returned numerous discussions unrelated to government workforce
+reductions. Similarly, `DOGE' produced results related to DOGEcoin,
+which is outside the scope of this study. Therefore, we meticulously
+examined the subreddits identified in our initial scrape and selected
+those containing relevant discussions. To ensure a balanced
+representation of viewpoints, we included subreddits with conservative
+perspectives, such as `neoliberal' and `AskConservatives,' while
+avoiding subreddits focused on specific agencies like `NIH' or `CDC,'
+which could skew the data. In total, we selected 19 subreddits (see
+Appendix A) and utilized eight keywords, resulting in 152 unique keyword
+and subreddit combinations for our data collection.
 
@@
 
-\emph{Analytic Plan}. We listened to the Reddit API from March 2 through
-the 10th on every top of the hour by scraping each combination of our
-seven keywords and 20 subreddits resulting in 152 API hits per hour.
-Reddit API scraping limits were managed by setting a sleep timer in
-between API hits. As new Reddit posts were scraped they were entered
-into a data table without preprocessing. After the listening period, the
-accumulated number of unprocessed posts was 643. Every row in our data
-table equated to one post, and we had 8 columns to include the date and
-time of the post, title and text of post, subreddit where the post
-derived from, number of comments associated with it, url, and we
-recorded the search term that was used to collect the post. We processed
-the posts to exclude duplicates, and in some instance two different
-keywords resulted in scraping the same posts so we kept we dropped one
-of them. Post text were cleaned in terms of removing weblinks and when
-possible translating special character such as the at sign to the word
-``at.'' The date column was converted to a date class variable and we
-extracted the day of the week and time of day from it to use in
-analysis. Cleaning our scraped posts resulted in 557 posts.
+\emph{Analytic Plan}. We collected data from the Reddit API hourly, from
+March 2nd through the 10th, by scraping each combination of our eight
+keywords and 19 subreddits, resulting in 152 API requests per hour.
+Reddit API rate limits were managed by implementing a sleep timer
+between requests. Raw data from new Reddit posts were entered into a
+data table without initial processing. Following the data collection
+period, the raw dataset contained 643 posts. Each row in the data table
+represented a single post, and the columns included the post's date and
+time, title, text, subreddit, comment count, URL, and the search term
+used for collection. Duplicate posts, which occurred when multiple
+keywords matched the same post, were removed. Post text was cleaned by
+removing weblinks and converting special characters, such as the at
+sign, to the word `at.' The date column was converted to a date class
+variable, and the day of the week and time of day were extracted for
+analysis. After cleaning, the dataset consisted of 557 posts.
 
-A glance at the posts revealed that many of them are factual statements,
-questions, or re-postings of news articles and videos. Therefore, these
-texts do not lend themselves to be coded for favorability, and we
-decided to also scrape the comments associated with each post. This
-resulted in 12,553 comments, post processing, containing information
-about the score, up/down votes, and date/time posted. We removed
-comments that had only a weblink, video, or image as these cannot be
-coded. A look into some of these comments revealed more opinionated
-statements and reactions which we than randomly (without replacement)
-selected 400 comments assigned to four graduate students to code for
-whether the comment favored DOGE's approach to the reduction in the
-federal force, opposed, or was neutral.
+A preliminary review of the posts revealed that many were factual
+statements, questions, or reposted news articles and videos, which were
+not suitable for sentiment coding. Therefore, we also scraped the
+comments associated with each post. This resulted in 12,553 comments
+after processing, including information on score, up/down votes, and
+date/time. Comments containing only weblinks, videos, or images were
+removed. A review of the comments revealed more opinionated statements
+and reactions. We then randomly selected 400 comments (without
+replacement) and assigned them to four graduate students for coding,
+categorizing each comment as favoring, opposing, or neutral towards
+DOGE's approach to federal workforce reductions.
 
@@
 We show the number of posts pre/post processing by day in Figure 1
-during the timeframe that we collected these data.. There appears to be
-a noticeable peak in activity during the middle of the week. However, we
-don't have enough data across weeks to conclusively say it's due to the
-day of the week itself. It's more likely that these spikes are linked to
-specific events that occurred on those days, which sparked
+during the timeframe that we collected these data. There appears to be a
+noticeable peak in activity during the middle of the week. However, we
+don't have enough data across weeks to conclusively say it is due to the
+day of the week itself. It is more likely that these spikes are linked
+to specific events that occurred on those days, which sparked
 conversations. The two peaks in our graph could be attributed to two
-major news stories. On March 5, Elon Musk made a statement about wanting
-to ``save Western civilization from empathy,'' and on March 6, there
-were reports that President Trump was limiting Musk's authority due to
-backlash over cuts to DOGE. These events likely had a significant impact
-on the volume of Reddit posts related to Elon Musk and DOGE, driving the
-observed spikes in activity.
+major news stories. On March 5th, Elon Musk made a statement about
+wanting to ``save Western civilization from empathy,'' and on March 6th,
+there were reports that President Trump was limiting Musk's authority
+due to backlash over cuts to DOGE. These events likely had a significant
+impact on the volume of Reddit posts related to Elon Musk and DOGE,
+driving the observed spikes in activity.
 
-On May third, news outlets started reporting that DOGE was claiming
+On March 3rd, news outlets started reporting that DOGE was claiming
 \$105 billion dollars in savings from cutting ``wasteful'' spending by
@@
 
-We see a peak in the comments in Figure 2 during March 6th, which was a
+We see a peak in the comments in Figure 2 on March 6th, which was a
 Thursday, and perhaps in anticipation of DOGE policies that often are
@@
 people posting during their lunch break. There is also significant
-activity in the afternoon, evening, and early morning. This could be
-because people have more free time or stay up late, allowing them to
-take the time to write posts, which require more effort than quick
-interactions. The fewest posts are seen in the morning, which makes
-sense as people are typically getting ready for work, commuting, or
-sleeping in. The trend for comments (see Figure 3) mirrors that of
-posts. This makes sense because people are likely using Reddit at
-similar times for both posting and commenting. However, the volume of
+activity in the afternoon, evening, and early morning. It is possible
+that people have more time in the evenings allowing them to be more
+likely to post on Reddit. The fewest posts are seen in the morning,
+which makes sense as people are typically getting ready for work,
+commuting, or sleeping in. The trend for comments (see Figure 3) mirrors
+that of posts. This makes sense because people are likely using Reddit
+at similar times for both posting and commenting. However, the volume of
 comments is much higher than the number of posts, as each post receives
@@
 The graphs below (Figure 4) show the most frequent words used in both
-Reddit posts and their comment sections. These words were identified by
-tokenizing the text and removing stop words, then counting the
-occurrences of the most common terms. From the visualizations, we can
-see that many of these words are directly related to our topic of
-discussion. Specifically, there are frequent mentions of `President,'
-`DOGE,' `federal government,' and `RIF,' which suggest that discussions
-surrounding political events, cryptocurrency (like Dogecoin), and
-government-related issues are significant in the posts and comments.
-This highlights the focus of the community on these key themes,
-reflecting the ongoing conversations and interests of Reddit users
-within this context.
+Reddit posts and their comment sections while excluding our keyword
+search terms. These words were identified by tokenizing the text and
+removing stop words, then counting the occurrences of the most common
+terms. Examining this visual reveals that in posts the current
+president's name is the top word. However, in both posts and comments,
+there appears to be an emerging theme of community as words like people,
+employees, service, care, jobs, and public are also top words. This
+highlights the focus of the community on these key themes, reflecting
+the ongoing conversations and interests of Reddit users within this
+context.
 
@@
 
-We randomly selected and coded 400 comments from the Reddit posts. The
-table below shows the distribution of favorability coding for these
-comments. Among the 400 comments, the majority (217) expressed
-opposition to DOGE's approach to reducing the federal workforce, while
-110 were supportive, and 73 remained neutral. A large number of comments
-(12,153) were not coded, as their content was not relevant for
-favorability assessment.
+We randomly selected and coded 400 comments from the Reddit posts. Table
+2 shows the distribution of favorability coding for these comments.
+Among the 400 comments, the majority (217) expressed opposition to
+DOGE's approach to reducing the federal workforce, while 110 were
+supportive, and 73 remained neutral. A large number of comments (12,153)
+were not coded, as their content was not relevant for favorability
+assessment.
 
@@
 
-In this study, we explored the impact of the Department of Government
-Efficiency's (DOGE) actions on federal workers' perceptions of job
-security, using Reddit as a platform to analyze public discourse. By
+In this study, we explored the impact of the DOGE's actions towards the
+reduction in force impacting federal workers' perceptions of job
+security, using Reddit as a platform to analyze public discourse. In
 examining Reddit posts and comments related to DOGE's workforce
@@
 wide range of reactions, with the majority being strongly opposed to
-DOGE's approach. The frequent mention of terms like `President,' `DOGE,'
-`federal government,' and `RIF' underscores the community's focus on
-government policies and the emotional responses these issues generate.
+DOGE's approach. The frequent mention of terms related to the
+administration underscores the community's focus on government policies
+and the emotional responses these issues generate.
 
@@
 of social media platforms like Reddit in capturing public sentiment on
-contemporary political and policy issues. However, it's important to
+contemporary political and policy issues. However, it is important to
 note that Reddit may not fully represent the broader population's views,
@@
 
-Furthermore, the use of sentiment analysis on social media presents
-challenges, as it can be influenced by sarcasm, humor, or polarized
-language, which might affect the accuracy of sentiment classification.
-The specific subreddits analyzed, while designed to capture diverse
-perspectives, may still over-represent certain political or ideological
-viewpoints. Additionally, the relatively short timeframe of this
-analysis---spanning only March 2-10, 2025---means that we may not have
-captured long-term trends or shifts in sentiment as the DOGE policies
-unfold. Future research could address these limitations by expanding the
-data collection to other platforms or a longer timeframe and by
-incorporating demographic data to better understand the views of
+The use of sentiment analysis on social media presents challenges, as it
+can be influenced by sarcasm, humor, or polarized language, which might
+affect the accuracy of sentiment classification. Therefore, our research
+team hand coded a subset of comments, yet inter-rater reliability was
+not estimated. The specific subreddits analyzed, while designed to
+capture diverse perspectives, may still over-represent certain political
+or ideological viewpoints. Moreover, the relatively short timeframe of
+this analysis---spanning only March 2nd to March 10th---means that we
+may not have captured long-term trends or shifts in sentiment as the
+DOGE policies unfold. Future research could address these limitations by
+expanding the data collection to other platforms or a longer timeframe
+and by incorporating demographic data to better understand the views of
 different Reddit user groups.
@@
 \section{Appendix}\label{appendix}
+
+We examined almost 100 subreddit posts while paying attention to the
+post topics and determined which ones were related to our topic. We also
+included right leaning subreddits to attempt to capture a balanced
+public sentiment on the topic. The following is our final list of
+subreddits that we scraped from.
 

### 2025-03-22 code/paper.qmd
final paper

@@
 There appears to be a noticeable peak in activity during the middle of the week.
-However, we don't have enough data across weeks to conclusively say it is due to the day of the week itself.
+However, we do not have enough data across weeks to conclusively say it is due to the day of the week itself.
 It is more likely that these spikes are linked to specific events that occurred on those days, which sparked conversations.
@@
 These words were identified by tokenizing the text and removing stop words, then counting the occurrences of the most common terms.
+The removal of stop words allowed us to focus on contextual words in the posts/comments rather than common words like "the" and "and" that are not useful in these types of analysis.
 Examining this visual reveals that in posts the current president's name is the top word.

### 2025-03-22 code/paper.tex
final paper

@@
 
-\date{March 21, 2025}
+\date{March 22, 2025}
 \title{\bf DOGE Days on Reddit: Decoding Public Sentiment in a Federal
@@
 noticeable peak in activity during the middle of the week. However, we
-don't have enough data across weeks to conclusively say it is due to the
-day of the week itself. It is more likely that these spikes are linked
-to specific events that occurred on those days, which sparked
+do not have enough data across weeks to conclusively say it is due to
+the day of the week itself. It is more likely that these spikes are
+linked to specific events that occurred on those days, which sparked
 conversations. The two peaks in our graph could be attributed to two
@@
 removing stop words, then counting the occurrences of the most common
-terms. Examining this visual reveals that in posts the current
-president's name is the top word. However, in both posts and comments,
-there appears to be an emerging theme of community as words like people,
-employees, service, care, jobs, and public are also top words. This
-highlights the focus of the community on these key themes, reflecting
-the ongoing conversations and interests of Reddit users within this
-context.
+terms. The removal of stop words allowed us to focus on contextual words
+in the posts/comments rather than common words like ``the'' and ``and''
+that are not useful in these types of analysis. Examining this visual
+reveals that in posts the current president's name is the top word.
+However, in both posts and comments, there appears to be an emerging
+theme of community as words like people, employees, service, care, jobs,
+and public are also top words. This highlights the focus of the
+community on these key themes, reflecting the ongoing conversations and
+interests of Reddit users within this context.
 

### 2025-03-27 code/ml_llm/R/MLtexttutorial.Rmd
assignment 3 materials

---
title: "Machine Learning for Automated Stance Detection"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE, warning=FALSE, message=FALSE)
```

This notebook gives a simple example of using supervised machine learning to automatically detect stance of topic from tweets. There's a lot of code here -- feel free to copy and paste much of it as you work on the exercises and you do your assignment. This is also only barely scratching the surface, and intended to be as transparent of an introduction as possible in terms of showing how everything is done. Of note, the `caret` package in R can be extremely helpful in doing some of what's done here with much less code involved (see https://www.machinelearningplus.com/machine-learning/caret-package/ for more information). However, there's somewhat of a learning curve associated with it, as well as the inability to see how everything works, so I only use the `caret` package to do a few things, like calculating precision and recall.

```{r}
# If you have not installed these, make sure to install first!

# Tidyverse and text analysis tools
library(tidyverse)
library(tidytext)

# Package for text mining
library(tm)

# Package for Stemming and Lemmatizing 
library(textstem)

# For SVM
library(e1071)

# For nearest neighbors
library(class)

# For ML evaluation
library(caret)
```

# Data

We downloaded the data from SemEval2016 website, and the details of the dataset can be seen in [SemEval2016 Task 6](https://aclanthology.org/S16-1003/).

```{r}
semeval_stance <- read.csv('../../data/SemEval2016-testdata-taskA-all-annotations.csv', stringsAsFactors = FALSE,)
semeval_stance$ID <- as.character(semeval_stance$ID) # Need to make this character for later joins
semeval_stance$Stance <- as.factor(semeval_stance$Stance) #Convert Char to Factor
# Also we need to remove #SemST from the Tweet column
semeval_stance$Tweet <- gsub("#SemST", "", semeval_stance$Tweet)
glimpse(semeval_stance)
```

Here, we have a few key variables. The `ID` variable is simply numbers from 1 to 4036, denoting the unique tweet. The tweet's `Target` and `Tweet` (i.e., the content) are all included. Finally, the `Stance` denotes what opinion the tweets express, Favore, Oppose, or . Our goal is to build a machine learning model that takes this data and is able to predict the topic of the tweet based on the content of the tweet.

We want to do the following steps to turn this text data into features:

-**Tokenize:** Split up the tweets into individual words

-**Stop Words:** Remove words that are too frequent and uninformative, like "a", "an", and "the".

-**Bag of Words:** We want columns representing all words in the entire corpus, and the rows representing tweets, with each cell indicating the counts of words in that tweet. This matrix is also known as a term-document matrix.

We'll look at the distribution of words as we go to inform how we're doing. Let's first tokenize and then look at what words in our corpus. First, let's tokenize and count the number of instances of each word. The key function we're using here is `unnest_tokens`, which we're using the break up the big tweet string for each tweet into individual strings with just one word each.

```{r}
semeval_stance %>% 
  unnest_tokens(word, 'Tweet') %>%  # tokenize
  count(word, sort = TRUE) %>% # count by word
  arrange(desc(n)) %>% # Everything from this point on is just to graph
  head(20) %>%
  ggplot(aes(x = reorder(word, n), y = n)) +
  geom_bar(stat= 'identity') + 
  coord_flip()
```

Looks like there are a lot of stop words being caught! Let's take those out. To do this, we use the `stop_words` from the `tidytext` package and use an `anti_join` to remove all instances of that word.

```{r}
semeval_stance %>% 
  unnest_tokens(word, 'Tweet') %>%  # tokenize
  anti_join(stop_words)%>% # Remove stop words
  count(word, sort = TRUE) %>% # count by word
  arrange(desc(n)) %>% # Everything from this point on is just to graph
  head(20) %>% 
  ggplot(aes(x = reorder(word, n), y = n)) +
  geom_bar(stat= 'identity') + 
  coord_flip()
```

That looks better! Let's also take a look at the distribution of word counts by using a histogram on a log scale.

```{r}
semeval_stance %>% 
  unnest_tokens(word, 'Tweet') %>%  # tokenize
  anti_join(stop_words)%>% # Remove stop words
  count(word, sort = TRUE) %>%
  ggplot(aes(n)) +
  geom_histogram() +
  scale_x_log10()
```

It looks like we have a lot of words that only happen once, or otherwise very infrequently. We'll also remove some of the most infrequent words, as they are likely typos, or are so rare that they are not useful. The threshold is arbitrary and very much depends on the corpus itself. Here we will remove words that occur less than 2 times.

```{r}
semeval_stance %>% 
  unnest_tokens(word, 'Tweet') %>%  # tokenize
  anti_join(stop_words)%>% # Remove stop words
  count(word, sort = TRUE) %>% # count by word
  filter(n >= 2) %>%  # Remove words that occur less than 2 times
  ggplot(aes(n)) +
  geom_histogram() +
  scale_x_log10()
```

Now that we've explored the data a little bit and know what steps we should take to clean it up, we can create our features. From this exercise, we know we need to tokenize, remove stop words, and remove infrequent words. We can also take additional steps at this stage to clean up the data a bit more. For example, we might consider removing all numbers or digits. We can think about stemming (or lemmatization) in order to group similar words together under a single root (e.g., invent, invention, inventor). If we were to stem (this step is optional, and it's actually possible your models run better without stemming), it might look something like this:

```{r}
# NOTE: This uses the corpus package, which we did not bring in at the beginning
semeval_stance %>% 
  unnest_tokens(word, 'Tweet') %>%  # tokenize
  anti_join(stop_words)%>% # Remove stop words
  mutate(word = lemmatize_words(word) %>% unlist()) %>% # add stemming process
  count(word, sort = TRUE) %>% # count by word
  filter(n >= 10) %>%  # Remove words that occur less than 10 times
  arrange(desc(n)) %>% # Everything from this point on is just to graph
  head(20) %>% 
  ggplot(aes(x = reorder(word, n), y = n)) +
  geom_bar(stat= 'identity') + 
  coord_flip()
```

## Creating Features

To create the features for our machine learning model, we will take all of the words in our corpus and count the number of times that they appear in the tweet. We will end up with a sparse term-document frequency matrix, with the columns representing each word, and rows representing the tweet.

In this section, we will use the `tm` package to construct the feature matrix, as it offers a more convenient and intuitively interpretable approach.

Let's go over the steps to create the term-document frequency matrix:

1. lower all character
2. remove numbers, punctuation, and stop words
3. Stemming or lemmatization

Using `tm` package, we first need to create a corpus, which is a collection of text documents. We can then use the `tm_map` function to apply a series of text processing steps to the corpus.

```{r}
tweet_corpus = Corpus(VectorSource(semeval_stance$Tweet))
# text preprocessing
# Lower text
tweet_corpus = tm_map(tweet_corpus, content_transformer(tolower))
# Remove numbers, pubctuation, and stop words
tweet_corpus = tm_map(tweet_corpus, removeNumbers)
tweet_corpus = tm_map(tweet_corpus, removePunctuation)
tweet_corpus = tm_map(tweet_corpus, removeWords, c("the", "and", stopwords("english")))
# Lemmatization
tweet_corpus = tm_map(tweet_corpus, lemmatize_words)
```

After text preprocessing, we can create the term-document frequency matrix simply using the `DocumentTermMatrix` function.

```{r}
tweet_dtm = DocumentTermMatrix(tweet_corpus)
# Take a look at tweet_dtm
tweet_dtm
```
As we mentioned before, most of cases, the matrix will be sparse because most of the words will not appear in most of the tweets. We can use the `inspect` function to take a look at the first few rows and columns of the matrix.

```{r}
inspect(tweet_dtm)
```
One way to address the sparsity of the matrix is to remove infrequent words, as we demenstracted before. We can use the `removeSparseTerms` function to remove words that appear in less than a certain percentage of the tweets.

```{r}
tweet_dtm = removeSparseTerms(tweet_dtm, 0.99)
# Inspect the matrix again
inspect(tweet_dtm)
```
By specifying `0.99`, we are removing words that appear in less than 1% of the tweets. notably, we only have 105 unique terms left.

```{r}
# Convert the matrix to a data frame
tweet_dtm_df = as.data.frame(as.matrix(tweet_dtm))

# Add the ID, Stance variable to the data frame
tweet_dtm_df$ID = semeval_stance$ID
tweet_dtm_df$Stance = semeval_stance$Stance

```

The full data contains the ID variable (which we will use to make our train/test split in the next section), as well as our features (each word) and the label (True/False for whether the topic was on cell biology or not)

Here, you might consider doing a bit more feature engineering and data manipulation. For example, you might consider scaling the variables, in order to avoid the influence of more frequent words. You can try cleaning the text data a bit more, to remove certain words that might be stop words in this specific context. You can also consider adding additional variables, such as length of tweet in number of words.

## Train and Test Split

For simplicity, we'll consider a simple holdout sample. At the end, we show how to do cross validation using the `caret` package in R. The cross validation code will be very similar to this, except repeated for multiple combinations of training and testing data.

```{r, message=FALSE}
# 30% holdout sample
test <- tweet_dtm_df %>% sample_frac(.3)

# Rest in the training set
train <- tweet_dtm_df %>% anti_join(test, by = 'ID') %>% select(-ID)

# Remove ID after using to create train/test
# We don't want to use ID to run models!
test <- test %>% select(-ID)
```

# Fitting Models

Now, we can fit some machine learning models. We'll do some simple ones here: K-Nearest Neighbors and Support Vector Machine (SVM). You can also use Logistic Regression, or Naive Bayes, or Decision Trees, or any number of other, more complicated models, though we won't cover them here. If you are familiar with ensemble models, such as Random Forests, I'd suggest trying those out as well.

## First attempt at a model

Let's start with a K-Nearest Neighbors model. This simply checks the class of closest k neighbors, and takes a vote of them to predict what the class of the data point will be. We can fit this model using the `class` package.

```{r}
# Create separate training and testing features and labels objects
train_features <- train %>% select(-Stance)
test_features <- test %>% select(-Stance)

train_label <- train$Stance
test_label <- test$Stance

# Predicted values from K-NN, with K = 3
knnpred <- knn(train_features,test_features,train_label, k = 3)
```

The `knnpred` object has the predicted values for each of the `test_features` that we gave it. Let's take a look at what the predicted values are. We'll put the predicted values in a data frame with the actual values.

```{r}
pred_actual <- data.frame(predicted = knnpred, actual = test_label)
pred_actual %>% head()
```

Now that we have the predicted and actual values in one data frame, we can create a confusion matrix and evaluate how well our model is performing.

```{r}
pred_actual %>% table()
confusionMatrix(pred_actual %>% table())
```

Note that we don't actually see the words "precision" or "recall" here -- instead, we can find them by their alternate names: sensitivity (for recall) and positive predictive value (for precision). We can also use the `precision` and `recall` functions (also in the `caret` package). Note that we use `relevant` to specify which outcome we're trying to predict (similar to the `positive` argument above).

## Running a Support Vector Machine

With the training and testing datasets that we've created, running the actual tree model is actually quite simple. If you have used `R` for running linear models before, the format is very similar.

```{r}
svmfit <- svm(Stance ~ ., 
              data = train, 
              kernel = 'linear', 
              cost = 10)
```

Let's break down each of the arguments in this function. First, we specify the model, putting the label that we want to predict on the left side of the "~" and all the features we want to include on the right. We include arguments for the dataframe from which we're taking the data, and the kernel method we want to use. Then, we can use the `cost` argument to specify the regularization term.

We have stored the model in the `svmfit` object. Let's look at what the model gave us. We can use summary to look at the summary of the model.
```{r}
# You can try running the summary, but it will give a LOT of output
summary(svmfit)
```

### Evaluating the Model
Now that we have a model, we need to test it. We can get predictions using the `predict` function.

```{r}
pred <- predict(svmfit, test)
head(pred)
```

We can get the values of precision and recall using `confusionMatrix` function from the `caret` package. First, we create a table with the confusion matrix, then run the function with the table as the argument.

```{r}
# Construct the confusion matrix
pred_actual <- data.frame(predicted = pred, actual = test_label)
pred_actual %>% head()
confusionMatrix(pred_actual %>% table())
```

### Looping through models

We've shown an example of two different types of models: K-Nearest Neighbors and SVM. In the real world, we would want to try many different models with many different values for the tuning parameters (e.g., K for K-NN, cost or gamma for trees). Using a loop, we can automatically run through many different models very quickly. Below is an example of trying many different SVM models.

```{r}
# We will look at gamma values of 0.1, 1, 10, 100
gammas <- c(0.1, 1, 10, 100)

# We'll look at cost values of 0.1, 1, 10, 100, 1000
costs <- c(0.1, 1, 10, 100)

# We'll consider different kernel types
kernels <- c('linear', 'radial', 'polynomial')

# How many different models are we running?
nmods <- length(gammas)*length(costs)*length(kernels)

# We will store results in this data frame
results <- data.frame(gammas = rep(NA,nmods), 
                      costs = rep(NA, nmods),
                      kernel = rep(NA,nmods),
                      precision = rep(NA,nmods),
                      recall = rep(NA,nmods))

# The model number that we will iterate on (aka models run so far)
mod_num <- 1

# The loop
for(i in 1:length(gammas)){
  for(j in 1:length(costs)){
    for(k in 1:length(kernels)){
        g <- gammas[i]
        c <- costs[j]
        kn <- kernels[k]
        # Running the model

        svmfit <- svm(Stance ~ ., 
                      data = train, 
                      gamma = g,
                      cost = c,
                      kernel = kn)

        # Find the predictions
        pred <- predict(svmfit, test)

        # Attach scores to the test set
        # Then sort by descending order
        pred_actual <- data.frame(predicted = pred, actual = test_label)
        pred_table <- pred_actual %>% table()

        # Store results and we set AGAINST as referent category and turn the          results into a binary classification. 
        results[mod_num,] <- c(g, 
                               c,
                               kn,
                               precision(pred_table, relevant = 'AGAINST'), 
                               recall(pred_table, relevant = 'AGAINST'))
        # Increment the model number
        mod_num <- mod_num + 1
    }
  }
}

# All results are stored in the "results" dataframe
head(results)

# Best recall? Top 5 in descending order
results %>% arrange(desc(recall)) %>% head()

# Best precision? Top 5 in descending order
results %>% arrange(desc(precision)) %>% head()
```

You can also loop through many different values of K for K-NN, and also different tuning parameters for other types of models. For example, for Logistic Regression, you might consider an L1 or L2 penalty (Lasso or Ridge Regression), with different values for the penalty parameter.

## Simplifying the Process with Caret

We've already used the `caret` package for tools like the confusion matrix and precision/recall. However, we can also use it to do other validation methods more easily, such as k-fold cross validation. Here, we'll look at a quick example of using `caret` to find the training and test sets need to do 10-fold cross validation.

```{r}
# Create a list of 10 folds (each element has indices of the fold)
flds <- createFolds(tweet_dtm_df$ID, k = 10, list = TRUE, returnTrain = FALSE)
str(flds)
```

As you can see, we created a list of 10 vectors, each containing a fold. So, to do our 10-fold cross validation, we can take the first fold, and create our train and test sets from that, take the second fold and create test and train from that, and so on. For example, to create test and train using the first fold, we can use the following code:

```{r}
# Create train and test using fold 1 as test
stance_test01 <- tweet_dtm_df[flds$Fold01,]
stance_train01 <- tweet_dtm_df[-flds$Fold01,]
```

You can then use these train and test sets as we have above. You should put this into a loop, and store the value of metrics such as accuracy, precision, and recall, similar to what we've done in the loop of trying out different parameters.

### 2025-03-27 code/reddit_project/Reddit_eda.qmd
assignment 3 materials

--- 2025-03-14 code/Reddit_eda.qmd
@@
   labs(
-    title = "Total Number of Posts per Day Pre and Post Processing",
+    title = "Total Number of Posts per Day Pre/Post Processing",
     x = "Day",
@@
   labs(
-    title = "Total Number of comments per Day during collection",
+    title = "Total Number of collected comments per Day",
     x = "Day",

### 2025-03-27 code/ml_llm/Python/LLMStanceTutorial.py
added token argument to python script

@@ -20,7 +20,8 @@ stance["Tweet"] = stance["Tweet"].str.replace("#SemST", "")
 model_name = "google/gemma-3-12b-it"  # 8x7B MoE model\
 tokenizer = AutoTokenizer.from_pretrained(model_name)  # Load tokenizer
 model = AutoModelForCausalLM.from_pretrained(
-    model_name, device_map=device
+    model_name, device_map=device,
+    # pass huggingface token using token = "<token key>", do not save token in code!
 )  # Load model
 
 # Loop through the tweets and generate the stance

### 2025-04-07 code/ml_llm/R/assign_3.qmd
adding assign 3 paper

---
title: "DOGE Days on Reddit: Decoding Public Sentiment in a Federal Shakeup"
format:
  jasa-pdf:
    keep-tex: true  
    journal:
      blinded: false
  jasa-html: default
date: last-modified
author:
  - name: Kevin Linares
    affiliations:
      - name: University of Maryland
  - name: Felix Baez-Santiago
  - name: Aria Lu
  - name: Gloria Zhou
    affiliations:
      - name: University of Michigan
abstract: |
   This study investigates public sentiment on Reddit towards the Department of Government Efficiency's (DOGE) federal workforce reduction. Analyzing 400 labeled Reddit comments, we employed supervised learning (KNN, Random Forest) and unsupervised Large Language Models (LLMs: Llama 3.2 3B, deepseek-r1:8b) to classify comment stance (favor, neutral, oppose). While LLMs showed higher precision for opposing comments, all models struggled with neutral and favoring stances. Agreement between the two LLMs was fair (Cohen's Kappa = 0.344), indicating divergent interpretations. Results suggest that accurately decoding nuanced public sentiment in this context remains challenging for both traditional and large language models.

keywords:
  - Reddit
  - Federal Government
  - DOGE
editor: 
  markdown: 
    wrap: sentence
---

```{r include=FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, error = FALSE, comment = FALSE)

library(readxl)
library(viridis)
library(ggthemes)
library(tidytext)
library(knitr)
library(ConfusionTableR)
library(caret)
library(tidyverse)

# read in ML results from repo
results_folder <- "~/repos/SURV622_Assignment/outputs/ml_llm/"

ml_results <-  read.csv(str_c(
  results_folder, "results_long.csv")) |> 
  filter( data == "counts",
    set == "test",# keep only test results
    metric %in% c("precision", "recall", "f1-score"),
    class %in% c("favor", "neutral", "oppose"),
    !str_detect(model, "Bernoulli")
         ) |> 
  # remove duplicates
  distinct() |> 
  mutate(model = str_remove(model,  "^[^|]+\\.")) |> 
  tibble()

llm_results <- read_xlsx(str_c(
  results_folder, "reddit_comments_LLM_analysis.xlsx")) |> 
  mutate_at(vars(outcome, llama, deepseek), factor)
```

## Introduction {#sec-intro}

Established in January 2025, the Department of Government Efficiency (DOGE) has significantly reduced the federal workforce by over 280,000 employees, fulfilling a key campaign promise of the new administration.
This has caused widespread concern and anxiety among federal workers about job security and mental well-being.
Questions have also been raised regarding DOGE's adherence to internal policies.
To understand the impact of DOGE's actions on federal worker perceptions of job security, we collected 400 reddit comments on topics related to DOGE's tactics in reducing the federal workforce.
Additionally, a team of researchers labeled each comment as whether the author favored, opposed, or had a neutral stance concerning how DOGE was implementing these strategies.
In the current study we employ two supervise learning model to predict, given a set of features, comments on stance.
We also employ an unsupervised large language model (LLM) to detect the stance of these reddit comments and report model findings.

## Methods {#sec-meth}

*Data*.
We collected Reddit comments from subreddits related to the topic of interest in early March of 2024.
This resulted in 12,553 comments which we preprocessed by removing weblinks, replace special characters (i.e., replaced "\@" with "at"), replaced numeric values with their spelling, and confirmed the absence of duplicate comments.
We then randomly selected 400 comments (without replacement) and assigned them to four graduate students for coding, categorizing each comment as favoring, opposing, or neutral towards DOGE's approach to federal workforce reductions.
Table 1 presents the breakdown in percent of our the comments we labelled and later use to train and evaluate our machine learning models.
A review of the comments revealed more negative opinionated statements and reactions.

```{r}
llm_results |> 
  count(outcome) |> 
  mutate(Percent = n/sum(n),
         Percent = round(Percent* 100)) |> 
  select(outcome, Percent) |> 
  kable(caption="Distribution of labeled Reddit comment data.")
```

We built two supervised machine learning models, K-nearest neighbor and random forest, to classify Reddit comments concerning stance on the current reduction in federal workforce into favor, oppose, or neutral.
For model predictors we used the Reddit score, up-votes, and down-votes each comment received at the time of the collection.
Additionally, we used the keyword that was used to scrape these data along with the subreddit where the comment was posted.
DISCUSS ADDITIONAL FEATURE ENGINERRING SUCH AS TEXT EDITING THAT WENT INTO THE MODEL. For the KNN model, we set the number of neighbors hyperparameter to thhree, and for the random forest, mtry was kept at a constant two as we did not have many features in these models.
We took an 80/20 split for our training-testing sets that we used to train each model and evaluate.

In addition to our supervised machine learning models, we also applied to our data two LLMs, llama 3.2.
3B and deepseek-r1:8b.
The llama model, developed by Meta AI released in February 2023, was designed for applications requiring low-latency inferencing with limited computational resources, which means that we were able to also deploy these models on a local machine with a GPU in addition to using the [Great Lakes HCP](https://its.umich.edu/advanced-research-computing/). This model also excels at text classification which is how we used it to classify the stance for each comment.
Deepseek, developed by Liang Wenfeng in July 2023 and based on the llama architecture, yet boosts efficiency improvements that appear to provide advances in reasoning, logic, while excelling at natural language processing.
We choose both of these LLMs as candidates to test against our supervised approaches because of their ability to apply locally and reputable performance on zero-shot classification tasks.
Both of these models received the same prompt and tasked which were developed by the research team to reflect the utility of classifying stance within our topic of interest.
Both LLMs resulted in not being able to classify five comments each while they only had one in common with the likely reason being that these comments did not contain enough useful text for a stance to be derive.

Prompt: "Is this comment in 'favor', 'neutral', or 'oppose' the reduction in federal workforce? Provide one word answer only!

Task: "You have assumed the role of a stakeholder that is presented with a reddit comment from a likely federal worker related to the current policies on reducing the federal workforce. Please determine the author's stance on this topic, and only provide the answer."

To evaluate model performance we used recall to determine how many of actual positive cases did the model correctly identify.
High recall indicates that the model can correctly identify positive instances but is also optimistic and may incorrectly label cases as positive.
The second performance metric we selected is precision, of all the items the model labels as positive how many are true positive, and high precision indicates that when the model predicts a case to be positive it is likely to be correct.

## Results

Our machine learning models reveal a mix of performance results in classifying comments into one of three stance categories.
Overall, the random forest model reduces the test misclassification error against KNN, yet not by much.
The stance oppose tended to have the highest recall of the three with the random forest model having higher scores: Of all the oppose cases, the random forest model found 74 percent and the KNN 64 percent.
For the neutral stance, the random forest captured 5 percent and KNN 21 percent.
While for the favor stance, the random forest identified 26 percent and KNN 16 percent (see Figure 1 for these results).
Neither model excelled in how many of the stance categories identified were right as indicated by the precision scores.
KNN slightly outperformed random forest on the oppose stance having correctly classified 56 percent vs random forest 51 percent or true oppose cases.
For neutral the performance is worse with random forest correctly identified 50 percent and KNN 21 percent, and same for favor with random forest correctly identifying 29 percent and KNN 23 percent.

```{r}
#| fig-width: 7
#| fig-height: 6
#| 
# number of total posts
ml_results |> 
  # filter models needed
  filter(model %in% 
           c("RandomForestClassifier", "KNeighborsClassifier"),
         metric %in% c("precision", "recall")) |> 
  ggplot(aes(x=model, y=value, fill=class)) +
  geom_col(position="dodge") +  
  coord_flip() +
  facet_grid(~metric) +
  guides(fill=guide_legend(title="", reverse = TRUE)) +
  scale_fill_viridis_d(option="F", direction = -1,
                       alpha=.85, end =.70, begin=.15) +
  labs(
    title = "Figure 1. Recall and precision scores for random forest
    and KNN models.",
    x = "Models",
    y = "Performance Scores"
  ) +
  theme_hc()

```

We observe higher precision scores for the oppose stance when using the LLMs to classify stance positions.
Of all the identified oppose stance cases these models identified, the percent of true oppose cases was 84 percent for llama and 69 percent for deepseek.
Similarly, of all the classified neutral stance classified by these models, the percent of true neutral cases was 21 percent for llama and 42 percent for deep seek.
Finalkly, of all the identified favor stance, the percent of true favor cases was 4 percent for llama and 10 percent for deepseek (see Figure 2 for these results).
Recall scores were worse for the oppose stance, and of all the oppose cases the llama model captured 56 percent and deepseek 60 percent.
For the neutral stance, llama captured 25 percent and deekseek 27 percent.
Finally, for the favor stance, llama captured 29 percent and deekseek 32 percent.

\

```{r}

 cm_metric_fun <- function(dat, model_name){

   subset_dat <- dat |> 
     # truth should go first, predicted 2nd
     select(outcome, all_of(model_name)) |> 
     rename(predictor = 2)

  cm_ob = multi_class_cm(subset_dat$outcome, 
                        subset_dat$predictor,
                        mode="everything")

  result = cm_ob$record_level_cm |> 
   tibble() |> 
   select(contains(c("precision", "recall", "f1"))) |> 
   pivot_longer(everything()) |> 
   separate(name, c("class", "metric")) |> 
   mutate(model = model_name) |> 
   rename(score=value)

  return(result)
 }

 llama_metrics <- cm_metric_fun(
   dat = llm_results, 
   model_name = "llama") # name of predicted column

 deepseek_metrics <- cm_metric_fun(
   dat = llm_results, 
   model_name = "deepseek" # name of predicted column
 )

 metric_results <- llama_metrics |> 
   add_row(deepseek_metrics)

```

```{r}
#| fig-width: 7
#| fig-height: 6
#| 
metric_results |> 
  filter(metric %in% c("Precision", "Recall")) |> 
  ggplot(aes(x=model, y=score, fill=class)) +
  geom_col(position="dodge") +  
  coord_flip() +
  facet_grid(~metric) +
  guides(fill=guide_legend(title="", reverse = TRUE)) +
  scale_fill_viridis_d(option="F", direction = -1,
                       alpha=.85, end =.70, begin=.15) +
  labs(
    title = "Figure 2. Recall and precision scores for LLMs.",
    x = "Models",
    y = "Performance Scores"
  ) +
  theme_hc()
```

Llama and DeepSeek demonstrated only fair agreement in stance classification (Cohen's Kappa = 0.344).
The contingency table, Table 2 below, reveals highest agreement for "oppose" (0.58), indicating some consistency in identifying strong negative sentiment.
However, agreement was substantially lower for "neutral" (0.11) and "favor" (0.02), highlighting divergent interpretations of more nuanced language.
Off-diagonal values further illustrate these discrepancies, suggesting fundamental differences in how the models process ambiguous cues and establish classification boundaries, particularly for less extreme stances.

```{r}
cm_results <- confusionMatrix(llm_results$llama, llm_results$deepseek)

coh_kappa <-  cm_results[[3]][[2]]

cm_results$table |> 
    kable(caption=str_c("Aggreement between LLMs, Cohens Kappa, ", 
                        round(coh_kappa, 2)))

```

## Conclusion

We explored public sentimenton Reddit regarding the DOGE federal workforce reduction using supervised learning (KNN, Random Forest) and unsupervised LLMs (Llama 3.2 3B, deepseek-r1:8b) for stance classification.
LLMs showed higher precision for "oppose" comments, suggesting better identification of negative sentiment, but lower recall, indicating missed opposing comments.
Supervised models performed consistently but generally poorly across all stances, and likely due to the limited feature set (Reddit metadata) as well as the small sample of comments.

The consistent difficulty in classifying "neutral" and "favor" stances across all models likely stems from class imbalance (more "oppose" comments), the inherent ambiguity of neutral language, and potentially more nuanced expressions of favor.
The zero-shot approach for LLMs might also limit their performance on this specific domain.
The few unclassifiable comments highlight the inherent challenges in stance detection within informal online text.

We conclude that while LLMs showed promise for identifying strong negative sentiment, accurately classifying the full spectrum of public opinion on Reddit regarding DOGE's actions remains challenging.
Future research should focus on incorporating richer text-based features for supervised models, addressing class imbalance, and potentially fine-tuning LLMs to better capture the nuances of online sentiment and stance.

### 2025-04-07 code/ml_llm/Python/LLMStanceTutorial.py
Added changes to LLMStanceTutorial.py script

@@ -9,45 +9,73 @@ Last updated on 2025-03-22
 import pandas as pd
 from tqdm import tqdm  # For progress bar
 from transformers import AutoModelForCausalLM, AutoTokenizer
+from huggingface_hub import login
 
-device = "cuda"
+# Read the token from the file
+with open("/Users/felbasa/Desktop/token.txt", "r") as token_file:
+    token = token_file.read().strip()
+
+# Log in to Hugging Face using the token
+login(token=token)
+
+device = "cuda"  # or "cpu" if you don't have GPU
 # Load the data
-stance = pd.read_csv("../data/SemEval2016-testdata-taskA-all-annotations.csv")
+stance = pd.read_excel("data/comments_to_code/merged_codes.xlsx")
 # Remove #SemST from the tweet
-stance["Tweet"] = stance["Tweet"].str.replace("#SemST", "")
+stance["comment"] = stance["comment"].str.replace("#SemST", "", regex=False)
 
 # Load the model
-model_name = "google/gemma-3-12b-it"  # 8x7B MoE model\
+model_name = "google/gemma-3-12b-it"  # 8x7B MoE model
 tokenizer = AutoTokenizer.from_pretrained(model_name)  # Load tokenizer
 model = AutoModelForCausalLM.from_pretrained(
-    model_name, device_map=device,
-    # pass huggingface token using token = "<token key>", do not save token in code!
-)  # Load model
+    model_name, device_map="auto"  # Let the model decide where to load itself
+)
 
-# Loop through the tweets and generate the stance
-for i, tweet in enumerate(tqdm(stance["Tweet"])):
-    # TODO: Define the prompt
+# Define prompt elements from your R script
+instructions = (
+    "Instruction: You have assumed the role of a stakeholder that is presented "
+    "with a reddit comment from likely federal workers related to the current policies "
+    "on reducing the federal workforce. Please determine the author of the comment's stance "
+    "on this topic, and only provide the answer."
+)
+
+prompt_template = (
+    "Is this comment in 'favor', 'neutral', or 'oppose' the reduction in federal workforce? "
+    "Provide one word answer only!\n\nComment: {comment}"
+)
+
+# Run inference
+tqdm.pandas()
+stance["LLM_stance"] = ""
+
+for i, row in stance.iterrows():
+    comment = row["comment"]
+    
+    # Prepare the prompt
     prompt = [
         {
             "role": "system",
-            "content": [{"type": "text", "text": "You are a helpful assistant."}],
[…]

### 2025-04-07 code/ml_llm/R/assign_3.tex

--- 2025-04-07 code/ml_llm/R/assign_3.qmd
@@
----
-title: "DOGE Days on Reddit: Decoding Public Sentiment in a Federal Shakeup"
-format:
-  jasa-pdf:
-    keep-tex: true  
-    journal:
-      blinded: false
-  jasa-html: default
-date: last-modified
-author:
-  - name: Kevin Linares
-    affiliations:
-      - name: University of Maryland
-  - name: Felix Baez-Santiago
-  - name: Aria Lu
-  - name: Gloria Zhou
-    affiliations:
-      - name: University of Michigan
-abstract: |
-   This study investigates public sentiment on Reddit towards the Department of Government Efficiency's (DOGE) federal workforce reduction.
-Analyzing 400 labeled Reddit comments, we employed supervised learning (KNN, Random Forest) and unsupervised Large Language Models (LLMs: Llama 3.2 3B, deepseek-r1:8b) to classify comment stance (favor, neutral, oppose).
-While LLMs showed higher precision for opposing comments, all models struggled with neutral and favoring stances.
-Agreement between the two LLMs was fair (Cohen's Kappa = 0.344), indicating divergent interpretations.
-Results suggest that accurately decoding nuanced public sentiment in this context remains challenging for both traditional and large language models.
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
+%
+\documentclass[
+  12pt]{article}
 
-keywords:
-  - Reddit
-  - Federal Government
-  - DOGE
-editor: 
-  markdown: 
-    wrap: sentence
----
+\usepackage{amsmath,amssymb}
+\usepackage{iftex}
+\ifPDFTeX
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else  
+    % xetex/luatex font selection
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\setcounter{secnumdepth}{5}
+% Make \paragraph and \subparagraph free-standing
+\makeatletter
+\ifx\paragraph\undefined\else
+  \let\oldparagraph\paragraph
+  \renewcommand{\paragraph}{
+    \@ifstar
+      \xxxParagraphStar
+      \xxxParagraphNoStar
+  }
+  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
+  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+  \let\oldsubparagraph\subparagraph
+  \renewcommand{\subparagraph}{
+    \@ifstar
+      \xxxSubParagraphStar
+      \xxxSubParagraphNoStar
+  }
+  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
+  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
+\makeatother
 
-```{r include=FALSE}
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
 
-knitr::opts_chunk$set(echo = FALSE, message = FALSE, error = FALSE, comment = FALSE)
+\addtolength{\oddsidemargin}{-.5in}%
+\addtolength{\evensidemargin}{-1in}%
+\addtolength{\textwidth}{1in}%
+\addtolength{\textheight}{1.7in}%
+\addtolength{\topmargin}{-1in}%
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\AtBeginDocument{%
+\ifdefined\contentsname
+  \renewcommand*\contentsname{Table of contents}
+\else
+  \newcommand\contentsname{Table of contents}
+\fi
+\ifdefined\listfigurename
+  \renewcommand*\listfigurename{List of Figures}
+\else
+  \newcommand\listfigurename{List of Figures}
+\fi
+\ifdefined\listtablename
+  \renewcommand*\listtablename{List of Tables}
+\else
+  \newcommand\listtablename{List of Tables}
+\fi
+\ifdefined\figurename
+  \renewcommand*\figurename{Figure}
+\else
+  \newcommand\figurename{Figure}
+\fi
+\ifdefined\tablename
+  \renewcommand*\tablename{Table}
+\else
+  \newcommand\tablename{Table}
+\fi
+}
+\@ifpackageloaded{float}{}{\usepackage{float}}
+\floatstyle{ruled}
+\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
+\floatname{codelisting}{Listing}
+\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
+\makeatother
+\makeatletter
+\makeatother
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
+\makeatother
 
-library(readxl)
-library(viridis)
-library(ggthemes)
-library(tidytext)
-library(knitr)
-library(ConfusionTableR)
-library(caret)
-library(tidyverse)
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\usepackage[]{natbib}
+\bibliographystyle{agsm}
+\usepackage{bookmark}
 
-# read in ML results from repo
-results_folder <- "~/repos/SURV622_Assignment/outputs/ml_llm/"
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={DOGE Days on Reddit: Decoding Public Sentiment in a Federal Shakeup},
+  pdfauthor={Kevin Linares; Felix Baez-Santiago; Aria Lu; Gloria Zhou},
+  pdfkeywords={Reddit, Federal Government, DOGE},
+  colorlinks=true,
+  linkcolor={blue},
+  filecolor={Maroon},
+  citecolor={Blue},
+  urlcolor={Blue},
+  pdfcreator={LaTeX via pandoc}}
 
-ml_results <-  read.csv(str_c(
-  results_folder, "results_long.csv")) |> 
-  filter( data == "counts",
-    set == "test",# keep only test results
-    metric %in% c("precision", "recall", "f1-score"),
-    class %in% c("favor", "neutral", "oppose"),
-    !str_detect(model, "Bernoulli")
-         ) |> 
-  # remove duplicates
-  distinct() |> 
-  mutate(model = str_remove(model,  "^[^|]+\\.")) |> 
-  tibble()
+\begin{document}
 
-llm_results <- read_xlsx(str_c(
-  results_folder, "reddit_comments_LLM_analysis.xlsx")) |> 
-  mutate_at(vars(outcome, llama, deepseek), factor)
-```
+\def\spacingset#1{\renewcommand{\baselinestretch}%
+{#1}\small\normalsize} \spacingset{1}
 
-## Introduction {#sec-intro}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-Established in January 2025, the Department of Government Efficiency (DOGE) has significantly reduced the federal workforce by over 280,000 employees, fulfilling a key campaign promise of the new administration.
-This has caused widespread concern and anxiety among federal workers about job security and mental well-being.
-Questions have also been raised regarding DOGE's adherence to internal policies.
-To understand the impact of DOGE's actions on federal worker perceptions of job security, we collected 400 reddit comments on topics related to DOGE's tactics in reducing the federal workforce.
-Additionally, a team of researchers labeled each comment as whether the author favored, opposed, or had a neutral stance concerning how DOGE was implementing these strategies.
-In the current study we employ two supervise learning model to predict, given a set of features, comments on stance.
-We also employ an unsupervised large language model (LLM) to detect the stance of these reddit comments and report model findings.
+\date{April 7, 2025}
+\title{\bf DOGE Days on Reddit: Decoding Public Sentiment in a Federal
+Shakeup}
+\author{
+Kevin Linares\\
+University of Maryland\\
+and\\Felix Baez-Santiago\\
+and\\Aria Lu\\
+and\\Gloria Zhou\\
+University of Michigan\\
+}
+\maketitle
 
-## Methods {#sec-meth}
+\bigskip
+\bigskip
+\begin{abstract}
+This study investigates public sentiment on Reddit towards the
+Department of Government Efficiency's (DOGE) federal workforce
+reduction. Analyzing 400 labeled Reddit comments, we employed supervised
+learning (KNN, Random Forest) and unsupervised Large Language Models
+(LLMs: Llama 3.2 3B, deepseek-r1:8b) to classify comment stance (favor,
+neutral, oppose). While LLMs showed higher precision for opposing
+comments, all models struggled with neutral and favoring stances.
+Agreement between the two LLMs was fair (Cohen's Kappa = 0.344),
+indicating divergent interpretations. Results suggest that accurately
+decoding nuanced public sentiment in this context remains challenging
+for both traditional and large language models.
+\end{abstract}
 
-*Data*.
-We collected Reddit comments from subreddits related to the topic of interest in early March of 2024.
-This resulted in 12,553 comments which we preprocessed by removing weblinks, replace special characters (i.e., replaced "\@" with "at"), replaced numeric values with their spelling, and confirmed the absence of duplicate comments.
-We then randomly selected 400 comments (without replacement) and assigned them to four graduate students for coding, categorizing each comment as favoring, opposing, or neutral towards DOGE's approach to federal workforce reductions.
-Table 1 presents the breakdown in percent of our the comments we labelled and later use to train and evaluate our machine learning models.
-A review of the comments revealed more negative opinionated statements and reactions.
+\noindent%
+{\it Keywords:} Reddit, Federal Government, DOGE
+\vfill
 
-```{r}
-llm_results |> 
-  count(outcome) |> 
-  mutate(Percent = n/sum(n),
-         Percent = round(Percent* 100)) |> 
-  select(outcome, Percent) |> 
-  kable(caption="Distribution of labeled Reddit comment data.")
-```
+\newpage
+\spacingset{1.9} % DON'T change the spacing!
 
-We built two supervised machine learning models, K-nearest neighbor and random forest, to classify Reddit comments concerning stance on the current reduction in federal workforce into favor, oppose, or neutral.
-For model predictors we used the Reddit score, up-votes, and down-votes each comment received at the time of the collection.
-Additionally, we used the keyword that was used to scrape these data along with the subreddit where the comment was posted.
-DISCUSS ADDITIONAL FEATURE ENGINERRING SUCH AS TEXT EDITING THAT WENT INTO THE MODEL.
-For the KNN model, we set the number of neighbors hyperparameter to thhree, and for the random forest, mtry was kept at a constant two as we did not have many features in these models.
-We took an 80/20 split for our training-testing sets that we used to train each model and evaluate.
+\section{Introduction}\label{sec-intro}
 
-In addition to our supervised machine learning models, we also applied to our data two LLMs, llama 3.2.
-3B and deepseek-r1:8b.
-The llama model, developed by Meta AI released in February 2023, was designed for applications requiring low-latency inferencing with limited computational resources, which means that we were able to also deploy these models on a local machine with a GPU in addition to using the [Great Lakes HCP](https://its.umich.edu/advanced-research-computing/).
-This model also excels at text classification which is how we used it to classify the stance for each comment.
-Deepseek, developed by Liang Wenfeng in July 2023 and based on the llama architecture, yet boosts efficiency improvements that appear to provide advances in reasoning, logic, while excelling at natural language processing.
-We choose both of these LLMs as candidates to test against our supervised approaches because of their ability to apply locally and reputable performance on zero-shot classification tasks.
-Both of these models received the same prompt and tasked which were developed by the research team to reflect the utility of classifying stance within our topic of interest.
-Both LLMs resulted in not being able to classify five comments each while they only had one in common with the likely reason being that these comments did not contain enough useful text for a stance to be derive.
+Established in January 2025, the Department of Government Efficiency
+(DOGE) has significantly reduced the federal workforce by over 280,000
+employees, fulfilling a key campaign promise of the new administration.
+This has caused widespread concern and anxiety among federal workers
+about job security and mental well-being. Questions have also been
+raised regarding DOGE's adherence to internal policies. To understand
+the impact of DOGE's actions on federal worker perceptions of job
+security, we collected 400 reddit comments on topics related to DOGE's
+tactics in reducing the federal workforce. Additionally, a team of
+researchers labeled each comment as whether the author favored, opposed,
+or had a neutral stance concerning how DOGE was implementing these
+strategies. In the current study we employ two supervise learning model
+to predict, given a set of features, comments on stance. We also employ
+an unsupervised large language model (LLM) to detect the stance of these
+reddit comments and report model findings.
 
-Prompt: "Is this comment in 'favor', 'neutral', or 'oppose' the reduction in federal workforce? Provide one word answer only!
+\section{Methods}\label{sec-meth}
 
-Task: "You have assumed the role of a stakeholder that is presented with a reddit comment from a likely federal worker related to the current policies on reducing the federal workforce.
-Please determine the author's stance on this topic, and only provide the answer."
+\emph{Data}. We collected Reddit comments from subreddits related to the
+topic of interest in early March of 2024. This resulted in 12,553
+comments which we preprocessed by removing weblinks, replace special
+characters (i.e., replaced ``@'' with ``at''), replaced numeric values
+with their spelling, and confirmed the absence of duplicate comments. We
+then randomly selected 400 comments (without replacement) and assigned
+them to four graduate students for coding, categorizing each comment as
+favoring, opposing, or neutral towards DOGE's approach to federal
+workforce reductions. Table 1 presents the breakdown in percent of our
+the comments we labelled and later use to train and evaluate our machine
+learning models. A review of the comments revealed more negative
+opinionated statements and reactions.
 
-To evaluate model performance we used recall to determine how many of actual positive cases did the model correctly identify.
-High recall indicates that the model can correctly identify positive instances but is also optimistic and may incorrectly label cases as positive.
-The second performance metric we selected is precision, of all the items the model labels as positive how many are true positive, and high precision indicates that when the model predicts a case to be positive it is likely to be correct.
+\begin{longtable}[]{@{}lr@{}}
+\caption{Distribution of labeled Reddit comment data.}\tabularnewline
+\toprule\noalign{}
+outcome & Percent \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+outcome & Percent \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+favor & 28 \\
+neutral & 18 \\
+oppose & 54 \\
+\end{longtable}
 
-## Results
+We built two supervised machine learning models, K-nearest neighbor and
+random forest, to classify Reddit comments concerning stance on the
+current reduction in federal workforce into favor, oppose, or neutral.
+For model predictors we used the Reddit score, up-votes, and down-votes
+each comment received at the time of the collection. Additionally, we
+used the keyword that was used to scrape these data along with the
+subreddit where the comment was posted. DISCUSS ADDITIONAL FEATURE
+ENGINERRING SUCH AS TEXT EDITING THAT WENT INTO THE MODEL. For the KNN
+model, we set the number of neighbors hyperparameter to thhree, and for
+the random forest, mtry was kept at a constant two as we did not have
+many features in these models. We took an 80/20 split for our
+training-testing sets that we used to train each model and evaluate.
 
-Our machine learning models reveal a mix of performance results in classifying comments into one of three stance categories.
-Overall, the random forest model reduces the test misclassification error against KNN, yet not by much.
-The stance oppose tended to have the highest recall of the three with the random forest model having higher scores: Of all the oppose cases, the random forest model found 74 percent and the KNN 64 percent.
-For the neutral stance, the random forest captured 5 percent and KNN 21 percent.
-While for the favor stance, the random forest identified 26 percent and KNN 16 percent (see Figure 1 for these results).
-Neither model excelled in how many of the stance categories identified were right as indicated by the precision scores.
-KNN slightly outperformed random forest on the oppose stance having correctly classified 56 percent vs random forest 51 percent or true oppose cases.
-For neutral the performance is worse with random forest correctly identified 50 percent and KNN 21 percent, and same for favor with random forest correctly identifying 29 percent and KNN 23 percent.
+In addition to our supervised machine learning models, we also applied
+to our data two LLMs, llama 3.2. 3B and deepseek-r1:8b. The llama model,
+developed by Meta AI released in February 2023, was designed for
+applications requiring low-latency inferencing with limited
+computational resources, which means that we were able to also deploy
+these models on a local machine with a GPU in addition to using the
+\href{https://its.umich.edu/advanced-research-computing/}{Great Lakes
+HCP}. This model also excels at text classification which is how we used
+it to classify the stance for each comment. Deepseek, developed by Liang
+Wenfeng in July 2023 and based on the llama architecture, yet boosts
+efficiency improvements that appear to provide advances in reasoning,
+logic, while excelling at natural language processing. We choose both of
+these LLMs as candidates to test against our supervised approaches
+because of their ability to apply locally and reputable performance on
+zero-shot classification tasks. Both of these models received the same
+prompt and tasked which were developed by the research team to reflect
+the utility of classifying stance within our topic of interest. Both
+LLMs resulted in not being able to classify five comments each while
+they only had one in common with the likely reason being that these
+comments did not contain enough useful text for a stance to be derive.
 
-```{r}
-#| fig-width: 7
-#| fig-height: 6
-#| 
-# number of total posts
-ml_results |> 
-  # filter models needed
-  filter(model %in% 
-           c("RandomForestClassifier", "KNeighborsClassifier"),
-         metric %in% c("precision", "recall")) |> 
-  ggplot(aes(x=model, y=value, fill=class)) +
-  geom_col(position="dodge") +  
-  coord_flip() +
-  facet_grid(~metric) +
-  guides(fill=guide_legend(title="", reverse = TRUE)) +
-  scale_fill_viridis_d(option="F", direction = -1,
-                       alpha=.85, end =.70, begin=.15) +
-  labs(
-    title = "Figure 1. Recall and precision scores for random forest
-    and KNN models.",
-    x = "Models",
-    y = "Performance Scores"
-  ) +
-  theme_hc()
+Prompt: ``Is this comment in `favor', `neutral', or `oppose' the
+reduction in federal workforce? Provide one word answer only!
 
-```
+Task: ``You have assumed the role of a stakeholder that is presented
+with a reddit comment from a likely federal worker related to the
+current policies on reducing the federal workforce. Please determine the
+author's stance on this topic, and only provide the answer.''
 
-We observe higher precision scores for the oppose stance when using the LLMs to classify stance positions.
-Of all the identified oppose stance cases these models identified, the percent of true oppose cases was 84 percent for llama and 69 percent for deepseek.
-Similarly, of all the classified neutral stance classified by these models, the percent of true neutral cases was 21 percent for llama and 42 percent for deep seek.
-Finalkly, of all the identified favor stance, the percent of true favor cases was 4 percent for llama and 10 percent for deepseek (see Figure 2 for these results).
-Recall scores were worse for the oppose stance, and of all the oppose cases the llama model captured 56 percent and deepseek 60 percent.
-For the neutral stance, llama captured 25 percent and deekseek 27 percent.
-Finally, for the favor stance, llama captured 29 percent and deekseek 32 percent.
+To evaluate model performance we used recall to determine how many of
+actual positive cases did the model correctly identify. High recall
+indicates that the model can correctly identify positive instances but
+is also optimistic and may incorrectly label cases as positive. The
+second performance metric we selected is precision, of all the items the
+model labels as positive how many are true positive, and high precision
+indicates that when the model predicts a case to be positive it is
+likely to be correct.
 
-\
+\section{Results}\label{results}
 
-```{r}
+Our machine learning models reveal a mix of performance results in
+classifying comments into one of three stance categories. Overall, the
+random forest model reduces the test misclassification error against
+KNN, yet not by much. The stance oppose tended to have the highest
+recall of the three with the random forest model having higher scores:
+Of all the oppose cases, the random forest model found 74 percent and
+the KNN 64 percent. For the neutral stance, the random forest captured 5
+percent and KNN 21 percent. While for the favor stance, the random
+forest identified 26 percent and KNN 16 percent (see Figure 1 for these
+results). Neither model excelled in how many of the stance categories
+identified were right as indicated by the precision scores. KNN slightly
+outperformed random forest on the oppose stance having correctly
+classified 56 percent vs random forest 51 percent or true oppose cases.
+For neutral the performance is worse with random forest correctly
+identified 50 percent and KNN 21 percent, and same for favor with random
+forest correctly identifying 29 percent and KNN 23 percent.
 
- cm_metric_fun <- function(dat, model_name){
+\includegraphics{assign_3_files/figure-pdf/unnamed-chunk-3-1.pdf}
 
-   subset_dat <- dat |> 
-     # truth should go first, predicted 2nd
-     select(outcome, all_of(model_name)) |> 
-     rename(predictor = 2)
+We observe higher precision scores for the oppose stance when using the
+LLMs to classify stance positions. Of all the identified oppose stance
+cases these models identified, the percent of true oppose cases was 84
+percent for llama and 69 percent for deepseek. Similarly, of all the
+classified neutral stance classified by these models, the percent of
+true neutral cases was 21 percent for llama and 42 percent for deep
+seek. Finalkly, of all the identified favor stance, the percent of true
+favor cases was 4 percent for llama and 10 percent for deepseek (see
+Figure 2 for these results). Recall scores were worse for the oppose
+stance, and of all the oppose cases the llama model captured 56 percent
+and deepseek 60 percent. For the neutral stance, llama captured 25
+percent and deekseek 27 percent. Finally, for the favor stance, llama
+captured 29 percent and deekseek 32 percent.
 
-  cm_ob = multi_class_cm(subset_dat$outcome, 
-                        subset_dat$predictor,
-                        mode="everything")
+\hfill\break
 
-  result = cm_ob$record_level_cm |> 
-   tibble() |> 
-   select(contains(c("precision", "recall", "f1"))) |> 
-   pivot_longer(everything()) |> 
-   separate(name, c("class", "metric")) |> 
-   mutate(model = model_name) |> 
-   rename(score=value)
+\includegraphics{assign_3_files/figure-pdf/unnamed-chunk-5-1.pdf}
 
-  return(result)
- }
+Llama and DeepSeek demonstrated only fair agreement in stance
+classification (Cohen's Kappa = 0.344). The contingency table, Table 2
+below, reveals highest agreement for ``oppose'' (0.58), indicating some
+consistency in identifying strong negative sentiment. However, agreement
+was substantially lower for ``neutral'' (0.11) and ``favor'' (0.02),
+highlighting divergent interpretations of more nuanced language.
+Off-diagonal values further illustrate these discrepancies, suggesting
+fundamental differences in how the models process ambiguous cues and
+establish classification boundaries, particularly for less extreme
+stances.
 
- llama_metrics <- cm_metric_fun(
-   dat = llm_results, 
-   model_name = "llama") # name of predicted column
+\begin{longtable}[]{@{}lrrr@{}}
+\caption{Aggreement between LLMs, Cohens Kappa, 0.34}\tabularnewline
+\toprule\noalign{}
+& favor & neutral & oppose \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+& favor & neutral & oppose \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+favor & 6 & 7 & 1 \\
+neutral & 3 & 42 & 14 \\
+oppose & 29 & 61 & 228 \\
+\end{longtable}
 
- deepseek_metrics <- cm_metric_fun(
-   dat = llm_results, 
-   model_name = "deepseek" # name of predicted column
- )
+\section{Conclusion}\label{conclusion}
 
- metric_results <- llama_metrics |> 
-   add_row(deepseek_metrics)
+We explored public sentimenton Reddit regarding the DOGE federal
+workforce reduction using supervised learning (KNN, Random Forest) and
+unsupervised LLMs (Llama 3.2 3B, deepseek-r1:8b) for stance
+classification. LLMs showed higher precision for ``oppose'' comments,
+suggesting better identification of negative sentiment, but lower
+recall, indicating missed opposing comments. Supervised models performed
+consistently but generally poorly across all stances, and likely due to
+the limited feature set (Reddit metadata) as well as the small sample of
+comments.
 
-```
+The consistent difficulty in classifying ``neutral'' and ``favor''
+stances across all models likely stems from class imbalance (more
+``oppose'' comments), the inherent ambiguity of neutral language, and
+potentially more nuanced expressions of favor. The zero-shot approach
+for LLMs might also limit their performance on this specific domain. The
+few unclassifiable comments highlight the inherent challenges in stance
+detection within informal online text.
 
-```{r}
-#| fig-width: 7
-#| fig-height: 6
-#| 
-metric_results |> 
-  filter(metric %in% c("Precision", "Recall")) |> 
-  ggplot(aes(x=model, y=score, fill=class)) +
-  geom_col(position="dodge") +  
-  coord_flip() +
-  facet_grid(~metric) +
-  guides(fill=guide_legend(title="", reverse = TRUE)) +
-  scale_fill_viridis_d(option="F", direction = -1,
-                       alpha=.85, end =.70, begin=.15) +
-  labs(
-    title = "Figure 2. Recall and precision scores for LLMs.",
-    x = "Models",
-    y = "Performance Scores"
-  ) +
-  theme_hc()
-```
+We conclude that while LLMs showed promise for identifying strong
+negative sentiment, accurately classifying the full spectrum of public
+opinion on Reddit regarding DOGE's actions remains challenging. Future
+research should focus on incorporating richer text-based features for
+supervised models, addressing class imbalance, and potentially
+fine-tuning LLMs to better capture the nuances of online sentiment and
+stance.
 
-Llama and DeepSeek demonstrated only fair agreement in stance classification (Cohen's Kappa = 0.344).
-The contingency table, Table 2 below, reveals highest agreement for "oppose" (0.58), indicating some consistency in identifying strong negative sentiment.
-However, agreement was substantially lower for "neutral" (0.11) and "favor" (0.02), highlighting divergent interpretations of more nuanced language.
-Off-diagonal values further illustrate these discrepancies, suggesting fundamental differences in how the models process ambiguous cues and establish classification boundaries, particularly for less extreme stances.
-
-```{r}
-cm_results <- confusionMatrix(llm_results$llama, llm_results$deepseek)
-
-coh_kappa <-  cm_results[[3]][[2]]
-
-cm_results$table |> 
-    kable(caption=str_c("Aggreement between LLMs, Cohens Kappa, ", 
-                        round(coh_kappa, 2)))
-
-```
-
-## Conclusion
-
-We explored public sentimenton Reddit regarding the DOGE federal workforce reduction using supervised learning (KNN, Random Forest) and unsupervised LLMs (Llama 3.2 3B, deepseek-r1:8b) for stance classification.
-LLMs showed higher precision for "oppose" comments, suggesting better identification of negative sentiment, but lower recall, indicating missed opposing comments.
-Supervised models performed consistently but generally poorly across all stances, and likely due to the limited feature set (Reddit metadata) as well as the small sample of comments.
-
-The consistent difficulty in classifying "neutral" and "favor" stances across all models likely stems from class imbalance (more "oppose" comments), the inherent ambiguity of neutral language, and potentially more nuanced expressions of favor.
-The zero-shot approach for LLMs might also limit their performance on this specific domain.
-The few unclassifiable comments highlight the inherent challenges in stance detection within informal online text.
-
-We conclude that while LLMs showed promise for identifying strong negative sentiment, accurately classifying the full spectrum of public opinion on Reddit regarding DOGE's actions remains challenging.
-Future research should focus on incorporating richer text-based features for supervised models, addressing class imbalance, and potentially fine-tuning LLMs to better capture the nuances of online sentiment and stance.
+\end{document}

### 2025-04-07 code/ml_llm/Python/LLMStanceTutorial.py
Changed token filepath to inside HPC

@@ -12,7 +12,7 @@ from transformers import AutoModelForCausalLM, AutoTokenizer
 from huggingface_hub import login
 
 # Read the token from the file
-with open("/Users/felbasa/Desktop/token.txt", "r") as token_file:
+with open("/home/felbasa/token.txt", "r") as token_file:
     token = token_file.read().strip()
 
 # Log in to Hugging Face using the token

### 2025-04-08 code/ml_llm/R/assign_3.qmd
adding paper

@@
 ---
-title: "DOGE Days on Reddit: Decoding Public Sentiment in a Federal Shakeup"
+title: "DOGE's Downsizing, Can AI Read the Reddit Room?"
 format:
@@
 abstract: |
-   This study investigates public sentiment on Reddit towards the Department of Government Efficiency's (DOGE) federal workforce reduction.
-Analyzing 400 labeled Reddit comments, we employed supervised learning (KNN, Random Forest) and unsupervised Large Language Models (LLMs: Llama 3.2 3B, deepseek-r1:8b) to classify comment stance (favor, neutral, oppose).
-While LLMs showed higher precision for opposing comments, all models struggled with neutral and favoring stances.
-Agreement between the two LLMs was fair (Cohen's Kappa = 0.344), indicating divergent interpretations.
-Results suggest that accurately decoding nuanced public sentiment in this context remains challenging for both traditional and large language models.
+ We investigate public sentiment on Reddit regarding the Department of Government Efficiency's federal workforce reduction by classifying 400 labeled comments (28% favor, 18% neutral, 54% oppose) using supervised and unsupervised Large Language Models.
+Supervised models showed moderate success, particularly with "oppose" comments, but struggled with "favor" and "neutral" stances.
+Similarly, LLMs best identified "oppose" sentiment but exhibited low precision for "favor" and "neutral." These findings highlight the challenges of accurately gauging nuanced public opinion on government policy changes using automated methods on social media data.
 
@@
 library(ConfusionTableR)
-library(caret)
 library(tidyverse)
@@
   distinct() |> 
-  mutate(model = str_remove(model,  "^[^|]+\\.")) |> 
-  tibble()
+  mutate(model = str_remove(model,  "^[^|]+\\."),
+         model = str_remove(model, "Classifier")) |> 
+  tibble() |> 
+  rename(score=value)
 
-llm_results <- read_xlsx(str_c(
-  results_folder, "reddit_comments_LLM_analysis.xlsx")) |> 
+llama_results <- read_xlsx(str_c(
+  results_folder, "reddit_comments_LLM_analysis_llama.xlsx")) |> 
   mutate_at(vars(outcome, llama, deepseek), factor)
+
+gemma_results <- read_csv(str_c(
+  results_folder, "reddit_comments_LLM_analysis_gemma.csv")) |> 
+  mutate( gemma = factor(LLM_stance))
+
+# merge results
+llm_results <- llama_results |> 
+  add_column(gemma_results |> select(gemma))
 ```
@@
 
-Established in January 2025, the Department of Government Efficiency (DOGE) has significantly reduced the federal workforce by over 280,000 employees, fulfilling a key campaign promise of the new administration.
-This has caused widespread concern and anxiety among federal workers about job security and mental well-being.
-Questions have also been raised regarding DOGE's adherence to internal policies.
-To understand the impact of DOGE's actions on federal worker perceptions of job security, we collected 400 reddit comments on topics related to DOGE's tactics in reducing the federal workforce.
-Additionally, a team of researchers labeled each comment as whether the author favored, opposed, or had a neutral stance concerning how DOGE was implementing these strategies.
-In the current study we employ two supervise learning model to predict, given a set of features, comments on stance.
-We also employ an unsupervised large language model (LLM) to detect the stance of these reddit comments and report model findings.
+The newly formed Department of Government Efficiency (DOGE) has reduced the federal workforce by almost 280,000 employees, a central pledge of the current administration.
+This action has generated significant apprehension among federal workers in regards to mental health and job security.
+To understand the impact of DOGE's actions on federal worker perceptions of job security, we labeled 400 Reddit comments on topics related to the current reduction in *federal* workforce by DOGE as whether the author favored, opposed, or had a neutral stance.
+We use these labels to build supervised learning models to predict stance.
+Additionally, we employ unsupervised large language models (LLM) to detect the stance of these Reddit comments from text, to further explore appropriate models for this current topic.
 
@@
 We collected Reddit comments from subreddits related to the topic of interest in early March of 2024.
-This resulted in 12,553 comments which we preprocessed by removing weblinks, replace special characters (i.e., replaced "\@" with "at"), replaced numeric values with their spelling, and confirmed the absence of duplicate comments.
+This resulted in 12,553 comments which we preprocessed by removing web-URLs, replace special characters (i.e., replaced "\@" with "at"), replaced numeric values with their spelling, and confirmed the absence of duplicate comments.
 We then randomly selected 400 comments (without replacement) and assigned them to four graduate students for coding, categorizing each comment as favoring, opposing, or neutral towards DOGE's approach to federal workforce reductions.
@@
 
-We built two supervised machine learning models, K-nearest neighbor and random forest, to classify Reddit comments concerning stance on the current reduction in federal workforce into favor, oppose, or neutral.
-For model predictors we used the Reddit score, up-votes, and down-votes each comment received at the time of the collection.
+We built two supervised machine learning models–K-nearest neighbor and random forest–to classify Reddit comments concerning stance on the current reduction in federal workforce into favor, oppose, or neutral.
+For predictors we used the Reddit score, up-votes, and down-votes each comment received at the time of the collection.
 Additionally, we used the keyword that was used to scrape these data along with the subreddit where the comment was posted.
-DISCUSS ADDITIONAL FEATURE ENGINERRING SUCH AS TEXT EDITING THAT WENT INTO THE MODEL.
-For the KNN model, we set the number of neighbors hyperparameter to thhree, and for the random forest, mtry was kept at a constant two as we did not have many features in these models.
+**DISCUSS ADDITIONAL FEATURE ENGINERRING SUCH AS TEXT EDITING THAT WENT INTO THE MODEL.** For the KNN model, we set the number of neighbors hyperparameter to three, and for the random forest, mtry was kept at a constant two as we did not have many features in these models.
 We took an 80/20 split for our training-testing sets that we used to train each model and evaluate.
 
-In addition to our supervised machine learning models, we also applied to our data two LLMs, llama 3.2.
-3B and deepseek-r1:8b.
-The llama model, developed by Meta AI released in February 2023, was designed for applications requiring low-latency inferencing with limited computational resources, which means that we were able to also deploy these models on a local machine with a GPU in addition to using the [Great Lakes HCP](https://its.umich.edu/advanced-research-computing/).
-This model also excels at text classification which is how we used it to classify the stance for each comment.
-Deepseek, developed by Liang Wenfeng in July 2023 and based on the llama architecture, yet boosts efficiency improvements that appear to provide advances in reasoning, logic, while excelling at natural language processing.
+In addition to our supervised machine learning models, we also applied to our comments two LLMs, gemma 3.12 and llama 3.2.
+3B.
+Gemma, was developed by Google and is based on Gemini, is able to generate text output using instruction-tuned prompts from the user, such as providing answers on a user specified task reviewing text.
+We deployed gemma on a higher performance computing cluster ([Great Lakes HCP](https://its.umich.edu/advanced-research-computing/)) and processed text from Reddit comments on a GPU.
+We were also interested in deploying other lightweight LLMs locally on a machine with a dedicated-GPU and found llama, developed by Meta AI, to be an excellent candidate.
+Llama excels at text classification which is how we used it to classify the stance for each comment text given a user specified prompt.
 We choose both of these LLMs as candidates to test against our supervised approaches because of their ability to apply locally and reputable performance on zero-shot classification tasks.
 Both of these models received the same prompt and tasked which were developed by the research team to reflect the utility of classifying stance within our topic of interest.
-Both LLMs resulted in not being able to classify five comments each while they only had one in common with the likely reason being that these comments did not contain enough useful text for a stance to be derive.
 
-Prompt: "Is this comment in 'favor', 'neutral', or 'oppose' the reduction in federal workforce? Provide one word answer only!
+|  |  |
+|----------------|--------------------------------------------------------|
+| **Prompt**: | "Is this comment in 'favor', 'neutral', or 'oppose' the reduction in federal workforce? Provide one word answer only! |
+| **Task**: | "You have assumed the role of a stakeholder that is presented with a reddit comment from a likely federal worker related to the current policies on reducing the federal workforce.
+Please determine the author's stance on this topic, and only provide the answer." |
 
-Task: "You have assumed the role of a stakeholder that is presented with a reddit comment from a likely federal worker related to the current policies on reducing the federal workforce.
-Please determine the author's stance on this topic, and only provide the answer."
-
-To evaluate model performance we used recall to determine how many of actual positive cases did the model correctly identify.
-High recall indicates that the model can correctly identify positive instances but is also optimistic and may incorrectly label cases as positive.
-The second performance metric we selected is precision, of all the items the model labels as positive how many are true positive, and high precision indicates that when the model predicts a case to be positive it is likely to be correct.
+We evaluate model performance using the F1-score which is a harmonic mean balance between precision and recall.
+This metric considers both the ability to correctly identify positive instances, known as recall, and the ability to avoid incorrectly labeling negative instances as positive (i.e., precision).
+A high F1-score indicates a model with well balanced recall and precision that both minimize false negativesand false positives.
+The second performance metric we used is recall, as this determines how many of the actual positive cases the model can correctly identify.
+Recall can be prone to incorrectly labeling negative cases as positive, suggesting more false positives, which is why we intereggoate on two performance metrics in this study.
 
@@
 
-Our machine learning models reveal a mix of performance results in classifying comments into one of three stance categories.
-Overall, the random forest model reduces the test misclassification error against KNN, yet not by much.
-The stance oppose tended to have the highest recall of the three with the random forest model having higher scores: Of all the oppose cases, the random forest model found 74 percent and the KNN 64 percent.
-For the neutral stance, the random forest captured 5 percent and KNN 21 percent.
-While for the favor stance, the random forest identified 26 percent and KNN 16 percent (see Figure 1 for these results).
-Neither model excelled in how many of the stance categories identified were right as indicated by the precision scores.
-KNN slightly outperformed random forest on the oppose stance having correctly classified 56 percent vs random forest 51 percent or true oppose cases.
-For neutral the performance is worse with random forest correctly identified 50 percent and KNN 21 percent, and same for favor with random forest correctly identifying 29 percent and KNN 23 percent.
+Our machine learning models reveal a mix of performance results in classifying the stance of Reddit comment into favor, neutral, oppose.
+Both models exhibit low recall and F1-scores for the "favor" stance (see Figure 1), yet the random forest model (recall .26: f1-score .28) slightly outperforms KNN (recall .16: f1-score .19).
+The "neutral" class presented a significant challenge for the random forest with very low scores (recall .05: f1-score .10), while KNN exhibited slightly better performance (recall .21: f1-score .21).
+Both models showed the strongest performance in identifying comments expressing opposition.
+The random forest correctly identified 74 percent of all the actual Reddit comments expressing opposition compared to KNN at 64 percent, meaning that KNN missed a larger proportion of true "oppose" comments.
+The f1-scores were similar for both models at 60 percent, this implies that KNN may have a slightly higher precision score given that it had a lower recall score than the random forest model.
+This implies that when KNN predicts comments for the "oppose" class, it is as likely as the random forest to be correct.
 
@@
   filter(model %in% 
-           c("RandomForestClassifier", "KNeighborsClassifier"),
-         metric %in% c("precision", "recall")) |> 
-  ggplot(aes(x=model, y=value, fill=class)) +
+           c("RandomForest", "KNeighbors"),
+         metric %in% c("f1-score", "recall")) |> 
+  ggplot(aes(x=model, y=score, fill=class)) +
   geom_col(position="dodge") +  
@@
 
-We observe higher precision scores for the oppose stance when using the LLMs to classify stance positions.
-Of all the identified oppose stance cases these models identified, the percent of true oppose cases was 84 percent for llama and 69 percent for deepseek.
-Similarly, of all the classified neutral stance classified by these models, the percent of true neutral cases was 21 percent for llama and 42 percent for deep seek.
-Finalkly, of all the identified favor stance, the percent of true favor cases was 4 percent for llama and 10 percent for deepseek (see Figure 2 for these results).
-Recall scores were worse for the oppose stance, and of all the oppose cases the llama model captured 56 percent and deepseek 60 percent.
-For the neutral stance, llama captured 25 percent and deekseek 27 percent.
-Finally, for the favor stance, llama captured 29 percent and deekseek 32 percent.
-
-\
+The LLMs, showed poor performance in classifying the "favor" stance, with very low f1-scores (llama .07: gemma .02) despite moderate recall (llama .29: gemma .33), indicating low precision (see Figure 2).
+For the "neutral" class, both models showed modest results, with llama achieving a slightly better F1-score (.23) compared to gemma (0.18), although gemma had a higher recall (.50 vs .25), again suggesting lower precision for gemma.
+Similar to the supervised models, both LLMs performed best in classifying the "oppose" stance, with relatively high and similar F1-scores (llama .67: gemma .70) and comparable recall (llama .56: gemma .56), suggesting a better balance between precision and recall for this category.
+Both models correctly identify 67 to 70 percent of all the actual Reddit comments expressing opposition.
+Overall, both LLMs struggled with the "favor" and "neutral" classes but demonstrated a stronger ability to identify opposing comments.\
 
@@
    tibble() |> 
-   select(contains(c("precision", "recall", "f1"))) |> 
+   select(contains(c("f1", "recall"))) |> 
    pivot_longer(everything()) |> 
@@
 
- deepseek_metrics <- cm_metric_fun(
+gemma_metrics <- cm_metric_fun(
    dat = llm_results, 
-   model_name = "deepseek" # name of predicted column
+   model_name = "gemma" # name of predicted column
  )
@@
  metric_results <- llama_metrics |> 
-   add_row(deepseek_metrics)
+   add_row(gemma_metrics)
 
@@
 metric_results |> 
-  filter(metric %in% c("Precision", "Recall")) |> 
+  filter(metric %in% c("F1", "Recall")) |> 
   ggplot(aes(x=model, y=score, fill=class)) +
@@
 
-Llama and DeepSeek demonstrated only fair agreement in stance classification (Cohen's Kappa = 0.344).
-The contingency table, Table 2 below, reveals highest agreement for "oppose" (0.58), indicating some consistency in identifying strong negative sentiment.
-However, agreement was substantially lower for "neutral" (0.11) and "favor" (0.02), highlighting divergent interpretations of more nuanced language.
+Gemma and llama demonstrated only fair agreement in stance classification (Cohen's Kappa = .24).
+The contingency table, Table 2 below, reveals highest agreement for "oppose" (.80), indicating some consistency in identifying a strong negative stance.
+However, agreement was substantially lower for "neutral" (.03) and "favor" (.01), highlighting divergent interpretations of more nuanced language.
 Off-diagonal values further illustrate these discrepancies, suggesting fundamental differences in how the models process ambiguous cues and establish classification boundaries, particularly for less extreme stances.
@@
 ```{r}
-cm_results <- confusionMatrix(llm_results$llama, llm_results$deepseek)
+cm_results <- multi_class_cm(llm_results$llama, 
+                              llm_results$gemma)
 
-coh_kappa <-  cm_results[[3]][[2]]
+coh_kappa <-  cm_results$record_level_cm |> 
+  pull(contains("Kappa"))
 
-cm_results$table |> 
+cm_results$cm_tbl |> 
     kable(caption=str_c("Aggreement between LLMs, Cohens Kappa, ", 
@@
 
-We explored public sentimenton Reddit regarding the DOGE federal workforce reduction using supervised learning (KNN, Random Forest) and unsupervised LLMs (Llama 3.2 3B, deepseek-r1:8b) for stance classification.
-LLMs showed higher precision for "oppose" comments, suggesting better identification of negative sentiment, but lower recall, indicating missed opposing comments.
-Supervised models performed consistently but generally poorly across all stances, and likely due to the limited feature set (Reddit metadata) as well as the small sample of comments.
+We explored public sentiment on Reddit regarding the DOGE federal workforce reduction using supervised learning (KNN, Random Forest) and unsupervised LLMs ( gemma 3.12b and Llama 3.2 3B) for stance classification.
+Our supervised learning models achieved moderate success in this classification task, with the strongest performance in identifying opposing viewpoints, which were also the most prevalent in our labeled data.
+Moreover, both models struggled with the "favor" and "neutral" stances, suggesting limitations in our initial features to capture these nuances.
+Our unsupervised learning models also showed the best ability to classify "oppose" comments, yet exhibited significant challenges with the "favor" and "neutral" categories, particularly demonstrating low precision.
 
-The consistent difficulty in classifying "neutral" and "favor" stances across all models likely stems from class imbalance (more "oppose" comments), the inherent ambiguity of neutral language, and potentially more nuanced expressions of favor.
-The zero-shot approach for LLMs might also limit their performance on this specific domain.
-The few unclassifiable comments highlight the inherent challenges in stance detection within informal online text.
-
-We conclude that while LLMs showed promise for identifying strong negative sentiment, accurately classifying the full spectrum of public opinion on Reddit regarding DOGE's actions remains challenging.
-Future research should focus on incorporating richer text-based features for supervised models, addressing class imbalance, and potentially fine-tuning LLMs to better capture the nuances of online sentiment and stance.
+This study had limitations such as the small size of our labelled dataset of 400 Reddit, imbalance in the stance categories, and few features in the supervised approach.
+The zero-shot capabilities of the LLMs are suitable for topic exploration but may require fine-tuning for optimal performance on this specific domain, particularly with nuance language used in "favor" comments.
+Future research should continue to understand federal worker perceptions and improve stance classification by expanding labeled dataset and incorporate more contextual text rather than single comment text.
+Fine tuning LLMs on a larger corpus with relevant comments could render more accuracy in the classification task.

### 2025-04-08 code/ml_llm/R/assign_3.tex
adding paper

@@
 \hypersetup{
-  pdftitle={DOGE Days on Reddit: Decoding Public Sentiment in a Federal Shakeup},
+  pdftitle={DOGE's Downsizing, Can AI Read the Reddit Room?},
   pdfauthor={Kevin Linares; Felix Baez-Santiago; Aria Lu; Gloria Zhou},
@@
 
-\date{April 7, 2025}
-\title{\bf DOGE Days on Reddit: Decoding Public Sentiment in a Federal
-Shakeup}
+\date{April 8, 2025}
+\title{\bf DOGE's Downsizing, Can AI Read the Reddit Room?}
 \author{
@@
 \begin{abstract}
-This study investigates public sentiment on Reddit towards the
-Department of Government Efficiency's (DOGE) federal workforce
-reduction. Analyzing 400 labeled Reddit comments, we employed supervised
-learning (KNN, Random Forest) and unsupervised Large Language Models
-(LLMs: Llama 3.2 3B, deepseek-r1:8b) to classify comment stance (favor,
-neutral, oppose). While LLMs showed higher precision for opposing
-comments, all models struggled with neutral and favoring stances.
-Agreement between the two LLMs was fair (Cohen's Kappa = 0.344),
-indicating divergent interpretations. Results suggest that accurately
-decoding nuanced public sentiment in this context remains challenging
-for both traditional and large language models.
+We investigate public sentiment on Reddit regarding the Department of
+Government Efficiency's federal workforce reduction by classifying 400
+labeled comments (28\% favor, 18\% neutral, 54\% oppose) using
+supervised and unsupervised Large Language Models. Supervised models
+showed moderate success, particularly with ``oppose'' comments, but
+struggled with ``favor'' and ``neutral'' stances. Similarly, LLMs best
+identified ``oppose'' sentiment but exhibited low precision for
+``favor'' and ``neutral.'' These findings highlight the challenges of
+accurately gauging nuanced public opinion on government policy changes
+using automated methods on social media data.
 \end{abstract}
@@
 
-Established in January 2025, the Department of Government Efficiency
-(DOGE) has significantly reduced the federal workforce by over 280,000
-employees, fulfilling a key campaign promise of the new administration.
-This has caused widespread concern and anxiety among federal workers
-about job security and mental well-being. Questions have also been
-raised regarding DOGE's adherence to internal policies. To understand
-the impact of DOGE's actions on federal worker perceptions of job
-security, we collected 400 reddit comments on topics related to DOGE's
-tactics in reducing the federal workforce. Additionally, a team of
-researchers labeled each comment as whether the author favored, opposed,
-or had a neutral stance concerning how DOGE was implementing these
-strategies. In the current study we employ two supervise learning model
-to predict, given a set of features, comments on stance. We also employ
-an unsupervised large language model (LLM) to detect the stance of these
-reddit comments and report model findings.
+The newly formed Department of Government Efficiency (DOGE) has reduced
+the federal workforce by almost 280,000 employees, a central pledge of
+the current administration. This action has generated significant
+apprehension among federal workers in regards to mental health and job
+security. To understand the impact of DOGE's actions on federal worker
+perceptions of job security, we labeled 400 Reddit comments on topics
+related to the current reduction in \emph{federal} workforce by DOGE as
+whether the author favored, opposed, or had a neutral stance. We use
+these labels to build supervised learning models to predict stance.
+Additionally, we employ unsupervised large language models (LLM) to
+detect the stance of these Reddit comments from text, to further explore
+appropriate models for this current topic.
 
@@
 topic of interest in early March of 2024. This resulted in 12,553
-comments which we preprocessed by removing weblinks, replace special
+comments which we preprocessed by removing web-URLs, replace special
 characters (i.e., replaced ``@'' with ``at''), replaced numeric values
@@
 
-We built two supervised machine learning models, K-nearest neighbor and
-random forest, to classify Reddit comments concerning stance on the
+We built two supervised machine learning models--K-nearest neighbor and
+random forest--to classify Reddit comments concerning stance on the
 current reduction in federal workforce into favor, oppose, or neutral.
-For model predictors we used the Reddit score, up-votes, and down-votes
-each comment received at the time of the collection. Additionally, we
-used the keyword that was used to scrape these data along with the
-subreddit where the comment was posted. DISCUSS ADDITIONAL FEATURE
-ENGINERRING SUCH AS TEXT EDITING THAT WENT INTO THE MODEL. For the KNN
-model, we set the number of neighbors hyperparameter to thhree, and for
+For predictors we used the Reddit score, up-votes, and down-votes each
+comment received at the time of the collection. Additionally, we used
+the keyword that was used to scrape these data along with the subreddit
+where the comment was posted. \textbf{DISCUSS ADDITIONAL FEATURE
+ENGINERRING SUCH AS TEXT EDITING THAT WENT INTO THE MODEL.} For the KNN
+model, we set the number of neighbors hyperparameter to three, and for
 the random forest, mtry was kept at a constant two as we did not have
@@
 In addition to our supervised machine learning models, we also applied
-to our data two LLMs, llama 3.2. 3B and deepseek-r1:8b. The llama model,
-developed by Meta AI released in February 2023, was designed for
-applications requiring low-latency inferencing with limited
-computational resources, which means that we were able to also deploy
-these models on a local machine with a GPU in addition to using the
-\href{https://its.umich.edu/advanced-research-computing/}{Great Lakes
-HCP}. This model also excels at text classification which is how we used
-it to classify the stance for each comment. Deepseek, developed by Liang
-Wenfeng in July 2023 and based on the llama architecture, yet boosts
-efficiency improvements that appear to provide advances in reasoning,
-logic, while excelling at natural language processing. We choose both of
-these LLMs as candidates to test against our supervised approaches
-because of their ability to apply locally and reputable performance on
-zero-shot classification tasks. Both of these models received the same
-prompt and tasked which were developed by the research team to reflect
-the utility of classifying stance within our topic of interest. Both
-LLMs resulted in not being able to classify five comments each while
-they only had one in common with the likely reason being that these
-comments did not contain enough useful text for a stance to be derive.
+to our comments two LLMs, gemma 3.12 and llama 3.2. 3B. Gemma, was
+developed by Google and is based on Gemini, is able to generate text
+output using instruction-tuned prompts from the user, such as providing
+answers on a user specified task reviewing text. We deployed gemma on a
+higher performance computing cluster
+(\href{https://its.umich.edu/advanced-research-computing/}{Great Lakes
+HCP}) and processed text from Reddit comments on a GPU. We were also
+interested in deploying other lightweight LLMs locally on a machine with
+a dedicated-GPU and found llama, developed by Meta AI, to be an
+excellent candidate. Llama excels at text classification which is how we
+used it to classify the stance for each comment text given a user
+specified prompt. We choose both of these LLMs as candidates to test
+against our supervised approaches because of their ability to apply
+locally and reputable performance on zero-shot classification tasks.
+Both of these models received the same prompt and tasked which were
+developed by the research team to reflect the utility of classifying
+stance within our topic of interest.
 
-Prompt: ``Is this comment in `favor', `neutral', or `oppose' the
-reduction in federal workforce? Provide one word answer only!
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.2222}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.7778}}@{}}
+\toprule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+\textbf{Prompt}: & ``Is this comment in `favor', `neutral', or `oppose'
+the reduction in federal workforce? Provide one word answer only! \\
+\textbf{Task}: & ``You have assumed the role of a stakeholder that is
+presented with a reddit comment from a likely federal worker related to
+the current policies on reducing the federal workforce. Please determine
+the author's stance on this topic, and only provide the answer.'' \\
+\end{longtable}
 
-Task: ``You have assumed the role of a stakeholder that is presented
-with a reddit comment from a likely federal worker related to the
-current policies on reducing the federal workforce. Please determine the
-author's stance on this topic, and only provide the answer.''
-
-To evaluate model performance we used recall to determine how many of
-actual positive cases did the model correctly identify. High recall
-indicates that the model can correctly identify positive instances but
-is also optimistic and may incorrectly label cases as positive. The
-second performance metric we selected is precision, of all the items the
-model labels as positive how many are true positive, and high precision
-indicates that when the model predicts a case to be positive it is
-likely to be correct.
+We evaluate model performance using the F1-score which is a harmonic
+mean balance between precision and recall. This metric considers both
+the ability to correctly identify positive instances, known as recall,
+and the ability to avoid incorrectly labeling negative instances as
+positive (i.e., precision). A high F1-score indicates a model with well
+balanced recall and precision that both minimize false negativesand
+false positives. The second performance metric we used is recall, as
+this determines how many of the actual positive cases the model can
+correctly identify. Recall can be prone to incorrectly labeling negative
+cases as positive, suggesting more false positives, which is why we
+intereggoate on two performance metrics in this study.
 
@@
 Our machine learning models reveal a mix of performance results in
-classifying comments into one of three stance categories. Overall, the
-random forest model reduces the test misclassification error against
-KNN, yet not by much. The stance oppose tended to have the highest
-recall of the three with the random forest model having higher scores:
-Of all the oppose cases, the random forest model found 74 percent and
-the KNN 64 percent. For the neutral stance, the random forest captured 5
-percent and KNN 21 percent. While for the favor stance, the random
-forest identified 26 percent and KNN 16 percent (see Figure 1 for these
-results). Neither model excelled in how many of the stance categories
-identified were right as indicated by the precision scores. KNN slightly
-outperformed random forest on the oppose stance having correctly
-classified 56 percent vs random forest 51 percent or true oppose cases.
-For neutral the performance is worse with random forest correctly
-identified 50 percent and KNN 21 percent, and same for favor with random
-forest correctly identifying 29 percent and KNN 23 percent.
+classifying the stance of Reddit comment into favor, neutral, oppose.
+Both models exhibit low recall and F1-scores for the ``favor'' stance
+(see Figure 1), yet the random forest model (recall .26: f1-score .28)
+slightly outperforms KNN (recall .16: f1-score .19). The ``neutral''
+class presented a significant challenge for the random forest with very
+low scores (recall .05: f1-score .10), while KNN exhibited slightly
+better performance (recall .21: f1-score .21). Both models showed the
+strongest performance in identifying comments expressing opposition. The
+random forest correctly identified 74 percent of all the actual Reddit
+comments expressing opposition compared to KNN at 64 percent, meaning
+that KNN missed a larger proportion of true ``oppose'' comments. The
+f1-scores were similar for both models at 60 percent, this implies that
+KNN may have a slightly higher precision score given that it had a lower
+recall score than the random forest model. This implies that when KNN
+predicts comments for the ``oppose'' class, it is as likely as the
+random forest to be correct.
 
@@
 
-We observe higher precision scores for the oppose stance when using the
-LLMs to classify stance positions. Of all the identified oppose stance
-cases these models identified, the percent of true oppose cases was 84
-percent for llama and 69 percent for deepseek. Similarly, of all the
-classified neutral stance classified by these models, the percent of
-true neutral cases was 21 percent for llama and 42 percent for deep
-seek. Finalkly, of all the identified favor stance, the percent of true
-favor cases was 4 percent for llama and 10 percent for deepseek (see
-Figure 2 for these results). Recall scores were worse for the oppose
-stance, and of all the oppose cases the llama model captured 56 percent
-and deepseek 60 percent. For the neutral stance, llama captured 25
-percent and deekseek 27 percent. Finally, for the favor stance, llama
-captured 29 percent and deekseek 32 percent.
-
-\hfill\break
+The LLMs, showed poor performance in classifying the ``favor'' stance,
+with very low f1-scores (llama .07: gemma .02) despite moderate recall
+(llama .29: gemma .33), indicating low precision (see Figure 2). For the
+``neutral'' class, both models showed modest results, with llama
+achieving a slightly better F1-score (.23) compared to gemma (0.18),
+although gemma had a higher recall (.50 vs .25), again suggesting lower
+precision for gemma. Similar to the supervised models, both LLMs
+performed best in classifying the ``oppose'' stance, with relatively
+high and similar F1-scores (llama .67: gemma .70) and comparable recall
+(llama .56: gemma .56), suggesting a better balance between precision
+and recall for this category. Both models correctly identify 67 to 70
+percent of all the actual Reddit comments expressing opposition.
+Overall, both LLMs struggled with the ``favor'' and ``neutral'' classes
+but demonstrated a stronger ability to identify opposing comments.\\
 
@@
 
-Llama and DeepSeek demonstrated only fair agreement in stance
-classification (Cohen's Kappa = 0.344). The contingency table, Table 2
-below, reveals highest agreement for ``oppose'' (0.58), indicating some
-consistency in identifying strong negative sentiment. However, agreement
-was substantially lower for ``neutral'' (0.11) and ``favor'' (0.02),
+Gemma and llama demonstrated only fair agreement in stance
+classification (Cohen's Kappa = .24). The contingency table, Table 2
+below, reveals highest agreement for ``oppose'' (.80), indicating some
+consistency in identifying a strong negative stance. However, agreement
+was substantially lower for ``neutral'' (.03) and ``favor'' (.01),
 highlighting divergent interpretations of more nuanced language.
@@
 \begin{longtable}[]{@{}lrrr@{}}
-\caption{Aggreement between LLMs, Cohens Kappa, 0.34}\tabularnewline
+\caption{Aggreement between LLMs, Cohens Kappa, 0.24}\tabularnewline
 \toprule\noalign{}
@@
 \endlastfoot
-favor & 6 & 7 & 1 \\
-neutral & 3 & 42 & 14 \\
-oppose & 29 & 61 & 228 \\
+favor & 3 & 1 & 10 \\
+neutral & 0 & 10 & 49 \\
+oppose & 0 & 5 & 317 \\
 \end{longtable}
@@
 
-We explored public sentimenton Reddit regarding the DOGE federal
+We explored public sentiment on Reddit regarding the DOGE federal
 workforce reduction using supervised learning (KNN, Random Forest) and
-unsupervised LLMs (Llama 3.2 3B, deepseek-r1:8b) for stance
-classification. LLMs showed higher precision for ``oppose'' comments,
-suggesting better identification of negative sentiment, but lower
-recall, indicating missed opposing comments. Supervised models performed
-consistently but generally poorly across all stances, and likely due to
-the limited feature set (Reddit metadata) as well as the small sample of
-comments.
+unsupervised LLMs ( gemma 3.12b and Llama 3.2 3B) for stance
+classification. Our supervised learning models achieved moderate success
+in this classification task, with the strongest performance in
+identifying opposing viewpoints, which were also the most prevalent in
+our labeled data. Moreover, both models struggled with the ``favor'' and
+``neutral'' stances, suggesting limitations in our initial features to
+capture these nuances. Our unsupervised learning models also showed the
+best ability to classify ``oppose'' comments, yet exhibited significant
+challenges with the ``favor'' and ``neutral'' categories, particularly
+demonstrating low precision.
 
-The consistent difficulty in classifying ``neutral'' and ``favor''
-stances across all models likely stems from class imbalance (more
-``oppose'' comments), the inherent ambiguity of neutral language, and
-potentially more nuanced expressions of favor. The zero-shot approach
-for LLMs might also limit their performance on this specific domain. The
-few unclassifiable comments highlight the inherent challenges in stance
-detection within informal online text.
-
-We conclude that while LLMs showed promise for identifying strong
-negative sentiment, accurately classifying the full spectrum of public
-opinion on Reddit regarding DOGE's actions remains challenging. Future
-research should focus on incorporating richer text-based features for
-supervised models, addressing class imbalance, and potentially
-fine-tuning LLMs to better capture the nuances of online sentiment and
-stance.
+This study had limitations such as the small size of our labelled
+dataset of 400 Reddit, imbalance in the stance categories, and few
+features in the supervised approach. The zero-shot capabilities of the
+LLMs are suitable for topic exploration but may require fine-tuning for
+optimal performance on this specific domain, particularly with nuance
+language used in ``favor'' comments. Future research should continue to
+understand federal worker perceptions and improve stance classification
+by expanding labeled dataset and incorporate more contextual text rather
+than single comment text. Fine tuning LLMs on a larger corpus with
+relevant comments could render more accuracy in the classification task.
 

### 2025-04-09 code/ml_llm/R/assign_3.qmd
2nd round of assing 3 paper

@@
 abstract: |
- We investigate public sentiment on Reddit regarding the Department of Government Efficiency's federal workforce reduction by classifying 400 labeled comments (28% favor, 18% neutral, 54% oppose) using supervised and unsupervised Large Language Models.
+  We investigate public sentiment on Reddit regarding the Department of Government Efficiency's federal workforce reduction by classifying 400 labeled comments (28% favor, 18% neutral, 54% oppose) using supervised and unsupervised Large Language Models (LLM).
 Supervised models showed moderate success, particularly with "oppose" comments, but struggled with "favor" and "neutral" stances.
@@
 # read in ML results from repo
-results_folder <- "~/repos/SURV622_Assignment/outputs/ml_llm/"
+results_folder <- "~/work/d/SURV622_Assignment/outputs/ml_llm/"
 
@@
 
-## Methods {#sec-meth}
+## Method {#sec-meth}
 
-*Data*.
-We collected Reddit comments from subreddits related to the topic of interest in early March of 2024.
-This resulted in 12,553 comments which we preprocessed by removing web-URLs, replace special characters (i.e., replaced "\@" with "at"), replaced numeric values with their spelling, and confirmed the absence of duplicate comments.
-We then randomly selected 400 comments (without replacement) and assigned them to four graduate students for coding, categorizing each comment as favoring, opposing, or neutral towards DOGE's approach to federal workforce reductions.
-Table 1 presents the breakdown in percent of our the comments we labelled and later use to train and evaluate our machine learning models.
-A review of the comments revealed more negative opinionated statements and reactions.
+We collected a total of 12,553 Reddit comments in early March 2024 from subreddits relevant to the topic of interest.
+These comments were retrieved using keyword-based queries designed to capture posts of discussions that would reflect users’ stances on the federal workforce reduction by DOGE.
+To prepare the data for analysis, a comprehensive preprocessing pipline were conducted in Pytho 3.
+This process involved removing HTML tags and web-URLs, stripping special characters and tagging artifacts such as “\@”, and replacing emojis with textual descriptions.
+Also, it entailed eliminating punctuations and converting numerical values into their spelled-out forms.
+The text was standardized to lowercase, lemmatized using the SpaCy library, and further refined by removing stopwords per the Natural Language Toolkit (NLTK) lists.
+Spelling corrections were performed to improve textual coherence, while Duplicate comments were identified and removed to maintain data integrity.
+
+From this cleaned dataset, 400 uniqe comments without replacement were randomly sampled for manual annotation.
+Four graudate students independently coded and labeled each comment with one of three possible stances:favor, opopose, or neutral toward DOGE’s approach to federal workforce reductions.
+As shown in Table 1, there were 28% favor, 18% neutral, and 54% oppose.
+These labeled comments were subsequently used for training and evaluating both supervised and unsupervised classification models.
 
@@
 
-We built two supervised machine learning models–K-nearest neighbor and random forest–to classify Reddit comments concerning stance on the current reduction in federal workforce into favor, oppose, or neutral.
-For predictors we used the Reddit score, up-votes, and down-votes each comment received at the time of the collection.
-Additionally, we used the keyword that was used to scrape these data along with the subreddit where the comment was posted.
-**DISCUSS ADDITIONAL FEATURE ENGINERRING SUCH AS TEXT EDITING THAT WENT INTO THE MODEL.** For the KNN model, we set the number of neighbors hyperparameter to three, and for the random forest, mtry was kept at a constant two as we did not have many features in these models.
-We took an 80/20 split for our training-testing sets that we used to train each model and evaluate.
+The feature set used in model training and evluation consisted of two primary categories: metadata features and textual features.
+Metadata features included the Reddit comment’s score, the subreddit in which it appeared in, and the search term that retrieved it.
+As the variables for score and upvotes were perfectly collinear in this dataset, only the score was retained.
+To ensure all values were non-negative, the score was adjusted by subtracting the dataset’s minimum value from each score.
+The categorical variables, subreddit and search term, were numerically encoded using scikit-learn’s label encoder.
 
-In addition to our supervised machine learning models, we also applied to our comments two LLMs, gemma 3.12 and llama 3.2.
-3B.
-Gemma, was developed by Google and is based on Gemini, is able to generate text output using instruction-tuned prompts from the user, such as providing answers on a user specified task reviewing text.
-We deployed gemma on a higher performance computing cluster ([Great Lakes HCP](https://its.umich.edu/advanced-research-computing/)) and processed text from Reddit comments on a GPU.
-We were also interested in deploying other lightweight LLMs locally on a machine with a dedicated-GPU and found llama, developed by Meta AI, to be an excellent candidate.
-Llama excels at text classification which is how we used it to classify the stance for each comment text given a user specified prompt.
-We choose both of these LLMs as candidates to test against our supervised approaches because of their ability to apply locally and reputable performance on zero-shot classification tasks.
-Both of these models received the same prompt and tasked which were developed by the research team to reflect the utility of classifying stance within our topic of interest.
+Textual features were derived from each comment and represented using two distinct approaches: unigram term frequency and term freuqency-inverse document frequency (TF-IDF).
+The unigram used a bag-of-words model to represent each word as a feature based on its frequency in comment.
+The TF-IDF transformation built upon these raw counts by accounting for term importance across the corpus.
+For both unigram and TF-IDF methods, the total number of text-derived features was 2,102.
+Combined with the three metadata features, each dataset contained a total of 2,105 features.
+Two datasets were constructed for classification: one combining the metadata with unigram features, and another with metadat and TF-IDF features.
+Each dataset was divded into 80% training data and 20% test data.
+All supervised learning models were implemented using Python 3, with scikit-learn and XGBoost as the primary machine learning (ML) techniques.
+Classification was conducted using a diverse set of algorithms, including Extra Trees Classifier, Random Forest Classifier, Logistic Regression, Ridge Classifier, K-Nearest Neightbors (KNN), Nearest Centroid, Multi-layer Perceptron Classifier, Bernoulli Naive Bayes, Multino- mial Naive Bayes, Linear Support Vector Classifier, Decision Tree Classifier, Extra Tree Classifier, and the XGBoost Classifier.
+
+All models were trained using default hyperparameter confiurations.
+The number of neighbors for KNN model was set to three, and the mtry parameter for Random Forrest was fixed at two, reflecting the relatively small number of metadata features in those models.
+All experiments were conducted on a personal computer without the use of a GPU
+
+In addition to traditional supervised models, we employed two instruction-tuned LLMs to perform zero- shot classification: Gemma 3.12B, developed by Google and based on the Gemini framework, and LLaMA 3.2B, developed by Meta AI.
+Gemma was deployed using the Great Lakes High-Performance Computing (HPC) cluster, while LLaMA was deployed locally on a GPU-enabled personal workstation using the rollama r pacakge.
+These models were selected for their strong zero-shot classification capabilities and ability to be run locally or on cluster environments without reliance on commercial APIs.
 
 |  |  |
-|----------------|--------------------------------------------------------|
+|------------------|------------------------------------------------------|
 | **Prompt**: | "Is this comment in 'favor', 'neutral', or 'oppose' the reduction in federal workforce? Provide one word answer only! |
@@
 
-We evaluate model performance using the F1-score which is a harmonic mean balance between precision and recall.
-This metric considers both the ability to correctly identify positive instances, known as recall, and the ability to avoid incorrectly labeling negative instances as positive (i.e., precision).
-A high F1-score indicates a model with well balanced recall and precision that both minimize false negativesand false positives.
-The second performance metric we used is recall, as this determines how many of the actual positive cases the model can correctly identify.
-Recall can be prone to incorrectly labeling negative cases as positive, suggesting more false positives, which is why we intereggoate on two performance metrics in this study.
+The model performance was evaluated by the F1-score and recall.
+The F1-score, a harmonic mean of precision and recall, serves as a balanced indicator of a model’s ability to correctly identify relevant instances while minimizing both false positives and false negatives.
+Recall was also independently assessed to evaluate the proportion of true postive cases accurately identified by each model.
+While a high recall may increase the risk of false positives, its combination with the F1-score allows a more robust evaluation of model performance, especially for addressing the challenges inherent in imbalanced classification tasks
 

### 2025-04-09 code/ml_llm/R/assign_3.tex
2nd round of assing 3 paper

@@
 
-\date{April 8, 2025}
+\date{April 9, 2025}
 \title{\bf DOGE's Downsizing, Can AI Read the Reddit Room?}
@@
 labeled comments (28\% favor, 18\% neutral, 54\% oppose) using
-supervised and unsupervised Large Language Models. Supervised models
-showed moderate success, particularly with ``oppose'' comments, but
-struggled with ``favor'' and ``neutral'' stances. Similarly, LLMs best
-identified ``oppose'' sentiment but exhibited low precision for
+supervised and unsupervised Large Language Models (LLM). Supervised
+models showed moderate success, particularly with ``oppose'' comments,
+but struggled with ``favor'' and ``neutral'' stances. Similarly, LLMs
+best identified ``oppose'' sentiment but exhibited low precision for
 ``favor'' and ``neutral.'' These findings highlight the challenges of
@@
 
-\section{Methods}\label{sec-meth}
+\section{Method}\label{sec-meth}
 
-\emph{Data}. We collected Reddit comments from subreddits related to the
-topic of interest in early March of 2024. This resulted in 12,553
-comments which we preprocessed by removing web-URLs, replace special
-characters (i.e., replaced ``@'' with ``at''), replaced numeric values
-with their spelling, and confirmed the absence of duplicate comments. We
-then randomly selected 400 comments (without replacement) and assigned
-them to four graduate students for coding, categorizing each comment as
-favoring, opposing, or neutral towards DOGE's approach to federal
-workforce reductions. Table 1 presents the breakdown in percent of our
-the comments we labelled and later use to train and evaluate our machine
-learning models. A review of the comments revealed more negative
-opinionated statements and reactions.
+We collected a total of 12,553 Reddit comments in early March 2024 from
+subreddits relevant to the topic of interest. These comments were
+retrieved using keyword-based queries designed to capture posts of
+discussions that would reflect users' stances on the federal workforce
+reduction by DOGE. To prepare the data for analysis, a comprehensive
+preprocessing pipline were conducted in Pytho 3. This process involved
+removing HTML tags and web-URLs, stripping special characters and
+tagging artifacts such as ``@'', and replacing emojis with textual
+descriptions. Also, it entailed eliminating punctuations and converting
+numerical values into their spelled-out forms. The text was standardized
+to lowercase, lemmatized using the SpaCy library, and further refined by
+removing stopwords per the Natural Language Toolkit (NLTK) lists.
+Spelling corrections were performed to improve textual coherence, while
+Duplicate comments were identified and removed to maintain data
+integrity.
+
+From this cleaned dataset, 400 uniqe comments without replacement were
+randomly sampled for manual annotation. Four graudate students
+independently coded and labeled each comment with one of three possible
+stances:favor, opopose, or neutral toward DOGE's approach to federal
+workforce reductions. As shown in Table 1, there were 28\% favor, 18\%
+neutral, and 54\% oppose. These labeled comments were subsequently used
+for training and evaluating both supervised and unsupervised
+classification models.
 
@@
 
-We built two supervised machine learning models--K-nearest neighbor and
-random forest--to classify Reddit comments concerning stance on the
-current reduction in federal workforce into favor, oppose, or neutral.
-For predictors we used the Reddit score, up-votes, and down-votes each
-comment received at the time of the collection. Additionally, we used
-the keyword that was used to scrape these data along with the subreddit
-where the comment was posted. \textbf{DISCUSS ADDITIONAL FEATURE
-ENGINERRING SUCH AS TEXT EDITING THAT WENT INTO THE MODEL.} For the KNN
-model, we set the number of neighbors hyperparameter to three, and for
-the random forest, mtry was kept at a constant two as we did not have
-many features in these models. We took an 80/20 split for our
-training-testing sets that we used to train each model and evaluate.
+The feature set used in model training and evluation consisted of two
+primary categories: metadata features and textual features. Metadata
+features included the Reddit comment's score, the subreddit in which it
+appeared in, and the search term that retrieved it. As the variables for
+score and upvotes were perfectly collinear in this dataset, only the
+score was retained. To ensure all values were non-negative, the score
+was adjusted by subtracting the dataset's minimum value from each score.
+The categorical variables, subreddit and search term, were numerically
+encoded using scikit-learn's label encoder.
 
-In addition to our supervised machine learning models, we also applied
-to our comments two LLMs, gemma 3.12 and llama 3.2. 3B. Gemma, was
-developed by Google and is based on Gemini, is able to generate text
-output using instruction-tuned prompts from the user, such as providing
-answers on a user specified task reviewing text. We deployed gemma on a
-higher performance computing cluster
-(\href{https://its.umich.edu/advanced-research-computing/}{Great Lakes
-HCP}) and processed text from Reddit comments on a GPU. We were also
-interested in deploying other lightweight LLMs locally on a machine with
-a dedicated-GPU and found llama, developed by Meta AI, to be an
-excellent candidate. Llama excels at text classification which is how we
-used it to classify the stance for each comment text given a user
-specified prompt. We choose both of these LLMs as candidates to test
-against our supervised approaches because of their ability to apply
-locally and reputable performance on zero-shot classification tasks.
-Both of these models received the same prompt and tasked which were
-developed by the research team to reflect the utility of classifying
-stance within our topic of interest.
+Textual features were derived from each comment and represented using
+two distinct approaches: unigram term frequency and term
+freuqency-inverse document frequency (TF-IDF). The unigram used a
+bag-of-words model to represent each word as a feature based on its
+frequency in comment. The TF-IDF transformation built upon these raw
+counts by accounting for term importance across the corpus. For both
+unigram and TF-IDF methods, the total number of text-derived features
+was 2,102. Combined with the three metadata features, each dataset
+contained a total of 2,105 features. Two datasets were constructed for
+classification: one combining the metadata with unigram features, and
+another with metadat and TF-IDF features. Each dataset was divded into
+80\% training data and 20\% test data. All supervised learning models
+were implemented using Python 3, with scikit-learn and XGBoost as the
+primary machine learning (ML) techniques. Classification was conducted
+using a diverse set of algorithms, including Extra Trees Classifier,
+Random Forest Classifier, Logistic Regression, Ridge Classifier,
+K-Nearest Neightbors (KNN), Nearest Centroid, Multi-layer Perceptron
+Classifier, Bernoulli Naive Bayes, Multino- mial Naive Bayes, Linear
+Support Vector Classifier, Decision Tree Classifier, Extra Tree
+Classifier, and the XGBoost Classifier.
+
+All models were trained using default hyperparameter confiurations. The
+number of neighbors for KNN model was set to three, and the mtry
+parameter for Random Forrest was fixed at two, reflecting the relatively
+small number of metadata features in those models. All experiments were
+conducted on a personal computer without the use of a GPU
+
+In addition to traditional supervised models, we employed two
+instruction-tuned LLMs to perform zero- shot classification: Gemma
+3.12B, developed by Google and based on the Gemini framework, and LLaMA
+3.2B, developed by Meta AI. Gemma was deployed using the Great Lakes
+High-Performance Computing (HPC) cluster, while LLaMA was deployed
+locally on a GPU-enabled personal workstation using the rollama r
+pacakge. These models were selected for their strong zero-shot
+classification capabilities and ability to be run locally or on cluster
+environments without reliance on commercial APIs.
 
 \begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.2222}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.7778}}@{}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.2500}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.7500}}@{}}
 \toprule\noalign{}
@@
 
-We evaluate model performance using the F1-score which is a harmonic
-mean balance between precision and recall. This metric considers both
-the ability to correctly identify positive instances, known as recall,
-and the ability to avoid incorrectly labeling negative instances as
-positive (i.e., precision). A high F1-score indicates a model with well
-balanced recall and precision that both minimize false negativesand
-false positives. The second performance metric we used is recall, as
-this determines how many of the actual positive cases the model can
-correctly identify. Recall can be prone to incorrectly labeling negative
-cases as positive, suggesting more false positives, which is why we
-intereggoate on two performance metrics in this study.
+The model performance was evaluated by the F1-score and recall. The
+F1-score, a harmonic mean of precision and recall, serves as a balanced
+indicator of a model's ability to correctly identify relevant instances
+while minimizing both false positives and false negatives. Recall was
+also independently assessed to evaluate the proportion of true postive
+cases accurately identified by each model. While a high recall may
+increase the risk of false positives, its combination with the F1-score
+allows a more robust evaluation of model performance, especially for
+addressing the challenges inherent in imbalanced classification tasks
 

### 2025-04-09 code/ml_llm/R/assign_3.qmd
3rd draft of assing 3

@@
 abstract: |
-  We investigate public sentiment on Reddit regarding the Department of Government Efficiency's federal workforce reduction by classifying 400 labeled comments (28% favor, 18% neutral, 54% oppose) using supervised and unsupervised Large Language Models (LLM).
-Supervised models showed moderate success, particularly with "oppose" comments, but struggled with "favor" and "neutral" stances.
-Similarly, LLMs best identified "oppose" sentiment but exhibited low precision for "favor" and "neutral." These findings highlight the challenges of accurately gauging nuanced public opinion on government policy changes using automated methods on social media data.
+  We investigated public sentiment on Reddit regarding the Department of Government Efficiency's federal workforce reduction by classifying 400 labeled comments (28% favor, 18% neutral, 54% oppose) using supervised and unsupervised Large Language Models (LLMs).
+It turned out that supervised models showed low to moderate success, particularly with "oppose" comments, but struggled with "favor" and "neutral" stances.
+Similarly, LLMs best intent identified "oppose" sentiment but exhibited low precision for "favor" and "neutral." These findings highlight the challenges of accurately gauging nuanced public opinion on government policy changes through automated methods on social media data.
 
-keywords:
-  - Reddit
-  - Federal Government
-  - DOGE
 editor: 
@@
 library(tidytext)
+library(kableExtra)
 library(knitr)
@@
 This action has generated significant apprehension among federal workers in regards to mental health and job security.
-To understand the impact of DOGE's actions on federal worker perceptions of job security, we labeled 400 Reddit comments on topics related to the current reduction in *federal* workforce by DOGE as whether the author favored, opposed, or had a neutral stance.
+To understand the impact of DOGE's actions on federal worker perceptions of job security, we labeled 400 Reddit comments on topics related to the current reduction in federal workforce by DOGE as whether the author favored, opposed, or had a neutral stance.
 We use these labels to build supervised learning models to predict stance.
-Additionally, we employ unsupervised large language models (LLM) to detect the stance of these Reddit comments from text, to further explore appropriate models for this current topic.
+Additionally, we employ unsupervised large language models (LLMs) to detect the stance of these Reddit comments from text, to further explore appropriate models for this current topic.
 
@@
 These comments were retrieved using keyword-based queries designed to capture posts of discussions that would reflect users’ stances on the federal workforce reduction by DOGE.
-To prepare the data for analysis, a comprehensive preprocessing pipline were conducted in Pytho 3.
+To prepare the data for analysis, a comprehensive preprocessing pipeline was conducted in Python 3.
 This process involved removing HTML tags and web-URLs, stripping special characters and tagging artifacts such as “\@”, and replacing emojis with textual descriptions.
@@
 The text was standardized to lowercase, lemmatized using the SpaCy library, and further refined by removing stopwords per the Natural Language Toolkit (NLTK) lists.
-Spelling corrections were performed to improve textual coherence, while Duplicate comments were identified and removed to maintain data integrity.
+Spelling corrections were performed to improve textual coherence, while duplicate comments were identified and removed to maintain data integrity.
 
-From this cleaned dataset, 400 uniqe comments without replacement were randomly sampled for manual annotation.
-Four graudate students independently coded and labeled each comment with one of three possible stances:favor, opopose, or neutral toward DOGE’s approach to federal workforce reductions.
+From this cleaned dataset, 400 unique comments without replacement were randomly sampled for manual annotation.
+Four graduate students independently coded and labeled each comment with one of three possible stances: favor, oppose, or neutral toward DOGE’s approach to federal workforce reductions.
 As shown in Table 1, there were 28% favor, 18% neutral, and 54% oppose.
@@
   mutate(Percent = n/sum(n),
-         Percent = round(Percent* 100)) |> 
+         Percent = scales::percent(Percent)) |> 
   select(outcome, Percent) |> 
-  kable(caption="Distribution of labeled Reddit comment data.")
+  kable(caption="Distribution of Labeled Reddit Comment Data",
+        col.names = c("Stance", "%"),  align = "c", booktabs = TRUE) 
 ```
 
-The feature set used in model training and evluation consisted of two primary categories: metadata features and textual features.
+The feature set used in model training and evaluation consisted of two primary categories: metadata features and textual features.
 Metadata features included the Reddit comment’s score, the subreddit in which it appeared in, and the search term that retrieved it.
@@
 
-Textual features were derived from each comment and represented using two distinct approaches: unigram term frequency and term freuqency-inverse document frequency (TF-IDF).
+Textual features were derived from each comment and represented using two distinct approaches: unigram term frequency and term frequency-inverse document frequency (TF-IDF).
 The unigram used a bag-of-words model to represent each word as a feature based on its frequency in comment.
@@
 Combined with the three metadata features, each dataset contained a total of 2,105 features.
-Two datasets were constructed for classification: one combining the metadata with unigram features, and another with metadat and TF-IDF features.
-Each dataset was divded into 80% training data and 20% test data.
+Two datasets were constructed for classification: one combining the metadata with unigram features, and another with metadata and TF-IDF features.
+Each dataset was divided into 80% training data and 20% test data.
 All supervised learning models were implemented using Python 3, with scikit-learn and XGBoost as the primary machine learning (ML) techniques.
@@
 
-All models were trained using default hyperparameter confiurations.
+All models were trained using default hyperparameter configurations.
 The number of neighbors for KNN model was set to three, and the mtry parameter for Random Forrest was fixed at two, reflecting the relatively small number of metadata features in those models.
@@
 In addition to traditional supervised models, we employed two instruction-tuned LLMs to perform zero- shot classification: Gemma 3.12B, developed by Google and based on the Gemini framework, and LLaMA 3.2B, developed by Meta AI.
-Gemma was deployed using the Great Lakes High-Performance Computing (HPC) cluster, while LLaMA was deployed locally on a GPU-enabled personal workstation using the rollama r pacakge.
+Gemma was deployed using the Great Lakes High-Performance Computing (HPC) cluster, while LLaMA was deployed locally on a GPU-enabled personal workstation using the rollama r-pacakge.
 These models were selected for their strong zero-shot classification capabilities and ability to be run locally or on cluster environments without reliance on commercial APIs.
+Both models were given the same prompt and tasks, which were developed by the research team to assess the effectiveness of classifying stance within our topic of interest (see Table 2).
+
+\
+
+Table 2.
+Example of Prompt and Task for LLMs
 
 |  |  |
-|------------------|------------------------------------------------------|
+|--------------------|----------------------------------------------------|
 | **Prompt**: | "Is this comment in 'favor', 'neutral', or 'oppose' the reduction in federal workforce? Provide one word answer only! |
-| **Task**: | "You have assumed the role of a stakeholder that is presented with a reddit comment from a likely federal worker related to the current policies on reducing the federal workforce.
-Please determine the author's stance on this topic, and only provide the answer." |
+| **Task**: | "You have assumed the role of a stakeholder that is presented with a Reddit comment from a likely federal worker related to the current policies on reducing the federal workforce.
+Please determine the author's stance on this topic, and provide the answer only." |
 
@@
 The F1-score, a harmonic mean of precision and recall, serves as a balanced indicator of a model’s ability to correctly identify relevant instances while minimizing both false positives and false negatives.
-Recall was also independently assessed to evaluate the proportion of true postive cases accurately identified by each model.
+Recall was also independently assessed to evaluate the proportion of true positive cases accurately identified by each model.
 While a high recall may increase the risk of false positives, its combination with the F1-score allows a more robust evaluation of model performance, especially for addressing the challenges inherent in imbalanced classification tasks
@@
 
-Our machine learning models reveal a mix of performance results in classifying the stance of Reddit comment into favor, neutral, oppose.
-Both models exhibit low recall and F1-scores for the "favor" stance (see Figure 1), yet the random forest model (recall .26: f1-score .28) slightly outperforms KNN (recall .16: f1-score .19).
-The "neutral" class presented a significant challenge for the random forest with very low scores (recall .05: f1-score .10), while KNN exhibited slightly better performance (recall .21: f1-score .21).
+Our machine learning models revealed a mix of performance results in classifying the stance of Reddit comment into "favor", "neutral", and "oppose." Both models exhibited low recall and F1-scores for the "favor" stance (see Figure 1), and the random forest model (recall .26: F1-score .28) slightly outperformed KNN (recall .16: F1-score .19).
+The "neutral" class presented a significant challenge for the random forest with very low scores (recall .05: F1-score .10), while KNN exhibited slightly better performance (recall .21: F1-score .21).
 Both models showed the strongest performance in identifying comments expressing opposition.
-The random forest correctly identified 74 percent of all the actual Reddit comments expressing opposition compared to KNN at 64 percent, meaning that KNN missed a larger proportion of true "oppose" comments.
-The f1-scores were similar for both models at 60 percent, this implies that KNN may have a slightly higher precision score given that it had a lower recall score than the random forest model.
-This implies that when KNN predicts comments for the "oppose" class, it is as likely as the random forest to be correct.
+The random forest correctly identified 74% of all the actual Reddit comments expressing opposition compared to KNN at 64%, suggesting that KNN missed a larger proportion of true "oppose" comments.
+Both models obtained similar F!-
+scores of 60%, suggesting that KNN may have slightly higher precision, given its lower recall compared to the random forest model.
+This implies that when KNN predicts comments for the "oppose" class, its accuracy is comparable to that of the random forest model.
 
@@
   labs(
-    title = "Figure 1. Recall and precision scores for random forest
-    and KNN models.",
+    title = "Figure 1. Recall and Precision Scores for Random Forest
+    and KNN Models",
     x = "Models",
@@
 
-The LLMs, showed poor performance in classifying the "favor" stance, with very low f1-scores (llama .07: gemma .02) despite moderate recall (llama .29: gemma .33), indicating low precision (see Figure 2).
-For the "neutral" class, both models showed modest results, with llama achieving a slightly better F1-score (.23) compared to gemma (0.18), although gemma had a higher recall (.50 vs .25), again suggesting lower precision for gemma.
-Similar to the supervised models, both LLMs performed best in classifying the "oppose" stance, with relatively high and similar F1-scores (llama .67: gemma .70) and comparable recall (llama .56: gemma .56), suggesting a better balance between precision and recall for this category.
-Both models correctly identify 67 to 70 percent of all the actual Reddit comments expressing opposition.
-Overall, both LLMs struggled with the "favor" and "neutral" classes but demonstrated a stronger ability to identify opposing comments.\
+The LLMs, showed poor performance in classifying the "favor" stance, with very low F1-scores (Llama .07: Gemma .02) despite moderate recall (Llama .29: Gemma .33), indicating low precision (see Figure 2).
+For the "neutral" class, both models showed modest results, with Llama achieving a slightly better F1-score (.23) compared to Gemma (.18), although Gemma had a higher recall (Gemma .50: Llama .25), again suggesting lower precision for Gemma.
+Similar to the supervised models, both LLMs performed best in classifying the "oppose" stance, with relatively high and similar F1-scores (Llama .67: Gemma .70) and comparable recall (Llama .56: Gemma .56), suggesting a better balance between precision and recall for this category.
+Both models correctly identified 67% to 70% of all the actual Reddit comments expressing opposition.
+Overall, both LLMs struggled with the "favor" and "neutral" stance but demonstrated a stronger ability to identify opposing comments.\
 
@@
   labs(
-    title = "Figure 2. Recall and precision scores for LLMs.",
+    title = "Figure 2. Recall and Precision Scores for LLMs",
     x = "Models",
@@
 
-Gemma and llama demonstrated only fair agreement in stance classification (Cohen's Kappa = .24).
-The contingency table, Table 2 below, reveals highest agreement for "oppose" (.80), indicating some consistency in identifying a strong negative stance.
-However, agreement was substantially lower for "neutral" (.03) and "favor" (.01), highlighting divergent interpretations of more nuanced language.
-Off-diagonal values further illustrate these discrepancies, suggesting fundamental differences in how the models process ambiguous cues and establish classification boundaries, particularly for less extreme stances.
+Gemma and Llama demonstrated only fair agreement in stance classification (Cohen's Kappa = .24).
+The contingency table ( see Table 3) reveals the highest agreement for "oppose" (.80), indicating some consistency in identifying a strong negative stance.
+However, agreement was substantially lower for "neutral" (.03) and "favor" (.01), highlighting the divergent interpretations of more nuanced language.
+The off-diagonal values further illustrates these discrepancies, suggesting the fundamental differences in how the models process ambiguous cues and establish classification boundaries, particularly for less extreme stances.
 
@@
 cm_results$cm_tbl |> 
-    kable(caption=str_c("Aggreement between LLMs, Cohens Kappa, ", 
+    kable(caption=str_c("Aggreement Between LLMs, Cohen's Kappa, ", 
                         round(coh_kappa, 2)))
@@
 
-We explored public sentiment on Reddit regarding the DOGE federal workforce reduction using supervised learning (KNN, Random Forest) and unsupervised LLMs ( gemma 3.12b and Llama 3.2 3B) for stance classification.
-Our supervised learning models achieved moderate success in this classification task, with the strongest performance in identifying opposing viewpoints, which were also the most prevalent in our labeled data.
-Moreover, both models struggled with the "favor" and "neutral" stances, suggesting limitations in our initial features to capture these nuances.
+Public sentiment on Reddit were explored in terms of the DOGE federal workforce reduction through supervised learning (KNN, Random Forest) and unsupervised LLMs ( Gemma 3.12b and Llama 3.2 3B) for stance classifications.
+Our supervised learning models overall achieved low to moderate success in this classification task, with the strongest performance in identifying opposing viewpoints, which were also the most prevalent in our labeled data.
+Moreover, both models struggled with the "favor" and "neutral" stances, suggesting limitations in our features to capture these nuances.
 Our unsupervised learning models also showed the best ability to classify "oppose" comments, yet exhibited significant challenges with the "favor" and "neutral" categories, particularly demonstrating low precision.
 
-This study had limitations such as the small size of our labelled dataset of 400 Reddit, imbalance in the stance categories, and few features in the supervised approach.
-The zero-shot capabilities of the LLMs are suitable for topic exploration but may require fine-tuning for optimal performance on this specific domain, particularly with nuance language used in "favor" comments.
-Future research should continue to understand federal worker perceptions and improve stance classification by expanding labeled dataset and incorporate more contextual text rather than single comment text.
+This study had limitations such as the small size of our labelled dataset of 400 Reddit comments, the imbalance in the stance categories, and few features in the supervised approach.
+The zero-shot capabilities of the LLMs are suitable for topic exploration but may require fine-tuning for optimal performance on this specific domain, particularly with nuance language used in "favor" stance.
+To deepen the understanding of federal worker perceptions and enhance stance classification, future research may further expand the labeled datasets and incorporate more contextual text, rather than relying on single comments.
 Fine tuning LLMs on a larger corpus with relevant comments could render more accuracy in the classification task.

### 2025-04-09 code/ml_llm/R/assign_3.tex
3rd draft of assing 3

@@
 \addtolength{\topmargin}{-1in}%
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
 \makeatletter
@@
   pdfauthor={Kevin Linares; Felix Baez-Santiago; Aria Lu; Gloria Zhou},
-  pdfkeywords={Reddit, Federal Government, DOGE},
   colorlinks=true,
@@
 \begin{abstract}
-We investigate public sentiment on Reddit regarding the Department of
+We investigated public sentiment on Reddit regarding the Department of
 Government Efficiency's federal workforce reduction by classifying 400
 labeled comments (28\% favor, 18\% neutral, 54\% oppose) using
-supervised and unsupervised Large Language Models (LLM). Supervised
-models showed moderate success, particularly with ``oppose'' comments,
-but struggled with ``favor'' and ``neutral'' stances. Similarly, LLMs
-best identified ``oppose'' sentiment but exhibited low precision for
-``favor'' and ``neutral.'' These findings highlight the challenges of
-accurately gauging nuanced public opinion on government policy changes
-using automated methods on social media data.
+supervised and unsupervised Large Language Models (LLMs). It turned out
+that supervised models showed low to moderate success, particularly with
+``oppose'' comments, but struggled with ``favor'' and ``neutral''
+stances. Similarly, LLMs best intent identified ``oppose'' sentiment but
+exhibited low precision for ``favor'' and ``neutral.'' These findings
+highlight the challenges of accurately gauging nuanced public opinion on
+government policy changes through automated methods on social media
+data.
 \end{abstract}
-
-\noindent%
-{\it Keywords:} Reddit, Federal Government, DOGE
-\vfill
 
@@
 perceptions of job security, we labeled 400 Reddit comments on topics
-related to the current reduction in \emph{federal} workforce by DOGE as
-whether the author favored, opposed, or had a neutral stance. We use
-these labels to build supervised learning models to predict stance.
-Additionally, we employ unsupervised large language models (LLM) to
+related to the current reduction in federal workforce by DOGE as whether
+the author favored, opposed, or had a neutral stance. We use these
+labels to build supervised learning models to predict stance.
+Additionally, we employ unsupervised large language models (LLMs) to
 detect the stance of these Reddit comments from text, to further explore
@@
 reduction by DOGE. To prepare the data for analysis, a comprehensive
-preprocessing pipline were conducted in Pytho 3. This process involved
+preprocessing pipeline was conducted in Python 3. This process involved
 removing HTML tags and web-URLs, stripping special characters and
@@
 Spelling corrections were performed to improve textual coherence, while
-Duplicate comments were identified and removed to maintain data
+duplicate comments were identified and removed to maintain data
 integrity.
 
-From this cleaned dataset, 400 uniqe comments without replacement were
-randomly sampled for manual annotation. Four graudate students
+From this cleaned dataset, 400 unique comments without replacement were
+randomly sampled for manual annotation. Four graduate students
 independently coded and labeled each comment with one of three possible
-stances:favor, opopose, or neutral toward DOGE's approach to federal
+stances: favor, oppose, or neutral toward DOGE's approach to federal
 workforce reductions. As shown in Table 1, there were 28\% favor, 18\%
@@
 
-\begin{longtable}[]{@{}lr@{}}
-\caption{Distribution of labeled Reddit comment data.}\tabularnewline
+\begin{longtable}[]{@{}cc@{}}
+\caption{Distribution of Labeled Reddit Comment Data}\tabularnewline
 \toprule\noalign{}
-outcome & Percent \\
+Stance & \% \\
 \midrule\noalign{}
@@
 \toprule\noalign{}
-outcome & Percent \\
+Stance & \% \\
 \midrule\noalign{}
@@
 \endlastfoot
-favor & 28 \\
-neutral & 18 \\
-oppose & 54 \\
+favor & 27.5\% \\
+neutral & 18.2\% \\
+oppose & 54.2\% \\
 \end{longtable}
 
-The feature set used in model training and evluation consisted of two
+The feature set used in model training and evaluation consisted of two
 primary categories: metadata features and textual features. Metadata
@@
 two distinct approaches: unigram term frequency and term
-freuqency-inverse document frequency (TF-IDF). The unigram used a
+frequency-inverse document frequency (TF-IDF). The unigram used a
 bag-of-words model to represent each word as a feature based on its
@@
 classification: one combining the metadata with unigram features, and
-another with metadat and TF-IDF features. Each dataset was divded into
+another with metadata and TF-IDF features. Each dataset was divided into
 80\% training data and 20\% test data. All supervised learning models
@@
 
-All models were trained using default hyperparameter confiurations. The
+All models were trained using default hyperparameter configurations. The
 number of neighbors for KNN model was set to three, and the mtry
@@
 High-Performance Computing (HPC) cluster, while LLaMA was deployed
-locally on a GPU-enabled personal workstation using the rollama r
-pacakge. These models were selected for their strong zero-shot
+locally on a GPU-enabled personal workstation using the rollama
+r-pacakge. These models were selected for their strong zero-shot
 classification capabilities and ability to be run locally or on cluster
-environments without reliance on commercial APIs.
+environments without reliance on commercial APIs. Both models were given
+the same prompt and tasks, which were developed by the research team to
+assess the effectiveness of classifying stance within our topic of
+interest (see Table 2).
+
+\hfill\break
+
+Table 2. Example of Prompt and Task for LLMs
 
 \begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.2500}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.7500}}@{}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.2778}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.7222}}@{}}
 \toprule\noalign{}
@@
 \textbf{Task}: & ``You have assumed the role of a stakeholder that is
-presented with a reddit comment from a likely federal worker related to
+presented with a Reddit comment from a likely federal worker related to
 the current policies on reducing the federal workforce. Please determine
-the author's stance on this topic, and only provide the answer.'' \\
+the author's stance on this topic, and provide the answer only.'' \\
 \end{longtable}
@@
 while minimizing both false positives and false negatives. Recall was
-also independently assessed to evaluate the proportion of true postive
+also independently assessed to evaluate the proportion of true positive
 cases accurately identified by each model. While a high recall may
@@
 
-Our machine learning models reveal a mix of performance results in
-classifying the stance of Reddit comment into favor, neutral, oppose.
-Both models exhibit low recall and F1-scores for the ``favor'' stance
-(see Figure 1), yet the random forest model (recall .26: f1-score .28)
-slightly outperforms KNN (recall .16: f1-score .19). The ``neutral''
-class presented a significant challenge for the random forest with very
-low scores (recall .05: f1-score .10), while KNN exhibited slightly
-better performance (recall .21: f1-score .21). Both models showed the
-strongest performance in identifying comments expressing opposition. The
-random forest correctly identified 74 percent of all the actual Reddit
-comments expressing opposition compared to KNN at 64 percent, meaning
-that KNN missed a larger proportion of true ``oppose'' comments. The
-f1-scores were similar for both models at 60 percent, this implies that
-KNN may have a slightly higher precision score given that it had a lower
-recall score than the random forest model. This implies that when KNN
-predicts comments for the ``oppose'' class, it is as likely as the
-random forest to be correct.
+Our machine learning models revealed a mix of performance results in
+classifying the stance of Reddit comment into ``favor'', ``neutral'',
+and ``oppose.'' Both models exhibited low recall and F1-scores for the
+``favor'' stance (see Figure 1), and the random forest model (recall
+.26: F1-score .28) slightly outperformed KNN (recall .16: F1-score .19).
+The ``neutral'' class presented a significant challenge for the random
+forest with very low scores (recall .05: F1-score .10), while KNN
+exhibited slightly better performance (recall .21: F1-score .21). Both
+models showed the strongest performance in identifying comments
+expressing opposition. The random forest correctly identified 74\% of
+all the actual Reddit comments expressing opposition compared to KNN at
+64\%, suggesting that KNN missed a larger proportion of true ``oppose''
+comments. Both models obtained similar F!- scores of 60\%, suggesting
+that KNN may have slightly higher precision, given its lower recall
+compared to the random forest model. This implies that when KNN predicts
+comments for the ``oppose'' class, its accuracy is comparable to that of
+the random forest model.
 
@@
 The LLMs, showed poor performance in classifying the ``favor'' stance,
-with very low f1-scores (llama .07: gemma .02) despite moderate recall
-(llama .29: gemma .33), indicating low precision (see Figure 2). For the
-``neutral'' class, both models showed modest results, with llama
-achieving a slightly better F1-score (.23) compared to gemma (0.18),
-although gemma had a higher recall (.50 vs .25), again suggesting lower
-precision for gemma. Similar to the supervised models, both LLMs
-performed best in classifying the ``oppose'' stance, with relatively
-high and similar F1-scores (llama .67: gemma .70) and comparable recall
-(llama .56: gemma .56), suggesting a better balance between precision
-and recall for this category. Both models correctly identify 67 to 70
-percent of all the actual Reddit comments expressing opposition.
-Overall, both LLMs struggled with the ``favor'' and ``neutral'' classes
-but demonstrated a stronger ability to identify opposing comments.\\
+with very low F1-scores (Llama .07: Gemma .02) despite moderate recall
+(Llama .29: Gemma .33), indicating low precision (see Figure 2). For the
+``neutral'' class, both models showed modest results, with Llama
+achieving a slightly better F1-score (.23) compared to Gemma (.18),
+although Gemma had a higher recall (Gemma .50: Llama .25), again
+suggesting lower precision for Gemma. Similar to the supervised models,
+both LLMs performed best in classifying the ``oppose'' stance, with
+relatively high and similar F1-scores (Llama .67: Gemma .70) and
+comparable recall (Llama .56: Gemma .56), suggesting a better balance
+between precision and recall for this category. Both models correctly
+identified 67\% to 70\% of all the actual Reddit comments expressing
+opposition. Overall, both LLMs struggled with the ``favor'' and
+``neutral'' stance but demonstrated a stronger ability to identify
+opposing comments.\\
 
@@
 
-Gemma and llama demonstrated only fair agreement in stance
-classification (Cohen's Kappa = .24). The contingency table, Table 2
-below, reveals highest agreement for ``oppose'' (.80), indicating some
+Gemma and Llama demonstrated only fair agreement in stance
+classification (Cohen's Kappa = .24). The contingency table ( see Table
+3) reveals the highest agreement for ``oppose'' (.80), indicating some
 consistency in identifying a strong negative stance. However, agreement
 was substantially lower for ``neutral'' (.03) and ``favor'' (.01),
-highlighting divergent interpretations of more nuanced language.
-Off-diagonal values further illustrate these discrepancies, suggesting
-fundamental differences in how the models process ambiguous cues and
+highlighting the divergent interpretations of more nuanced language. The
+off-diagonal values further illustrates these discrepancies, suggesting
+the fundamental differences in how the models process ambiguous cues and
 establish classification boundaries, particularly for less extreme
@@
 \begin{longtable}[]{@{}lrrr@{}}
-\caption{Aggreement between LLMs, Cohens Kappa, 0.24}\tabularnewline
+\caption{Aggreement Between LLMs, Cohen's Kappa, 0.24}\tabularnewline
 \toprule\noalign{}
@@
 
-We explored public sentiment on Reddit regarding the DOGE federal
-workforce reduction using supervised learning (KNN, Random Forest) and
-unsupervised LLMs ( gemma 3.12b and Llama 3.2 3B) for stance
-classification. Our supervised learning models achieved moderate success
-in this classification task, with the strongest performance in
-identifying opposing viewpoints, which were also the most prevalent in
-our labeled data. Moreover, both models struggled with the ``favor'' and
-``neutral'' stances, suggesting limitations in our initial features to
-capture these nuances. Our unsupervised learning models also showed the
-best ability to classify ``oppose'' comments, yet exhibited significant
-challenges with the ``favor'' and ``neutral'' categories, particularly
-demonstrating low precision.
+Public sentiment on Reddit were explored in terms of the DOGE federal
+workforce reduction through supervised learning (KNN, Random Forest) and
+unsupervised LLMs ( Gemma 3.12b and Llama 3.2 3B) for stance
+classifications. Our supervised learning models overall achieved low to
+moderate success in this classification task, with the strongest
+performance in identifying opposing viewpoints, which were also the most
+prevalent in our labeled data. Moreover, both models struggled with the
+``favor'' and ``neutral'' stances, suggesting limitations in our
+features to capture these nuances. Our unsupervised learning models also
+showed the best ability to classify ``oppose'' comments, yet exhibited
+significant challenges with the ``favor'' and ``neutral'' categories,
+particularly demonstrating low precision.
 
 This study had limitations such as the small size of our labelled
-dataset of 400 Reddit, imbalance in the stance categories, and few
-features in the supervised approach. The zero-shot capabilities of the
-LLMs are suitable for topic exploration but may require fine-tuning for
-optimal performance on this specific domain, particularly with nuance
-language used in ``favor'' comments. Future research should continue to
-understand federal worker perceptions and improve stance classification
-by expanding labeled dataset and incorporate more contextual text rather
-than single comment text. Fine tuning LLMs on a larger corpus with
-relevant comments could render more accuracy in the classification task.
+dataset of 400 Reddit comments, the imbalance in the stance categories,
+and few features in the supervised approach. The zero-shot capabilities
+of the LLMs are suitable for topic exploration but may require
+fine-tuning for optimal performance on this specific domain,
+particularly with nuance language used in ``favor'' stance. To deepen
+the understanding of federal worker perceptions and enhance stance
+classification, future research may further expand the labeled datasets
+and incorporate more contextual text, rather than relying on single
+comments. Fine tuning LLMs on a larger corpus with relevant comments
+could render more accuracy in the classification task.
 

### 2025-04-09 code/ml_llm/R/assign_3.qmd
3rd draft of assing 3

@@
 
-\
-
 Table 2.
@@
 #| fig-width: 7
-#| fig-height: 6
+#| fig-height: 5
 #| 
@@
 ```
+
+\newpage
 
@@
 #| fig-width: 7
-#| fig-height: 6
+#| fig-height: 4.75
 #| 

### 2025-04-09 code/ml_llm/R/assign_3.qmd
Update assign_3.qmd

@@
 To understand the impact of DOGE's actions on federal worker perceptions of job security, we labeled 400 Reddit comments on topics related to the current reduction in federal workforce by DOGE as whether the author favored, opposed, or had a neutral stance.
-We use these labels to build supervised learning models to predict stance.
-Additionally, we employ unsupervised large language models (LLMs) to detect the stance of these Reddit comments from text, to further explore appropriate models for this current topic.
+We used these labels to build supervised learning models to predict stance.
+Additionally, we employed unsupervised large language models (LLMs) to detect the stance of these Reddit comments from text, to further explore appropriate models for this current topic.
 
@@
 Gemma and Llama demonstrated only fair agreement in stance classification (Cohen's Kappa = .24).
-The contingency table ( see Table 3) reveals the highest agreement for "oppose" (.80), indicating some consistency in identifying a strong negative stance.
-However, agreement was substantially lower for "neutral" (.03) and "favor" (.01), highlighting the divergent interpretations of more nuanced language.
+The contingency table ( see Table 2) reveals the highest agreement for "oppose" (.80), indicating some consistency in identifying a strong negative stance.
+However, the agreement was substantially lower for "neutral" (.03) and "favor" (.01), highlighting the divergent interpretations of more nuanced language.
 The off-diagonal values further illustrates these discrepancies, suggesting the fundamental differences in how the models process ambiguous cues and establish classification boundaries, particularly for less extreme stances.

### 2025-04-10 code/ml_llm/R/assign_3.qmd
3rd draft of assing 3

@@
   We investigated public sentiment on Reddit regarding the Department of Government Efficiency's federal workforce reduction by classifying 400 labeled comments (28% favor, 18% neutral, 54% oppose) using supervised and unsupervised Large Language Models (LLMs).
-It turned out that supervised models showed low to moderate success, particularly with "oppose" comments, but struggled with "favor" and "neutral" stances.
+It turned out that supervised models showed low-moderate success, particularly with "oppose" comments, but struggled with "favor" and "neutral" stances.
 Similarly, LLMs best intent identified "oppose" sentiment but exhibited low precision for "favor" and "neutral." These findings highlight the challenges of accurately gauging nuanced public opinion on government policy changes through automated methods on social media data.
@@
 This action has generated significant apprehension among federal workers in regards to mental health and job security.
-To understand the impact of DOGE's actions on federal worker perceptions of job security, we labeled 400 Reddit comments on topics related to the current reduction in federal workforce by DOGE as whether the author favored, opposed, or had a neutral stance.
+To understand the impact of DOGE's actions on federal worker perceptions of job security, we labeled 400 Reddit comments on topics related to the current reduction in workforce as whether the author favored, opposed, or had a neutral stance.
 We used these labels to build supervised learning models to predict stance.
@@
 
-We collected a total of 12,553 Reddit comments in early March 2024 from subreddits relevant to the topic of interest.
-These comments were retrieved using keyword-based queries designed to capture posts of discussions that would reflect users’ stances on the federal workforce reduction by DOGE.
+We collected 12,553 Reddit comments earlier this March from subreddits relevant to the topic of interest.
+These comments were retrieved using keyword-based queries designed to capture discussion posts reflecting users’ stances on the federal workforce reduction by DOGE.
 To prepare the data for analysis, a comprehensive preprocessing pipeline was conducted in Python 3.
@@
 
-All models were trained using default hyperparameter configurations.
+All models were trained on a local machine with only the CPU using default hyperparameter configurations.
 The number of neighbors for KNN model was set to three, and the mtry parameter for Random Forrest was fixed at two, reflecting the relatively small number of metadata features in those models.
-All experiments were conducted on a personal computer without the use of a GPU
 
-In addition to traditional supervised models, we employed two instruction-tuned LLMs to perform zero- shot classification: Gemma 3.12B, developed by Google and based on the Gemini framework, and LLaMA 3.2B, developed by Meta AI.
-Gemma was deployed using the Great Lakes High-Performance Computing (HPC) cluster, while LLaMA was deployed locally on a GPU-enabled personal workstation using the rollama r-pacakge.
+We also employed two LLMs to perform zero-shot classification: Gemma 3.12B, developed by Google and based on the Gemini framework, and LLaMA 3.2B, developed by Meta AI.
+Gemma was deployed using the Great Lakes High-Performance Computing (HPC) cluster, while LLaMA was deployed locally on a dedicated-GPU using the rollama r-package.
 These models were selected for their strong zero-shot classification capabilities and ability to be run locally or on cluster environments without reliance on commercial APIs.
-Both models were given the same prompt and tasks, which were developed by the research team to assess the effectiveness of classifying stance within our topic of interest (see Table 2).
+Both models were given the same prompt and tasks, which were developed by the research team to assess the effectiveness of classifying stance within our topic (see Table 2).
 
@@
 |  |  |
-|--------------------|----------------------------------------------------|
+|----------------------|--------------------------------------------------|
 | **Prompt**: | "Is this comment in 'favor', 'neutral', or 'oppose' the reduction in federal workforce? Provide one word answer only! |
@@
 #| fig-width: 7
-#| fig-height: 5
+#| fig-height: 5.5
 #| 
@@
 Gemma and Llama demonstrated only fair agreement in stance classification (Cohen's Kappa = .24).
-The contingency table ( see Table 2) reveals the highest agreement for "oppose" (.80), indicating some consistency in identifying a strong negative stance.
+The contingency table ( see Table 3) reveals the highest agreement for "oppose" (.80), indicating some consistency in identifying a strong negative stance.
 However, the agreement was substantially lower for "neutral" (.03) and "favor" (.01), highlighting the divergent interpretations of more nuanced language.
@@
 
-Public sentiment on Reddit were explored in terms of the DOGE federal workforce reduction through supervised learning (KNN, Random Forest) and unsupervised LLMs ( Gemma 3.12b and Llama 3.2 3B) for stance classifications.
-Our supervised learning models overall achieved low to moderate success in this classification task, with the strongest performance in identifying opposing viewpoints, which were also the most prevalent in our labeled data.
+We explored public sentiment of DOGE's federal workforce reduction through supervised learning (KNN, Random Forest) and unsupervised LLMs ( Gemma 3.12b and Llama 3.2 3B) for stance classifications.
+Our supervised learning models achieved low-moderate success in this classification task, with the strongest performance in identifying opposing viewpoints.
 Moreover, both models struggled with the "favor" and "neutral" stances, suggesting limitations in our features to capture these nuances.

### 2025-04-10 code/ml_llm/R/assign_3.tex
3rd draft of assing 3

@@
 
-\date{April 9, 2025}
+\date{April 10, 2025}
 \title{\bf DOGE's Downsizing, Can AI Read the Reddit Room?}
@@
 supervised and unsupervised Large Language Models (LLMs). It turned out
-that supervised models showed low to moderate success, particularly with
+that supervised models showed low-moderate success, particularly with
 ``oppose'' comments, but struggled with ``favor'' and ``neutral''
@@
 perceptions of job security, we labeled 400 Reddit comments on topics
-related to the current reduction in federal workforce by DOGE as whether
-the author favored, opposed, or had a neutral stance. We use these
-labels to build supervised learning models to predict stance.
-Additionally, we employ unsupervised large language models (LLMs) to
-detect the stance of these Reddit comments from text, to further explore
-appropriate models for this current topic.
+related to the current reduction in workforce as whether the author
+favored, opposed, or had a neutral stance. We used these labels to build
+supervised learning models to predict stance. Additionally, we employed
+unsupervised large language models (LLMs) to detect the stance of these
+Reddit comments from text, to further explore appropriate models for
+this current topic.
 
@@
 
-We collected a total of 12,553 Reddit comments in early March 2024 from
-subreddits relevant to the topic of interest. These comments were
-retrieved using keyword-based queries designed to capture posts of
-discussions that would reflect users' stances on the federal workforce
-reduction by DOGE. To prepare the data for analysis, a comprehensive
-preprocessing pipeline was conducted in Python 3. This process involved
-removing HTML tags and web-URLs, stripping special characters and
-tagging artifacts such as ``@'', and replacing emojis with textual
-descriptions. Also, it entailed eliminating punctuations and converting
-numerical values into their spelled-out forms. The text was standardized
-to lowercase, lemmatized using the SpaCy library, and further refined by
-removing stopwords per the Natural Language Toolkit (NLTK) lists.
-Spelling corrections were performed to improve textual coherence, while
-duplicate comments were identified and removed to maintain data
-integrity.
+We collected 12,553 Reddit comments earlier this March from subreddits
+relevant to the topic of interest. These comments were retrieved using
+keyword-based queries designed to capture discussion posts reflecting
+users' stances on the federal workforce reduction by DOGE. To prepare
+the data for analysis, a comprehensive preprocessing pipeline was
+conducted in Python 3. This process involved removing HTML tags and
+web-URLs, stripping special characters and tagging artifacts such as
+``@'', and replacing emojis with textual descriptions. Also, it entailed
+eliminating punctuations and converting numerical values into their
+spelled-out forms. The text was standardized to lowercase, lemmatized
+using the SpaCy library, and further refined by removing stopwords per
+the Natural Language Toolkit (NLTK) lists. Spelling corrections were
+performed to improve textual coherence, while duplicate comments were
+identified and removed to maintain data integrity.
 
@@
 
-All models were trained using default hyperparameter configurations. The
-number of neighbors for KNN model was set to three, and the mtry
-parameter for Random Forrest was fixed at two, reflecting the relatively
-small number of metadata features in those models. All experiments were
-conducted on a personal computer without the use of a GPU
+All models were trained on a local machine with only the CPU using
+default hyperparameter configurations. The number of neighbors for KNN
+model was set to three, and the mtry parameter for Random Forrest was
+fixed at two, reflecting the relatively small number of metadata
+features in those models.
 
-In addition to traditional supervised models, we employed two
-instruction-tuned LLMs to perform zero- shot classification: Gemma
+We also employed two LLMs to perform zero-shot classification: Gemma
 3.12B, developed by Google and based on the Gemini framework, and LLaMA
@@
 High-Performance Computing (HPC) cluster, while LLaMA was deployed
-locally on a GPU-enabled personal workstation using the rollama
-r-pacakge. These models were selected for their strong zero-shot
-classification capabilities and ability to be run locally or on cluster
-environments without reliance on commercial APIs. Both models were given
-the same prompt and tasks, which were developed by the research team to
-assess the effectiveness of classifying stance within our topic of
-interest (see Table 2).
-
-\hfill\break
+locally on a dedicated-GPU using the rollama r-package. These models
+were selected for their strong zero-shot classification capabilities and
+ability to be run locally or on cluster environments without reliance on
+commercial APIs. Both models were given the same prompt and tasks, which
+were developed by the research team to assess the effectiveness of
+classifying stance within our topic (see Table 2).
 
@@
 \begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.2778}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.7222}}@{}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.3056}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.6944}}@{}}
 \toprule\noalign{}
@@
 
+\newpage
+
 The LLMs, showed poor performance in classifying the ``favor'' stance,
@@
 3) reveals the highest agreement for ``oppose'' (.80), indicating some
-consistency in identifying a strong negative stance. However, agreement
-was substantially lower for ``neutral'' (.03) and ``favor'' (.01),
-highlighting the divergent interpretations of more nuanced language. The
-off-diagonal values further illustrates these discrepancies, suggesting
-the fundamental differences in how the models process ambiguous cues and
-establish classification boundaries, particularly for less extreme
-stances.
+consistency in identifying a strong negative stance. However, the
+agreement was substantially lower for ``neutral'' (.03) and ``favor''
+(.01), highlighting the divergent interpretations of more nuanced
+language. The off-diagonal values further illustrates these
+discrepancies, suggesting the fundamental differences in how the models
+process ambiguous cues and establish classification boundaries,
+particularly for less extreme stances.
 
@@
 
-Public sentiment on Reddit were explored in terms of the DOGE federal
-workforce reduction through supervised learning (KNN, Random Forest) and
-unsupervised LLMs ( Gemma 3.12b and Llama 3.2 3B) for stance
-classifications. Our supervised learning models overall achieved low to
-moderate success in this classification task, with the strongest
-performance in identifying opposing viewpoints, which were also the most
-prevalent in our labeled data. Moreover, both models struggled with the
-``favor'' and ``neutral'' stances, suggesting limitations in our
-features to capture these nuances. Our unsupervised learning models also
-showed the best ability to classify ``oppose'' comments, yet exhibited
-significant challenges with the ``favor'' and ``neutral'' categories,
-particularly demonstrating low precision.
+We explored public sentiment of DOGE's federal workforce reduction
+through supervised learning (KNN, Random Forest) and unsupervised LLMs (
+Gemma 3.12b and Llama 3.2 3B) for stance classifications. Our supervised
+learning models achieved low-moderate success in this classification
+task, with the strongest performance in identifying opposing viewpoints.
+Moreover, both models struggled with the ``favor'' and ``neutral''
+stances, suggesting limitations in our features to capture these
+nuances. Our unsupervised learning models also showed the best ability
+to classify ``oppose'' comments, yet exhibited significant challenges
+with the ``favor'' and ``neutral'' categories, particularly
+demonstrating low precision.
 
